### 2018-10-11 manuscript/manuscript-export.tex
created latex version of manuscript

\hypertarget{a-comprehensive-framework-to-capture-the-arcana-of-neuroimaging-analysis}{%
\section{A comprehensive framework to capture the arcana of neuroimaging
analysis}\label{a-comprehensive-framework-to-capture-the-arcana-of-neuroimaging-analysis}}

Thomas G. Close\textsuperscript{1,2},
Phillip G. D. Ward\textsuperscript{1,3,4},
Francesco Sforazzini\textsuperscript{1},
Wojtek Goscinski\textsuperscript{6},
Zhaolin Chen\textsuperscript{1,5},
Gary F. Egan\textsuperscript{1,3,4}

1. Monash Biomedical Imaging, Monash University, Melbourne, Australia

2. Australian National Imaging Facility, Australia

3. Australian Research Council Centre of Excellence for integrative
Brain Function, Melbourne, Australia

4. Monash Institute of Cognitive and Clinical Neurosciences, Monash
University, Melbourne, Australia.

5. Department of Electrical and Computer Systems Engineering, Monash
University, Melbourne, Australia

6. Monash eResearch Centre, Monash University, Melbourne, Australia

\hypertarget{introduction}{%
\section{Introduction}\label{introduction}}

Despite the availability of well-established neuroimaging analysis
packages (Cox 1996; Smith et. al. 2004; Friston et. al. 2007; Tournier
et. al. 2012), the arcana of neuroimaging analysis is substantial due to
the range of available tools, tunable parameters, and imaging sequences
involved (Cusack et. al. 2015). The distribution of complete
``end-to-end'' workflows, from acquired data to publication results, is
necessary for routine reproduction because of the effort required to
accurately exactly reimplement such analyses (Kennedy 2018). It is also
difficult to adapt existing workflows to new studies without detailed
knowledge of their design. Therefore, flexible, portable and complete
workflows are important to promote reproduction and code reuse in
neuroimaging research.

A barrier to designing portable and complete workflows is the
heterogeneity of data storage conventions (Marcus et. al. 2007; Das et.
al. 2011; Gorgolewski et. al. 2016). To address this, the emerging Brain
Imaging Data Standard (BIDS) (Gorgolewski et. al. 2016) provides a way
to standardise the storage of neuroimaging data in file system
directories. BIDS specifies strict file and directory naming
conventions, which facilitate the design of portable \emph{BIDS Apps}
(https://bids-apps.neuroimaging.io). However, for research groups with
sufficient informatics support, software-managed repositories (Marcus
et. al. 2007; Das et. al. 2011) can provide additional features, such as
flexible access-control and automated pipelines. Therefore, for
published workflows, the choice of repository should be transparent in
order to maximise their audience.

While neuroimaging analyses are generally amenable to standardisation
(Kennedy 2018), minor modifications are often required to accommodate
idiosyncrasies of the acquisition protocols in use at different sites
(Esteban et al. 2018). Therefore, workflows may require conditional
logic in construction or execution to be portable. Nipype is a flexible
Python framework for neuroimaging analysis in which workflows are
constructed programmatically in Python (Gorgolewski et al. 2011).
Programmatic construction allows for rich control-flow logic that is not
readily available in alternative workflow frameworks (Cusack et. al.
2015; Achterberg et. al. 2016; Amstutz et. al. 2016), and has been used
to implement workflows that are robust to differences in fMRI protocols
across a large number of sites (Esteban et al. 2018).

The trend towards large multi-site and multi-contrast datasets collected
over a number of years (Van Essen et. al. 2012; Thompson et. al. 2014;
Sudlow et. al. 2015) presents additional challenges to workflow design.
Analysis packages are constantly being developed and improved, so the
state-of-the-art workflow for a particular analysis can change over
time. Therefore, it is challenging to ensure workflows are applied
consistently over the course of long studies (Cusack et. al. 2015).

While analysis workflows for different contrasts and modalities are
typically implemented independently, they can share common processing
steps (e.g. non-linear registration to standard space, surface
parcellation) and their outputs may need to be integrated to produce
publication results. For large scale studies, which are typically
processed on the cloud or high-performance computing (HPC) clusters,
rerunning common segments can lead to significant increases in
computation time and therefore project cost. In addition, duplication of
processing segments increases time for manual quality control (QC),
making the reuse of intermediate derivatives a practical requirement for
some large studies (Schreiber et. al. 2018).

To maximise the reusability of neuroimaging workflows and avoid frequent
reimplementation of standard analyses, workflow implementations should
be flexible, extensible and applicable to a wide range of storage
systems. In addition, in order to promote routine reproduction of
neuroimaging studies, published workflow implementations should include
the complete procedure, from acquired data to publication results.
However, ensuring workflow implementations are flexible, portable and
complete adds a high degree of complexity and effort to the design
process.

Our objective was to extract common elements of repository-centric
workflow design into an abstract framework to make it practical to
implement flexible, portable and complete workflows for a wide range of
neuroimaging analyses. \emph{Abstraction of Repository-Centric ANAlysis
(Arcana)} (http://arcana.readthedocs.io) is a Python framework for
designing complex workflows in which modular Nipype pipelines operate on
data stored in various repositories. Intermediate derivatives are
derived on demand, checking against stored provenance for required
updates. Analyses can be applied to XNAT, BIDS and plain-directory
repositories, and using Nipype's execution plugins, run on workstations
or be submitted as batch jobs to HPC schedulers. Arcana's architecture,
with programmatic workflow construction---yet clear delineation between
analysis design and application---facilitates the implementation of
complex workflows that are portable and complete.

The utility of the Arcana framework is demonstrated by the
implementation of analysis suites for T1, T2* and diffusion weighted MRI
(dMRI) data and the application of dMRI tractogram (Tournier 2012) and
composite vein image (Ward 2018) workflows to data collected from a
healthy subject.

\hypertarget{methods}{%
\section{Methods}\label{methods}}

\hypertarget{framework-overview}{%
\subsection{Framework overview}\label{framework-overview}}

The separation of analysis design and application in the Arcana
framework follows the conceptual divide between classes and objects in
Object-Oriented (OO) software design. \emph{Study} classes encapsulate
imaging data with the suite of analysis methods that can be performed on
them, and, in the basic case, are specialised for a specific imaging
contrast or modality. Study objects apply the analysis suite defined in
the Study class to a specific dataset.

The set of acquired data, the derivatives that can be derived from it,
and methods that construct pipelines to derive the derivatives, are
linked together by the \emph{data specification} \emph{table} of the
Study class (Figure 1). Likewise, free parameters used in pipeline
construction are defined in the class' \emph{parameter specification}
\emph{table}. Class inheritance can be used to specialise analysis
suites by overriding pipeline constructor methods or entries in the
specification tables. Analysis suites for multi-modal data can be
implemented by combining multiple Study classes in \emph{MultiStudy}
classes\emph{.}

\includegraphics[width=3.55074in,height=3.16146in]{media/image23.png}

\textbf{Figure 1} - Example study. Blue boxes represent acquired (input)
data (filesets or fields) stored in a repository and green derivatives
from that data stored alongside the original data. Orange ovals are
pipelines that operate on data in the repository to derive the
derivatives. Arrows represent data flows, i.e., inputs and outputs to
pipelines.

Analysis methods are applied to a specific dataset by instantiating an
appropriate Study class and requesting a derivative listed in the class'
data specification table. At instantiation, a Study object is passed
references to \emph{Repository} and \emph{Processor} objects, which
define how and where data is stored and processed. When a derivative is
requested, a Study object queries the repository for intermediate
derivatives that can be reused before constructing a workflow to produce
the requested derivative. Workflows are executed in the computing
environment specified by the Processor object and their products are
stored back in the repository for reuse by subsequent analyses (Figure
2). Input data to the study are also stored in the repository, and are
matched against entries in the class' data specification table using
criteria defined in \emph{Selector} objects passed to the Study object
at instantiation.

\includegraphics[width=6.27083in,height=3.15278in]{media/image33.png}

\textbf{Figure 2} - Simplified Unified Modelling Language (UML) diagram
of information flow in the Arcana framework. Boxes: Python classes,
blue=analysis-design, green=analysis-application. Arrows: orange=data,
magenta=workflow description, diamond=aggregated-in. Study classes
construct analysis pipelines, which are sent to the \emph{Processor} to
be processed. Input data is selected by \emph{Selector} objects and
pulled to the compute environment to be processed along with existing
intermediate derivatives. After the derivatives are pushed back to the
repository.

\hypertarget{analysis-design-study-classes}{%
\subsection{Analysis design: Study
classes}\label{analysis-design-study-classes}}

Study classes encapsulate a study dataset (i.e. data collected across
multiple subjects using the same acquisition protocol) with the suite of
analytical methods that can be applied to the dataset. The hierarchy of
a study dataset is assumed to have two levels, \emph{subjects} and
\emph{sessions}, with each session for each subject corresponding to a
specific \emph{visit}, e.g. timepoint in longitudinal study. Derivatives
can be created at any point in this hierarchy: per-session, per-subject,
per-visit and per-study. Iteration over subjects and visits is handled
implicitly by the framework. All Study classes must inherit from the
\emph{Study} base class and be created by the \emph{StudyMetaClass}
metaclass or subclasses thereof.

\hypertarget{data-and-parameter-specification-tables}{%
\subsubsection{Data and parameter specification
tables}\label{data-and-parameter-specification-tables}}

At the heart of each Study class is the data specification table, which
specifies both the input and output data of the analysis, and all the
stages in between. There is a one-to-one relationship between entries in
the data specification table and data that is stored in the repository
or will be stored if and when it is derived. Which intermediate
derivatives to include in the data specification table, and therefore
store in the repository, is left to the discretion of the researcher
designing the analysis. However, as a general rule, derivatives that
require manual QC or are likely to be reused between different branches
of analysis should be included in the table.

Data specified in the data specification table can be of either a
\emph{fileset} or \emph{field} type. Filesets represent single files,
header and data file pairs, or sets of related files typically contained
within single directories (e.g. a multi-volume DICOM dataset). Fields
represent a single integer, floating point value or character string
type. Each Fileset references a \emph{FileFormat} object, which
specifies the formats of the files in the set. File formats are
explicitly registered by the researcher at design time using the
\emph{FileFormat.register(format)} class method to avoid conflicts where
the same extension is used for different formats in different contexts.

Fileset and field specifications are passed to the data specification of
a Study class via the \emph{add\_data\_specs} class attribute as a list
of named \emph{FilesetSpec} and \emph{FieldSpec} objects (Figure 3).
Specifications for acquired data (i.e. input data to the study) are
distinguished from derived data by using the \emph{AcquiredFilesetSpec}
and \emph{AcquiredFieldSpec} subtypes. However, the distinction is
fluid, with derived specifications able to be overridden by acquired
specifications in subclasses or MultiStudy classes, and vice-versa, or
passed inputs when the class is instantiated.

\includegraphics[width=5.74851in,height=6.07813in]{media/image27.png}

\textbf{Figure 3} - Example data and parameter specifications. The data
specification specifies two ``acquired'' file sets, `one' and `ten' and
ten derived file sets that can be derived from them, at least
indirectly. Each derived data spec, specifies the name of the pipeline
constructor that creates the pipeline that derives them. Parameter
specifications specify a name and default value for free parameters of
the Study class.

Both acquired and derived data specifications have a \emph{frequency}
attribute which specifies where the data sits in the hierarchy of the
dataset and can take the values \emph{per\_session},
\emph{per\_subject}, \emph{per\_visit} or \emph{per\_study}. In
addition, derived specifications are passed the name of a method in the
class that constructs the pipeline to derive them. Therefore, while a
pipeline can have multiple outputs, each derivative is derived by only
one pipeline.

For fileset specifications that correspond to a known type in the BIDS
standard, a \emph{BidsSelector} or \emph{BidsAssociatedSelector} can be
provided to the \emph{bids} keyword arg of the spec. BidsSelector
specifies a primary scan in the BIDS standard using its type, modality
and optional run number. BidsAssociatedSelector is used to select
associated files, such as field maps and diffusion encoding matrices.
When passing a BidsSelector to a FilesetSpec the \emph{run} keyword
argument of the selector is typically not set, so it can be read from
the \emph{bids\_run} attribute of the Study. This allows the Study class
to be applicable to any BIDS run.

Similar to data specifications, parameter specifications are included in
the Study class by providing a list of \emph{ParameterSpec} objects to
the \emph{add\_parameter\_specs} class attribute. ParameterSpec objects
are initialised with a name and default value. Special parameters that
specify a qualitative change in the analysis, for example using ANTs
registration (Avants et. al. 2011) instead of FSL registration (Smith
et. al. 2004), are specified by the \emph{SwitchSpec} subtype.
SwitchSpecs take a name, default value and a list of accepted values at
initialisation.

\hypertarget{workflow-design}{%
\subsubsection{Workflow design}\label{workflow-design}}

Analysis workflows are implemented in Arcana as a series of pipelines
that each perform a unit of the analysis (e.g. registration, brain
extraction). Each pipeline is in turn constructed from a (typically
small) graph of Nipype nodes, with each node wrapping a stand alone tool
(e.g. FSL's FLIRT) or analysis package function (e.g. SPM's \emph{coreg}
tool).

Pipelines are included in the analysis suite of a Study class by
defining a method in the class that constructs and returns a
\emph{Pipeline} object, and referencing that method in the class' data
specification table. Pipeline objects are thin wrappers around Nipype
workflows, which manage the namespaces of the workflow nodes, and should
be created in constructor methods using the \emph{Study.new\_pipeline}
method (Figure 4).

\includegraphics[width=5.33854in,height=4.21623in]{media/image35.png}

\textbf{Figure 4} - Example pipeline constructor method. Pipelines are
created using the \emph{create\_pipeline} method of the Study class.
Pipeline objects are thin wrappers around Nipype workflows to allow for
namespace management.

At instantiation (via the new\_pipeline method) a Pipeline is passed the
following arguments:

\begin{itemize}
\item
  \begin{quote}
  A name for the pipeline
  \end{quote}
\item
  \begin{quote}
  The inputs to the pipeline
  \end{quote}
\item
  \begin{quote}
  The output specifications the pipeline
  \end{quote}
\item
  \begin{quote}
  Description of the pipeline
  \end{quote}
\item
  \begin{quote}
  A list of scientific references the analysis was informed by
  \end{quote}
\item
  \begin{quote}
  Keyword arguments passed directly from the pipeline constructor method
  \end{quote}
\end{itemize}

Inputs and outputs refer to entries in the data specification table and
specify the file formats (fileset) or data type (field) that the input
is expected in, or the output will be returned in. If this
format/data-type differs from that specified in the data specification
table then an implicit conversion will be performed when the pipeline is
executed, thereby making data conversion transparent to the researcher.
Every pipeline constructor should take only wildcard keyword arguments
(i.e. **kwargs), which should be passed directly through to the
new\_pipeline method to enable modification of the pipeline namespace by
overriding methods in subclasses.

The syntax for workflow graph construction in Arcana is inspired by the
proposed format for Nipype v2.0
(\href{https://github.com/nipy/nipype/issues/2539}{{https://github.com/nipy/nipype/issues/2539}}),
and will be updated as Nipype v2.0 is developed and upstream
functionality becomes available. Workflow nodes are created from Nipype
interfaces using the \emph{Pipeline.add(name, interface)} method of the
Pipeline should be used. Once created, the inputs of the node can be set
explicitly via the node's \emph{inputs} attribute, connected to other
nodes with the \emph{Pipeline.connect(out\_node, out\_node\_output,
in\_node, in\_node\_input)} method, or connected to inputs of the
pipeline. Pipeline inputs and outputs are connected to nodes using the
\emph{Pipeline.add\_input(spec\_name, node, node\_input)} and
\emph{Pipeline.add\_output(spec\_name, node, node\_output)} methods,
respectively.

Any external software packages required by a node should be referenced
in the \emph{requirements} keyword argument as a list of
\emph{Requirement} objects when the node added to the pipeline. These
requirements can be used by the Processor to configure environment
modules (Furlani, J. 1991) if present, to ensure the required software
packages are available. Similarly, the expected memory requirements and
wall time for the node execution should be provided as keyword args,
\emph{memory}, and \emph{wall\_time}, so they can be inserted into job
scripts submitted to schedulers by HPC Processors.

Iteration over subjects and visits is handled implicitly by Arcana and
depends on the frequency of the pipeline's inputs and outputs. To create
a summary derivative (i.e. frequency != \emph{per\_session}) from more
frequent data a join node is used. Join nodes that join over subjects or
visits are created with \emph{Pipeline.add}\_\emph{join\_subjects(name,
interface, joinfield)} and \emph{Pipeline.add\_join\_visits(name,
interface, joinfield)} respectively. As in the underlying Nipype, the
\emph{joinfield} argument specifies which inputs of the receiving node
to join into lists. If direct access to the subject or visit IDs is
required by a node they can be connected to the implicit iterator nodes
with \emph{Pipeline.connect\_subject\_id(node, name)} and
\emph{Pipeline.connect\_visit\_id} respectively. Note that expansion
over iterator sources is handled implicitly by Nipype when nodes with
different iterators are connected to a downstream node.

Study parameters can be accessed during pipeline construction with the
\emph{Study.parameter(name)} method. If conditional logic is included in
the workflow construction that alters the pipeline inputs, outputs or
parameters then it should be controlled by a switch instead of a
parameter. The analysis branch designated by a switch value should be
tested with \emph{Study.branch(name, ref\_value)} method.

For convenience when the pipeline to construct only consists of a single
node, the \emph{Study.pipeline\_constructor} classmethod to create the
method (Figure 5).

\includegraphics[width=6.27083in,height=2in]{media/image7.png}

\textbf{Figure 5} - Example basic constructor defined using the
\emph{Study.pipeline\_constructor} convenience method.

\hypertarget{extension-and-specialisation-by-class-inheritance}{%
\subsubsection{Extension and specialisation by class
inheritance}\label{extension-and-specialisation-by-class-inheritance}}

Because Arcana analyses are implemented as Python classes, class
inheritance can be used to specialise existing analyses.

Pipeline constructors can be overridden in subclasses like any Python
method. Typically the overriding method will call the superclass method
to construct a base Pipeline, apply modifications and return the
modified Pipeline. In this scenario, references to the data
specification in the superclass method can be mapped onto different
entries in the subclass by passing a dictionary containing the maps to
the \emph{name\_map} keyword argument of pipeline constructor in the
superclass.

Instead of setting the class attributes directly, the data and parameter
specifications are set by the metaclas\emph{s}, in order to combine with
specifications from base classes. The combined data and parameter
specifications are constructed by visiting the class' bases in reverse
method resolution order (MRO) and adding specifications from their
\emph{add\_data\_specs}, \emph{add\_parameter\_specs} attributes,
overriding previously added specifications with matching names. Note
that in this scheme, specifications can only be appended or overridden
but not removed by Study subclasses so as not to break workflows
inherited from base classes.

\hypertarget{implementing-multi-modal-studies}{%
\subsubsection{Implementing multi-modal
studies}\label{implementing-multi-modal-studies}}

While basic Study classes are typically associated with single image
modality or contrast, the analysis suites implemented by them can be
integrated into multi-modal analysis by aggregating multiple Study
classes (sub-studies) in a \emph{MultiStudy} class. Analysis suites are
integrated by joining the data specification tables of the sub-studies
of a MultiStudy class. Entries in specification tables of sub-studies
are joined by mapping them to a common entry in the specification table
of the MultiStudy (Figure 6). This enables derivatives from one
sub-study (e.g. brain extracted T1-weighted anatomical) to be referenced
by workflows of other sub-studies (e.g. anatomically constrained dMRI
tractography).

\includegraphics[width=3.86429in,height=4.70313in]{media/image20.png}

\textbf{Figure 6} - Example MultiStudy. Blue boxes represent acquired
(input) data (filesets or fields) and green derivatives. Orange ovals
are pipelines. Blue and green arrows: acquired and derived inputs to
pipelines, respectively. Orange arrows: outputs of pipelines. Dashed
boxes represent data specifications in a sub-study that are present in
the global namespace and mapped into the sub-study space, and dotted
arrows the mappings. Sub-studies are linked by mapping the same data
spec in the global space onto data specifications the multiple sub-study
namespaces (e.g. \emph{Derived 1, 2 \& 3}). There are no restrictions
between mapping acquired and derivative specifications: both acquired
and derivative specifications can be mapped onto acquired data or
derivative specifications in sub-studies. If a spec in the global spaced
is mapped onto a derivative spec in the sub-study space, then the
pipeline that generates that derivative in the sub-study will not run
unless it generates other required derivatives (e.g. \emph{Pipeline 3}).

All MultiStudy classes must inherit from the Multi\emph{Study} base
class and be created by the Multi\emph{StudyMetaClass} metaclass or
subclasses thereof. As in the case of subclassing the standard Study
class, additional data and parameter specifications can be added to the
class via \emph{add\_data\_specs} and \emph{add\_parameter\_specs}
respectively for additional analysis not included in the sub-studies.

Sub-studies are aggregated in the \emph{sub-study} \emph{specification
table} of a MultiStudy class via a list of \emph{SubStudySpec} objects
in the \emph{add\_sub\_study\_specs} class attribute, in the manner of
data and parameter specifications. A SubStudySpec consists of a name, a
Study class, and a \emph{name map} dictionary\emph{.} The name map
dictionary maps data and parameter specification names from the
namespace of the MultiStudy class to the namespace of the Study class.

Entries in the specification tables of sub-study classes that are not
referenced in the sub study's name map are implicitly mapped to the
MultiStudy namespace in the construction of the MultiStudy class by the
metaclass using the name of the sub-study as a prefix. If the spec is a
derivative then the pipeline constructor used to derive it is also
mapped into the MultiStudy namespace. For example, \emph{derived1} in
\emph{sub\_study2} would be mapped to \emph{sub\_study2\_derived1} along
with the method \emph{sub\_study2\_pipeline1}.

\hypertarget{analysis-application-study-instances}{%
\subsection{Analysis application: Study
instances}\label{analysis-application-study-instances}}

To apply the analysis blueprint specified in a Study class to a specific
dataset, an instance of the Study class is created with details of where
the data is stored (the \emph{Repository}) and the computing environment
available to process it (the \emph{Processor}). A Study object controls
the construction of analysis workflows, the execution of the workflows,
and the flow of data to and from the repository (Figure 7).

\includegraphics[width=6.27083in,height=4.69444in]{media/image21.png}

\textbf{Figure 7} - Detailed Unified Modelling Language (UML) diagram of
information flow in the Arcana framework. Boxes: Python classes
(blue=core, green=interchangeable modules, grey=example
specialisations). Arrows: orange=data, magenta=workflow description,
diamond=aggregated-in, triangle=subclass-of. Calling \emph{data(name)}
on a Study subclass constructs the requisite pipelines (as specified in
\emph{Study.data\_specs}) to produce the requested data, and sends them
to the \emph{Processor} to be processed. Data is selected by
\emph{Selector} objects, pulled to the compute environment to be
processed, and then the derivatives are pushed back to the repository.
Repositories can be of plain directories, or BIDS or XNAT repositories.

Each Study object is assigned a name, which is used to differentiate its
results from alternative analyses on the same dataset (e.g. by different
members of a lab). Parameters are set on initialisation of the Study
object along with the range of subject and visit IDs to be included in
the analysis (if they are not provided then all IDs are included). The
remaining arguments passed to the Study object initialisation are the
Repository and Processor modules and a list of \emph{Selector} objects
to select input datasets from the repository (Figure 8).

\includegraphics[width=6.27083in,height=3.94444in]{media/image36.png}\textbf{Figure
8} - Example application of Study class to a dataset stored in an XNAT
repository. Once the Study object has been initialised potential
derivatives of the Study can be requested, and will be generated and
stored in the repository if already present.

\hypertarget{repository-modules}{%
\subsubsection{Repository modules}\label{repository-modules}}

In Arcana, repository access is encapsulated within modular
\emph{Repository} objects to enable switching between different
repositories and repository types at analysis ``application time''
(Figure 2). There are currently three supported repository types, XNAT
(Marcus et al. 2007), BIDS (Gorgolewski et al. 2016) and a simple
``directory'' format, which are encapsulated by \emph{XnatRepository},
\emph{BidsRepository}, and \emph{DirectoryRepository} classes
respectively.

In its most basic form, a directory repository is just a file system
directory with separate subdirectories for each subject in the study,
with subject IDs taken from the subdirectory names. If the study has
more than one visit then nested subdirectories for each visit are
required in the subject subdirectories. Note that the directory
repository is similar to the BIDS format, however, there are no naming
conventions in the directory repository, which enables prototyping and
testing of analyses on loosely structured data.

Derivatives are stored by their specification name in a study-specific
namespaces to avoid clashes with separate analyses. In directory
repositories this namespace is a subdirectory named after the study
nested within each visit subdirectory if present or subject subdirectory
otherwise. In BIDS repositories, the namespace is a subdirectory of the
\emph{derivatives} directory, again named after the study. In XNAT
repositories, derivatives for each session are stored in separate
\emph{MrSession} objects alongside the primary session underneath its
\emph{Subject}, and are named
\emph{\textless{}primary-session-name\textgreater{}\_\textless{}study-name\textgreater{}}
(Table 1).

Derived filesets are stored with the format specified in the study's
data specification. In plain-directory and BIDS repositories, fields are
stored in a single JSON file named `\_\_fields\_\_.json' in each derived
session, and on XNAT they are stored in custom fields of the derived
session. Provenance is stored in a `\_\_prov\_\_' sub-directory (dataset
on XNAT) of the derivatives directory (MrSession on XNAT) in separate
JSON files for each pipeline named after the pipeline (Table 1).

Summary data (i.e. with \emph{per\_subject}, \emph{per\_visit}, and
\emph{per\_study} frequencies\emph{)} are stored in specially named
subjects and visits (e.g. `all'), the names for which are specified when
the repository is initialised. For example, given in plain-directory
repository using all as the summary name for both subjects and visits,
per\_subject data for `subj1' would be stored at
\emph{\textless{}root-dir\textgreater{}/subj1/}all, per\_visit data for
`visit1' in \emph{\textless{}root-dir\textgreater{}/}all\emph{/visit1},
and per\_study data in \emph{\textless{}root\_dir\textgreater{}/}all/all
(Table 1).

\begin{longtable}[]{@{}llll@{}}
\toprule
& \textbf{Plain-directory} & \textbf{BIDS} &
\textbf{XNAT}\tabularnewline
\midrule
\endhead
\textbf{Derivatives} & \emph{/subject/visit/study} &
/derivatives/study/subject/visit &
/subject/\emph{visit\_study}\tabularnewline
\textbf{Fields} & \emph{.../}\_\_fields\_\_\emph{.json} &
\emph{.../}\_\_fields\_\_\emph{.}json & ``custom
variables''\tabularnewline
\textbf{Provenance} & \emph{.../}\_\_prov\_\_\emph{/pipeline.}json &
\emph{.../}\_\_prov\_\_\emph{/pipeline.}json &
.../scans/\_\_prov\_\_/resources/\emph{pipeline/}prov\emph{.}json\tabularnewline
\textbf{per\_subject} & \emph{/subject/}all\emph{/study} &
\emph{/derivatives/study/subject/}all &
\emph{/subject/}all\_\emph{study}\tabularnewline
\textbf{per\_visit} & \emph{/}all\emph{/visit/study} &
\emph{/derivatives/study/}all\emph{/visit} &
\emph{/}all\emph{/visit\_study}\tabularnewline
\textbf{per\_study} & \emph{/}all\emph{/}all\emph{/study} &
\emph{/derivatives/study/}all\emph{/}all &
\emph{/}all\emph{/}all\_\emph{study}\tabularnewline
\bottomrule
\end{longtable}

\textbf{Table 1} - Storage locations of derived data for each repository
type. Derivatives are stored in separate namespaces for each Study
instance to enable multiple analyses on the same datasets with different
parameterisations. `...' refers to the \emph{Derivatives}
directory/xnat:MrSession.

Each study can only have one repository in which derivatives are stored.
However, a study can draw data from multiple auxiliary repositories,
which are specified in the inputs passed to the study. When using
multiple input repositories, subject and visit IDs will often need to be
mapped from their values in the auxiliary repositories to the ``ID
space'' of the study. This mapping is specified using \emph{IdMapper}
objects passed to \emph{subject\_id\_map} and \emph{visit\_id\_map}
keyword arguments during initialisation of a repository.

New repository modules for additional repository types can be
implemented by extending the Repository abstract base class and
implementing a small set of methods (Table 2).

\begin{longtable}[]{@{}ll@{}}
\toprule
\textbf{Method name} & \textbf{Function}\tabularnewline
\midrule
\endhead
find\_data() & Queries repository to find all existing filesets and
fields and registers them with the
\emph{Repository.found\_fileset(fileset)} and
\emph{Repository.found\_field(field)} methods
respectively.\tabularnewline
get\_fileset(Fileset) & Caches the files in a Fileset locally and
returns the path to the primary file or directory in the
cache.\tabularnewline
get\_field(Field) & Retrieves and returns the value of the field from
the repository\tabularnewline
put\_fileset(Fileset) & Inserts the files in the Fileset into the
repository and updates the local cache.\tabularnewline
put\_field(Field) & Inserts the value of the Field into the
repository\tabularnewline
connect() & Opens a connection to the repository (optional). Called by
methods in the base class before entering outer processing
loops.\tabularnewline
disconnect() & Closes connection to repository opened by
\emph{connect()} method (optional)\tabularnewline
\bottomrule
\end{longtable}

\textbf{Table 2} - Abstract methods in the base Repository class that
need to be implemented by platform-specific sub-classes.

\hypertarget{study-inputs}{%
\subsubsection{Study inputs}\label{study-inputs}}

While derivatives generated by a Study object are named in accordance
with the data specification of the Study class, arbitrary naming
conventions can be used for input datasets and fields to allow for
heterogeneity in acquisition procedures. A selection stage is therefore
necessary to match input data to appropriate entries in the data
specification table of the Study class. The criteria for this selection
is passed to the Study object at instantiation and is required to match
exactly one fileset or field in every session included in the study.

Selection criteria are specified by list of \emph{FilesetSelector} and
\emph{FieldSelector} objects provided to the \emph{inputs} argument of
the Study initialisation method. Matching is typically performed on file
names (dataset labels for XNAT repositories), and field names. If the
names are inconsistent across the study then regular expressions can be
used instead of exact matches by passing \emph{is\_regex=True} when
initialising the Selector. Additional criteria can be used to
distinguish cases where multiple filesets in the session match the
pattern provided, such as DICOM header values, or when using an XNAT
repository, the order and ID of the dataset.

Inputs can be drawn from auxiliary repositories by providing alternative
Repository instances to the \emph{repository} keyword of the Selector.
Care should be taken to ensure that the subject and visit ID schemes
will map correctly to that of the primary repository (see
\emph{Repository modules}). If the primary repository is empty (i.e. all
inputs come from auxiliary repositories) then explicit
\emph{subject\_ids}, \emph{visit\_ids} need to be provided and the
\emph{fill\_tree} flag set when initialising the Study.

If the data to select has been derived from an alternative study, then
the name of the alternative study can be passed to the
\emph{from\_study} keyword argument provided to the selector. There are
no restrictions on selecting any data, derived or otherwise, to match
acquired or derived specifications. For example, it is possible to
deliberately skip analysis steps by selecting an output of an early step
in a previous run as a match for a later derived spec although this is
not recommended as standard practice.

Specific files and fields that are not stored within a repository can be
passed as inputs in \emph{FilesetCollection} and \emph{FieldCollection}
objects. Collection objects reference an entry in the data specification
table and contain a single Fileset or Field for every session (or
subject/visit/study depending on the frequency of the corresponding data
spec). Collection objects can be used to pass reference atlases and
templates as inputs to analyses. They can also be set as the ``default
input'' for a data spec using the \emph{default\_input} keyword
argument. For the sake of portability, default inputs should be
restricted to data in publically accessible repositories or included in
standard software packages (e.g. FSL).

When using BIDS repositories, the selection stage is typically already
included in the data specification (see \emph{Data and parameter
specifications)} so inputs do not need to be provided to the
initialisation of the Study. However, BidsSelector and
BidsAssociatedSelector objects can be provided to override the default
selections is required.

\hypertarget{processor-modules}{%
\subsubsection{Processor modules}\label{processor-modules}}

Processor modules control how and where pipelines generated by a Study
are executed. There currently four Processor modules implemented in
Arcana: \emph{LinearProcessor}, \emph{MultiProcProcessor},
\emph{SlurmProcessor} and \emph{SgeProcessor}, which wrap the
correspondingly named Nipype execution plugins. The main task performed
by the processor, as separate from the Nipype execution plugin it wraps,
is to determine which pipelines need to be run and link them into a
single workflow. Since this logic is implemented in the Processor
abstract base class, wrapping additional Nipype plugins as required is
trivial.

A processor is used internally by a Study instance to execute pipelines
to derive derivatives requested from the data specification by the
\emph{Study.data(name{[}, name,...{]})} method (Figure 2). The first
step in this procedure is to query the repository tree for all data and
provenance associated with the study. Sessions for which the requested
outputs of the pipeline are already present in the repository are
excluded from the list to process. For the remaining sessions to
process, inputs of the pipeline that are derivatives themselves are
added to the stack of requested derivatives. This procedure is repeated
recursively until there are no sessions to process or all inputs to the
pipeline are study inputs at a given depth.

When a pipeline is processed it is connected to \emph{Source} and
\emph{Sink} nodes, which get and put the pipeline inputs and outputs
from and to a repository, respectively. Separate source and sink nodes
are used for each data frequency (i.e. per-session, per-subject,
per-visit, per-study). If implicit file format conversion is required
(i.e. the input or output format differs from the data specification)
then additional format converter nodes are inserted after the source
nodes or before the sink nodes. Iterator nodes that iterate over the
required subjects and visits are connected to the sources, and report
nodes that join over subjects and visits are connected to the sink
nodes. Report nodes of upstream pipelines are connected to downstream
iterator nodes to create a single workflow, which is then executed using
the Nipype execution plugin.

Software versions are managed by the processor if environment modules
(Furlani 1991) are installed on the system. These are loaded and
unloaded before the interface of a workflow node is run based on the
requirements specified for the node during construction of the pipeline
(see \emph{Pipeline constructors}). Maps from requirement names to
module names in the processing environment can be passed to the
Processor at initialisation. For plugins that submit jobs to HPC
schedulers (e.g. SLURM, SGE), node memory and wall-time requirements are
inserted into jobscripts where required.

Provenance is stored for each pipeline run alongside the generated
derivatives and consists of: parameter values used by the pipeline,
software versions used by the pipeline, a graph representation of the
underlying Nipype workflow, checksums of inputs, version of Arcana used,
version of Nipype used, subject and visit IDs used by study.

For subsequent analyses, changes w.r.t. Any of the stored values, with
the exception of subject and visit IDs, will be flagged as a mismatch.
Subject or visit IDs only flag a mismatch if any of the inputs, or
inputs of upstream pipelines, are per-visit or per-subject,
respectively, or per-study. How provenance mismatches are handled by the
study is determined by the \emph{reprocess} flag, which is passed to the
Study on initialisation (Table 3).

\begin{longtable}[]{@{}ll@{}}
\toprule
\textbf{\emph{Repocess} flag value} & \textbf{Behaviour when mismatching
derivatives are found}\tabularnewline
\midrule
\endhead
False (default) & An exception will be raised\tabularnewline
True & Mismatching derivatives will be reprocessed\tabularnewline
`Ignore' & Mismatches will be ignored\tabularnewline
`ignore\_versions' & Version mismatches will be ignored, other
mismatches cause an exception to be raised\tabularnewline
`ignore\_versions\_true' & version mismatches will be ignored, other
mismatches will cause the derivative to be reprocessed\tabularnewline
\bottomrule
\end{longtable}

\textbf{Table 3} - Effect of the \emph{reprocess} flag value on the
behaviour of the study when existing derivatives are found that were
derived with mismatching inputs and parameters.

Additionally, a time limit can be passed to the
\emph{reprocess\_time\_limit}, and if the estimated time to reprocess
all the required sessions is less than the time limit they will be
reprocessed and otherwise an exception will be raised.

\hypertarget{results}{%
\section{Results}\label{results}}

The Arcana framework is distributed as a publicly available software
package via GitHub
(\href{http://github.com/MonashBI/arcana}{{http://github.com/MonashBI/arcana}})
and the Python Package Index (PyPI)
(\href{https://pypi.org/project/arcana/}{{http://pypi.org/project/arcana/}}).
Study classes for T1, T2* and diffusion weighted MRI data have been
implemented as part of the \emph{Biomedical imAgiNg ANAlysis (Banana)}
package
(\href{https://github.com/MonashBI/banana}{{http://github.com/MonashBI/banana}};
\href{http://pypi.org./project/banana}{{http://pypi.org./project/banana}}).
All three classes, \emph{T1wStudy}, \emph{T2starwStudy} and
\emph{DmriStudy}, inherit generic image analysis methods, such as
registration and brain extraction, from the base class \emph{MRIStudy}.
The T1Study and T2starStudy classes are aggregated into the
\emph{T2starwT1wStudy} MultiStudy class to combine analysis of T2* and
T1-weighted contrasts.

The DmriStudy class implements diffusion tensor metrics, FA and ADC, as
well as global tractography using streamlines tracking from the MRtrix
toolbox (Tournier et. al. 2010; Tournier et. al. 2012) (Figure 9).

\includegraphics[width=3.82849in,height=6.85938in]{media/image28.png}

\textbf{Figure 9} - Example diffusion MRI (dMRI) study, which can derive
tensor metrics, fractional anisotropy (FA) and apparent diffusion
coefficient (ADC) as well as streamlines fibre tracking. Blue boxes:
acquired (input) data (filesets or fields). Green boxes: derivatives.
Orange ovals: pipelines. Blue and green arrows: acquired and derived
inputs to pipelines, respectively. Orange arrows: outputs of pipelines.
The dMRI magnitude image is preprocessed for motion correction and EPI
distortions masked and bias corrected. From the bias corrected image two
branches of analysis can be performed using the same intermediate
derivatives: FA and ADC and/or streamlines fibre tracking.

The \emph{T2starwT1wStudy} class implements an algorithm to generate
\emph{composite vein images} from the combination of QSM and SWI
contrasts derived from the T2*-weighted acquisition with an vein atlas
registered to the T1-weighted acquisition (Ward 2018) (Figure 10).

\includegraphics[width=4.29167in,height=7.43818in]{media/image32.png}

\textbf{Figure 10} - Combined T1-weighted/T2*-weighted multi-study,
which can derive vein masks by combining Quantitative Susceptibility
Mapping (QSM) and Susceptible Weighted Imaging (SWI) contrasts with a
manual atlas. Blue boxes: acquired (input) data (filesets or fields).
Green boxes: derivatives. Orange ovals: pipelines. Blue and green
arrows: acquired and derived inputs to pipelines, respectively. Orange
arrows: outputs of pipelines. Dashed boxes represent data specifications
in a sub-study that are present in the global namespace and mapped into
the sub-study space, and dotted arrows the mappings. The acquired
T1-weighted image is mapped to both the \emph{magnitude} spec of the
T1-weighted sub-study and the \emph{registration reference} spec of the
T2*-weighted sub-study. The nonlinear transformation from subject to
atlas space are mapped from the T1-weighted sub-study and combined with
the linear registration between T1-weighted and T2*-weighted images, QSM
and SWI images mapped from the T2*-weighted sub-study to produce the
composite-vein image. The brain mask from the T1-weighted sub-study is
combined with the composite vein image to produce the vein mask.

The DiffusionStudy and T2starT1Study classes are further aggregated in
turn into a single MultiStudy class for the results section of this
manuscript\emph{, ArcanaPaper}, (Figure S.1-5). Methods are implemented
in ArcanaPaper to generate and display the derivative images in Figures
11, 12, and 13.

To test the analysis workflows implemented in ArcanaPaper, a healthy
volunteer was scanned using a 3T Siemens Skyra with a 32-channel head
and neck coil. The protocol was a T1-weighted MPRAGE (1mm contiguous,
matrix size 256x240x192, FOV 256x240x192, TE = 2.13ms, TR, = 2300ms, TI
= 900ms, bandwidth=230Hz/pixel), GRE (1.8 mm contiguous, matrix size
256x232x72, FOV 230x208x130, TE = 20ms, TR, = 30ms,
bandwidth=120Hz/pixel), diffusion MRI (1.2 mm contiguous, matrix size
110x100x60, FOV 256x240x192, TE = 95ms, TR, = 8200ms, 33 diffusion
directions with b=1500 mm2/s and 3 b=0, bandwidth=781Hz/pixel)
(\textbf{cite Lifespan paper ??}). Methods for Figure 11, 12, and 13 in
the ArcanaPaper class were applied to the acquired dataset to using the
\emph{SlurmProcessor} to submit jobs to the the MASSIVE HPC cluster
(Goscinski 2014) in order to generate the figures.

Figure 11 displays composite vein images and vein masks for the healthy
volunteer along with the SWI and QSM intermediate derivatives and the
input vein atlas. The derived vein images are comparable to those
generated by the original implementation (Ward 2018). The complete
workflow took ?? min to complete over ?? compute cores.

\includegraphics[width=6.228in,height=4.72396in]{media/image22.png}

\textbf{Figure 11 -} Vein image (\emph{right column}) constructed by
combining susceptibility weighted imaging (SWI) (\emph{left column}),
quantitative susceptibility mapping (QSM) (\emph{left-middle column})
and a vein atlas from manual tracings (\emph{right-middle column}).
\emph{Top row}: sagittal slices. \emph{Middle row}: axial slices.
\emph{Bottom row}: coronal slices.

Figure 12 displays the FA and ADC maps derived from the diffusion MRI
acquisition. The FA map shows high intensity in known white matter
tracts and low intensities in known grey matter regions. The ADC map
shows high intensity in cortical spinal fluid and low intensity through
the rest of the brain.

\includegraphics[width=6.27083in,height=4.18056in]{media/image34.png}

\textbf{Figure 12 -} Fractional Anisotropy (FA) \emph{(top row)} and
Apparent Diffusion Coefficient (ADC) (\emph{bottom rowI)} derived from
diffusion MRI data. \emph{Left column:} axial midline slices.
\emph{Middle column:} coronal midline slices. \emph{Left column}:
sagittal midline slices.

Figure 12 displays the global tractography derived from the dMRI
acquisition. The streamlines follow well known white matter tracts such
as the cortico-spinal, fasciculus and corpus callosum. Intermediate
derivatives derived for the FA and ADC analysis, including the
preprocessed and bias-corrected dMRI image and a whole brain mask, were
reused in the generation of the streamlines reducing the time taken to
produce the tractography results from ?? to ??.

\includegraphics[width=6.27083in,height=2.09722in]{media/image30.png}

\textbf{Figure 13 -} Global tractography performed using the MRtrix
toolbox. Probabilistic streamlines generated with the iFOD2 algorithm
from fibre Orientation Distribution Function (fODF) estimated from
diffusion MRI datasets using Constrained Spherical Deconvolution (CSD).
Streamlines are colour-encoded by orientation: green=anterior-posterior,
blue=inferior-superior, red=left-right. \emph{Left panel:} axial midline
slice. \emph{Middle panel:} coronal midline slice. \emph{Left panel}:
sagittal midline slice.

\hypertarget{discussion}{%
\section{Discussion}\label{discussion}}

We present Arcana, a software framework to facilitate the development of
comprehensive analysis suites for neuroimaging data that implement
complete workflows from repository data to publication results. The
encapsulation of repository data and workflow generation in Arcana
enables researchers to create robust workflows while focussing on the
core logic of their analysis. Arcana's modular pipeline and OO
architecture promotes code reuse between different workflows by
facilitating the sharing of common segments (e.g. registration,
segmentation). The clear separation of analysis design from its
application leads to portable workflows, which can be applied to
datasets stored in a number of storage systems. In addition, the
management of intermediate derivatives, provenance and software
versioning, coupled with ability to submit jobs to HPC clusters, enables
workflows implemented in Arcana to scale to large datasets. Arcana
thereby enables researchers to quickly prototype analysis suites on
local workstations that can be deployed on enterprise-scale
infrastructure without modification.

Software frameworks (Yacoub and Ammar 2004) have been successful in
improving code quality and efficiency of development in a variety of
contexts (Moore et. al. 2008; White 2012; Abadi et. al. 2016). By
factoring out common elements, only features that are specific to the
given application need to be implemented by the analysis designer, and
the common elements become battle hardened through repeated use. Arcana
handles many of the menial tasks involved with workflow implementation,
such as data retrieval and storage, format conversions, and provenance,
reducing the time and effort required to implement robust workflows from
acquired data to publication results.

An oft-repeated mantra in the open-source software movement dubbed
Linus' Law is that "given a large enough beta-tester and co-developer
base, almost every problem will be characterized quickly and the fix
obvious to someone" or more compactly, "given enough eyeballs, all
\href{https://en.wikipedia.org/wiki/Software_bug}{bugs} are shallow"
(Raymond 1999). Given the size of the neuroimaging research community,
there are a large number of potential beta-testers and co-developers.
However, it has been difficult for researchers to collaborate on the
same code base due to slight differences in acquisition protocols,
storage conventions, researcher preferences, and study requirements.

The flexibility and portability of the Arcana framework increases the
feasibility of community collaborations on workflow implementations. The
improvement of code quality in larger community efforts, due to more
eyeballs to detect and fix errors, has the potential to form a
reinforcing cycle where in more developers are attracted to the project.
To these ends, the Banana code repository on GitHub
(\url{http://github.com/MonashBI/banana.git}) is proposed as a code base
for communal development of neuroimaging workflows in Arcana.

A level of proficiency in Python OO design is required to design new
analyses in Arcana, which may preclude inexperienced programmers.
However, only a basic knowledge of Python is required to apply existing
analyses to new datasets. Furthermore, a number of example Study classes
have been implemented, which can guide the hand of analysis designers.
Arcana imposes a consistent structure on workflows implemented within
it, making the code easier to understand for developers who are familiar
with the framework. In addition, class inheritance provides a manageable
way to adapt and extend to existing analyses and highlights where
modified analyses differ from standard procedures.

MR contrast-specific analyses are implemented in NiAnalysis via a chain
of successively specialised Study sub-classes (e.g.
MRI\textgreater{}EPI\textgreater{}dMRI) to enable generic processing
steps (e.g. registration) to be shared between classes. While not
necessary, it is recommended to create a subclass specific to the
research study in question and aggregate all related analysis within it,
since such classes can be applied to alternate datasets in order to
reproduce the exact analysis. The \emph{ArcanaPaper} class (Figure
S.1-5), which contains methods to generate all figures in the Results
section of this manuscript, is an example of this approach.

The abstraction of data and repositories in Arcana enables the same
workflow implementation to be applied to datasets stored in BIDS format
or XNAT repositories. A single code-base can therefore be containerized
into BIDS apps or XNAT pipelines without adaptation, helping to form a
bridge between the two communities of users and developers. Alternative
data storage systems (Book et. al. 2009; Das et. al. 2011, Scott et. al
2011), can be integrated into Arcana by overriding a small number of
methods from the Repository abstract base class. Repository modules
could also be created for data portals such as \emph{DataLad} (Halchenko
2018) in order to take advantage of the range of platforms they support.
Implementing analyses in Arcana therefore enables researchers and
research groups to easily migrate their workflows between storage
platforms, and not risk being locked in to a particular technology.

While Arcana was primarily developed for neuroimaging datasets, it is a
general framework that could be applied to data from other fields.
However, in other contexts, the subject and visit hierarchy may no
longer make sense. In many cases it may be sufficient to map subjects
and/or visits onto alternative concepts (e.g. for meteorological data
\emph{subjects} = \emph{weather stations}, \emph{visits = observation
times}). But some cases may require a deeper data hierarchy (i.e.
greater than two), which is not currently possible in Arcana.

Ensuring that the consistent versions of external tools are used
throughout the analysis is important to avoid introducing biases due to
algorithm updates. In systems with environment modules (Furlani 1991)
installed, Arcana loads and unloads the required modules before and
after each node is executed. When running Arcana within a container,
environment modules and software versions can be installed inside the
container giving exact control over the versions used. To these ends, a
Docker container is available on Docker Hub,
(\href{http://hub.docker.com/r/monashbi/banana}{{http://hub.docker.com/r/monashbi/banana}}),
which can be used as a base for neuroimaging analysis containers.

While the same tools and versions should be applied across an analysis
to avoid bias, there are cases where it is desirable to rerun the same
analysis with different tools substituted at various points in the
workflow. In particular, when introducing new tools or upgrades to
existing tools, it is important to show the effect on the final results
in comparison with existing methods. Furthermore, it is typically not
clear what variability between results produced by comparable tools is
due to. Therefore, in the absence of \emph{a priori} reason to favour a
particular tool, perhaps the most rigorous approach is to rerun analyses
with different combinations of available tools and only present results
that are robust to the ``analytic noise'' (cite here?) they introduce.
Switch parameters make it straightforward to rerun analyses in Arcana
with substituted tools while controlling all other aspects of the
workflow.

Arcana's management of intermediate derivatives and provenance
guarantees that the same analysis is applied across the dataset without
necessarily requiring a complete rerun of the analysis. This guarantee
makes it feasible to process data as it is acquired over the course of
long studies, and therefore help detect any problems that might arise
with the acquisition protocol when they occur. In addition, by reusing
shared intermediate derivatives between analyses, such as the
preprocessed dMRI shared between tensor and fibre tracking workflows
(Figures 12 and 13), processing time as well as time required for manual
QC is minimised. Given analyses implemented in Arcana are also able to
be processed on HPC clusters, they scale well to large studies.

\hypertarget{conclusion}{%
\section{Conclusion}\label{conclusion}}

By managing the complete flow of data from/to a repository with modular
components, Arcana enables complex analyses of large-scale neuroimaging
studies that are portable across a wide range of research sites. The
extensibility of analyses implemented in Arcana, coupled with the
flexibility afforded by programmatic constructuction of pipelines,
facilitates the design of comprehensive analyses by larger communities.
Larger communities of developers working on the same code-base should
make it feasible to capture the arcana of neuroimaging analysis in
templates that can be applied to a wide range of relevant datasets.

\hypertarget{references}{%
\section{References}\label{references}}

Abadi, M., Barham, P., Chen, J., Chen, Z., Davis, A., Dean, J., Devin,
M., Ghemawat, S., Irving, G., Isard, M., Kudlur, M., Levenberg, J.,
Monga, R., Moore, S., Murray, D. G., Steiner, B., Tucker, P., Vasudevan,
V., Warden, P., Wicke, M., Yu, Y., Zheng, X.. (2016). TensorFlow: A
System for Large-Scale Machine Learning TensorFlow: A system for
large-scale machine learning. \emph{12th USENIX Symposium on Operating
Systems Design and Implementation (OSDI '16)}, 265--284.
\href{https://doi.org/10.1038/nn.3331}{{https://doi.org/10.1038/nn.3331}}

Achterberg, H. C., Koek, M., \& Niessen, W. J. (2016). Fastr: A Workflow
Engine for Advanced Data Flows in Medical Image Analysis.
\emph{Frontiers in ICT}, 3(August), 1--11.
\href{https://doi.org/10.3389/fict.2016.00015}{{https://doi.org/10.3389/fict.2016.00015}}

Amstutz, P., Crusoe, M. R., Tijanić, N., Chapman, B., Chilton, J.,
Heuer, M., Kartashov, A., Leehr, D., Ménager, H., Nedeljkovich, M.,
Scales, M., Soiland-Reyes, S., Stojanovic, L. (2016). Common workflow
language, v1. 0. Figshare.
doi:\href{https://doi.org/10.6084/m9.figshare.3115156.v2}{{10.6084/m9.figshare.3115156.v2}}

Avants, B. B., Tustison, N. J., Song, G., Cook, P. A., Klein, A., \&
Gee, J. C. (2011). A reproducible evaluation of ANTs similarity metric
performance in brain image registration. \emph{NeuroImage},
\emph{54}(3), 2033--2044.
\href{https://doi.org/10.1016/J.NEUROIMAGE.2010.09.025}{{https://doi.org/10.1016/J.NEUROIMAGE.2010.09.025}}

Book, G. A., Anderson, B. M., Stevens, M. C., Glahn, D. C., Assaf, M.,
\& Pearlson, G. D. (2013). Neuroinformatics Database (NiDB)--a modular,
portable database for the storage, analysis, and sharing of neuroimaging
data. \emph{Neuroinformatics}, \emph{11}(4), 495-505.

Cox, R. W. (1996): AFNI: Software for analysis and visualization of
functional magnetic resonance neuroimages. \emph{Computers and
Biomedical Research}, 29:162-173.

Cusack R., Vicente-Grabovetsky A., Mitchell D.J., Wild C.J., Auer T.,
Linke A.C., Peelle J.E. (2015) Automatic analysis (aa): Efficient
neuroimaging workflows and parallel processing using Matlab and XML.
\emph{Frontiers in Neuroinformatics} 8:90.

Das, S., Zijdenbos, A. P., Harlap, J., Vins, D., \& Evans, A. C. (2012).
LORIS: a web-based data management system for multi-center studies.
\emph{Frontiers in Neuroinformatics}, 5(January), 1--11.
\href{https://doi.org/10.3389/fninf.2011.00037}{{https://doi.org/10.3389/fninf.2011.00037}}

Esteban O. (2018) FMRIPrep: a robust preprocessing pipeline for
functional MRI. \emph{bioRxiv.} 306951;
doi:\href{https://doi.org/10.1101/306951}{{10.1101/306951}}

Friston K. (2007): Statistical parametric mapping. In:.
\emph{Statistical Parametric Mapping}. Elsevier. pp 10--31.

Furlani, J. (1991). Modules: Providing a flexible user environment.
\emph{Proceedings of the Fifth Large Installation Systems Administration
Conference (LISA V)}, (1), 141--152.

Gorgolewski K.J. et al. (2011), `Nipype: A Flexible, Lightweight and
Extensible Neuroimaging Data Processing Framework in Python'.
\emph{Frontiers in Neuroinformatics}, vol. 5.

Gorgolewski K. J. et al. (2016): `The brain imaging data structure, a
format for organizing and describing outputs of neuroimaging
experiments'. \emph{Scientific Data}, vol. 3.

Goscinski, W. J., P. McIntosh, U. C. Felzmann, A. Maksimenko, C. J.
Hall, T. Gureyev, D. Thompson, A. Janke, G. Galloway, N. E. B. Killeen,
P. Raniga, O. Kaluza, A. Ng, G. Poudel, D. Barnes, T. Nguyen, P.
Bonnington and G. F. Egan (2014). "The Multi-modal Australian ScienceS
Imaging and Visualisation Environment (MASSIVE) high performance
computing infrastructure: applications in neuroscience and
neuroinformatics research." \emph{Frontiers in Neuroinformatics} 8.

Halchenko, Y., Hanke, M., Poldrack, B., Meyer, K., Debanjum, Alteva, G.,
\ldots{} Feilong Ma. (2018). Datalad/Datalad 0.10.2. Zenodo.
https://doi.org/10.5281/zenodo.808846

Kennedy, D. N. (2018). Neuroimaging Neuroinformatics: Sample Size and
Other Evolutionary Topics. \emph{Neuroinformatics}, 16(2), 149--150.
\href{https://doi.org/10.1007/s12021-018-9379-8}{{https://doi.org/10.1007/s12021-018-9379-8}}

Marcus D. S. et al. (2007), `The extensible neuroimaging archive
toolkit'. \emph{Neuroinformatics}, vol. 5, pp. 11--33.

Moore, D., Budd, R., \& Wright, W. (2008). \emph{Professional Python
Frameworks: Web 2.0 Programming with Django and Turbogears}. John Wiley
\& Sons.

Paszke, A., Chintala, S., Collobert, R., Kavukcuoglu, K., Farabet, C.,
Bengio, S., ... \& Mariethoz, J. Pytorch: Tensors and dynamic neural
networks in python with strong gpu acceleration, may 2017.

Raymond, E. S. (1999). The Cathedral and the Bazaar. O'Reilly Media.
ISBN 1-56592-724-9. pp. 30.

Scott, A., Courtney, W., Wood, D., De la Garza, R., Lane, S., Wang, R.,
... \& Calhoun, V. D. (2011). COINS: an innovative informatics and
neuroimaging tool suite built for large heterogeneous datasets.
\emph{Frontiers in neuroinformatics}, \emph{5}, 33.

Smith S. M. et al. (2004): Advances in functional and structural MR
image analysis and implementation as FSL. \emph{NeuroImage} vol. 23, pp.
S208--S219.

Sudlow C. et al. (2015) UK Biobank: An Open Access Resource for
Identifying the Causes of a Wide Range of Complex Diseases of Middle and
Old Age. \emph{PLoS Medicine};12:e1001779.

Schreiber J. et al (2018) `Using a Multi-Petaflop Supercomputer for
Pushing Neuroimaging Analytics to the Next Level', In: \emph{Proceedings
of Organisation for Human Brain Mapping 2018}, Singapore, Singapore

Tournier, J. D., Calamante, F., \& Connelly, A. (2010). Improved
probabilistic streamlines tractography by 2nd order integration over
fibre orientation distributions. In \emph{Proceedings of the
international society for magnetic resonance in medicine} (Vol. 18, p.
1670).

Tournier J.D. et al. (2012): `MRtrix: Diffusion tractography in crossing
fiber regions'. \emph{International Journal of Imaging Systems and
Technology}, vol. 22, pp. 53--66.

Thompson P.M. et al. (2014): `The ENIGMA Consortium: large-scale
collaborative analyses of neuroimaging and genetic data'. \emph{Brain
Imaging and Behavior}, vol. 8, pp.153--182.

Van Essen D.C. et al. (2012): `The Human Connectome Project: A data
acquisition perspective'. \emph{NeuroImage}, vol. 62, pp. 2222--2231.

Ward, P. G. D., Ferris, N. J., Raniga, P., Dowe, D. L., Ng, A. C. L.,
Barnes, D. G., \& Egan, G. F. (2018). Combining images and anatomical
knowledge to improve automated vein segmentation in MRI. NeuroImage,
165, 294--305.
\href{https://doi.org/10.1016/J.NEUROIMAGE.2017.10.049}{{https://doi.org/10.1016/J.NEUROIMAGE.2017.10.049}}

White, T. (2012). \emph{Hadoop: The definitive guide}. O'Reilly Media,
Inc..

Yacoub, S. M., \& Ammar, H. H. (2004). \emph{Pattern-oriented analysis
and design: composing patterns to design software systems}.
Addison-Wesley Professional.

\hypertarget{supplementary-material}{%
\section{Supplementary Material}\label{supplementary-material}}

\includegraphics[width=5.88542in,height=6.21875in]{media/image24.png}

\textbf{Figure S.1} - First section of the definition of the
\emph{ArcanaPaper} Study class. ArcanaPaper implements the analysis
performed for this manuscript. ArcanaPaper is a \emph{MultiStudy} with
two sub-studies, a T2*-weighted/T1-weighted multi-study and a dMRI
study. Two default parameters of the global tracking pipeline in the
dMRI study are overridden to reduce the number of tracks created for
visualisation purposes. The class inherits from the
\emph{ImageDisplayMixin} class to include methods to display slices of
the derived images.

\includegraphics[width=5.89583in,height=5.38542in]{media/image25.png}\textbf{Figure
S.2 -} Method in ArcanaPaper class to generate Figure 11 of this
manuscript. SWI, QSM and vein mask derivatives are generated on demand
if they don't already exist in the repository by the \emph{data} method.
\emph{display\_slice\_panel} and \emph{save\_or\_show} methods from the
\emph{nianalysis.plot.ImageDisplayMixin} base class are used to display
the generated filesets.

\includegraphics[width=5.83333in,height=4.58333in]{media/image31.png}

\textbf{Figure S.3 -} Method in ArcanaPaper class to generate Figure 12
of this manuscript. FA and ADC derivatives are generated on demand if
they don't already exist in the repository by the \emph{data} method.
\emph{display\_slice\_panel} and \emph{save\_or\_show} methods from the
\emph{nianalysis.plot.ImageDisplayMixin} base class are used to display
the generated filesets.

\includegraphics[width=5.98958in,height=5.76042in]{media/image26.png}

\textbf{Figure S.4 -} Method in ArcanaPaper class to generate Figure 13
of this manuscript. Global tracks and FA are derived on demand if they
don't already exist in the repository by the \emph{data} method. Uses
the \emph{display\_tcks\_with\_mrview} method in the
\emph{nianalysis.plot.ImageDisplayMixin} class to display streamlines on
a background of a fractional anisotropy (FA) map using MRtrix's
\emph{mrview} command.

\includegraphics[width=6.125in,height=6.78125in]{media/image29.png}

\textbf{Figure S.5 -} Instantiation of the specific study class to a
dataset stored on the local system. Images for Figures 11, 12 and 13 of
this manuscript are generated by eponymous methods of the study. Entries
in the study's data specification are matched to data in the repository
using \emph{FilesetSelector} objects. The use of \emph{LinearProcessor}
specifies that derivatives are derived using a single process on the
local system. Equivalent figures can be generated for alternative
datasets by specifying a different repository and inputs.

### 2018-10-11 manuscript/manuscript.tex
created latex version of manuscript

--- 2018-10-11 manuscript/manuscript-export.tex
@@
-\hypertarget{a-comprehensive-framework-to-capture-the-arcana-of-neuroimaging-analysis}{%
-\section{A comprehensive framework to capture the arcana of neuroimaging
-analysis}\label{a-comprehensive-framework-to-capture-the-arcana-of-neuroimaging-analysis}}
-
-Thomas G. Close\textsuperscript{1,2},
-Phillip G. D. Ward\textsuperscript{1,3,4},
-Francesco Sforazzini\textsuperscript{1},
-Wojtek Goscinski\textsuperscript{6},
-Zhaolin Chen\textsuperscript{1,5},
-Gary F. Egan\textsuperscript{1,3,4}
-
-1. Monash Biomedical Imaging, Monash University, Melbourne, Australia
-
-2. Australian National Imaging Facility, Australia
-
-3. Australian Research Council Centre of Excellence for integrative
-Brain Function, Melbourne, Australia
-
-4. Monash Institute of Cognitive and Clinical Neurosciences, Monash
-University, Melbourne, Australia.
-
-5. Department of Electrical and Computer Systems Engineering, Monash
-University, Melbourne, Australia
-
-6. Monash eResearch Centre, Monash University, Melbourne, Australia
-
-\hypertarget{introduction}{%
-\section{Introduction}\label{introduction}}
+%%%%%%%%%%%%%%%%%%%%%%% file template.tex %%%%%%%%%%%%%%%%%%%%%%%%%
+%
+% This is a general template file for the LaTeX package SVJour3
+% for Springer journals.          Springer Heidelberg 2010/09/16
+%
+% Copy it to a new file with a new name and use it as the basis
+% for your article. Delete % signs as needed.
+%
+% This template includes a few options for different layouts and
+% content for various journals. Please consult a previous issue of
+% your journal as needed.
+%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%
+% First comes an example EPS file -- just ignore it and
+% proceed on the \documentclass line
+% your LaTeX will extract the file if required
+\begin{filecontents*}{example.eps}
+%!PS-Adobe-3.0 EPSF-3.0
+%%BoundingBox: 19 19 221 221
+%%CreationDate: Mon Sep 29 1997
+%%Creator: programmed by hand (JK)
+%%EndComments
+gsave
+newpath
+  20 20 moveto
+  20 220 lineto
+  220 220 lineto
+  220 20 lineto
+closepath
+2 setlinewidth
+gsave
+  .4 setgray fill
+grestore
+stroke
+grestore
+\end{filecontents*}
+%
+\RequirePackage{fix-cm}
+%
+%\documentclass{svjour3}                     % onecolumn (standard format)
+%\documentclass[smallcondensed]{svjour3}     % onecolumn (ditto)
+\documentclass[smallextended]{svjour3}       % onecolumn (second format)
+%\documentclass[twocolumn]{svjour3}          % twocolumn
+%
+\smartqed  % flush right qed marks, e.g. at end of proof
+%
+\usepackage{graphicx}
+\usepackage{hyperref}
+\usepackage{longtable}
+\usepackage{booktabs}
+%
+% \usepackage{mathptmx}      % use Times fonts if available on your TeX system
+%
+% insert here the call for the packages your document requires
+%\usepackage{latexsym}
+% etc.
+%
+% please place your own definitions here and don't use \def but
+% \newcommand{}{}
+%
+% Insert the name of "your journal" with
+% \journalname{myjournal}
+%
+\begin{document}
+
+\title{A comprehensive framework to capture the arcana of neuroimaging
+analysis%\thanks{Grants or other notes
+%about the article that should go on the front page should be
+%placed here. General acknowledgments should be placed at the end of the article.}
+}
+
+%\titlerunning{Short form of title}        % if too long for running head
+
+\author{
+	Thomas G. Close \and
+	Phillip G. D. Ward  \and
+	Francesco Sforazzini  \and
+	Wojtek Goscinski  \and
+	Zhaolin Chen  \and
+	Gary F. Egan  \and
+}
+
+%\authorrunning{Short form of author list} % if too long for running head
+
+\institute{F. Author \at
+              first address \\
+              \email{tom.close@monash.edu}           %  \\
+%             \emph{Present address:} of F. Author  %  if needed
+           \and
+           S. Author \at
+              second address
+}
+
+\date{Received: date / Accepted: date}
+% The correct dates will be entered by the editor
+
+\maketitle
+
+\begin{abstract}
+Insert your abstract here. Include keywords, PACS and mathematical
+subject classification numbers as needed.
+\keywords{First keyword \and Second keyword \and More}
+% \PACS{PACS code1 \and PACS code2 \and more}
+% \subclass{MSC code1 \and MSC code2 \and more}
+\end{abstract}
+
+\section{Introduction}
+\label{intro}
 
@@
 et. al. 2012), the arcana of neuroimaging analysis is substantial due to
-the range of available tools, tunable parameters, and imaging sequences
+the range of available tools, tuneable parameters, and imaging sequences
 involved (Cusack et. al. 2015). The distribution of complete
@@
 
-\hypertarget{methods}{%
-\section{Methods}\label{methods}}
-
-\hypertarget{framework-overview}{%
-\subsection{Framework overview}\label{framework-overview}}
+\section{Methods}
+\label{methods}
+
+\subsection{Framework overview}
+\label{framework-overview}
 
@@
 
-\includegraphics[width=3.55074in,height=3.16146in]{media/image23.png}
+%\includegraphics[width=3.55074in,height=3.16146in]{media/image23.png}
 
@@
 
-\includegraphics[width=6.27083in,height=3.15278in]{media/image33.png}
+%\includegraphics[width=6.27083in,height=3.15278in]{media/image33.png}
 
@@
 
-\hypertarget{analysis-design-study-classes}{%
-\subsection{Analysis design: Study
-classes}\label{analysis-design-study-classes}}
+\subsection{Analysis design: Study classes}
+\label{analysis-design-study-classes}
 
@@
 
-\hypertarget{data-and-parameter-specification-tables}{%
 \subsubsection{Data and parameter specification
-tables}\label{data-and-parameter-specification-tables}}
+tables}
+\label{data-and-parameter-specification-tables}
 
@@
 
-\includegraphics[width=5.74851in,height=6.07813in]{media/image27.png}
+%\includegraphics[width=5.74851in,height=6.07813in]{media/image27.png}
 
@@
 
-\hypertarget{workflow-design}{%
-\subsubsection{Workflow design}\label{workflow-design}}
+\subsubsection{Workflow design}
+\label{workflow-design}
 
@@
 
-\includegraphics[width=5.33854in,height=4.21623in]{media/image35.png}
+%\includegraphics[width=5.33854in,height=4.21623in]{media/image35.png}
 
@@
 proposed format for Nipype v2.0
-(\href{https://github.com/nipy/nipype/issues/2539}{{https://github.com/nipy/nipype/issues/2539}}),
+(\href{https://github.com/nipy/nipype/issues/2539}{https://github.com/nipy/nipype/issues/2539}),
 and will be updated as Nipype v2.0 is developed and upstream
@@
 
-\includegraphics[width=6.27083in,height=2in]{media/image7.png}
+%\includegraphics[width=6.27083in,height=2in]{media/image7.png}
 
@@
 
-\hypertarget{extension-and-specialisation-by-class-inheritance}{%
-\subsubsection{Extension and specialisation by class
-inheritance}\label{extension-and-specialisation-by-class-inheritance}}
+\subsubsection{Extension and specialisation by class inheritance}
+\label{extension-and-specialisation-by-class-inheritance}
 
@@
 
-\hypertarget{implementing-multi-modal-studies}{%
 \subsubsection{Implementing multi-modal
-studies}\label{implementing-multi-modal-studies}}
+studies}
+\label{implementing-multi-modal-studies}
 
@@
 
-\includegraphics[width=3.86429in,height=4.70313in]{media/image20.png}
+%\includegraphics[width=3.86429in,height=4.70313in]{media/image20.png}
 
@@
 
-\includegraphics[width=6.27083in,height=4.69444in]{media/image21.png}
+%\includegraphics[width=6.27083in,height=4.69444in]{media/image21.png}
 
@@
 
-\includegraphics[width=6.27083in,height=3.94444in]{media/image36.png}\textbf{Figure
-8} - Example application of Study class to a dataset stored in an XNAT
-repository. Once the Study object has been initialised potential
-derivatives of the Study can be requested, and will be generated and
-stored in the repository if already present.
+%\includegraphics[width=6.27083in,height=3.94444in]{media/image36.png}\textbf{Figure 8} - Example application of Study class to a dataset stored in an XNAT
+%repository. Once the Study object has been initialised potential
+%derivatives of the Study can be requested, and will be generated and
+%stored in the repository if already present.
 
@@
 
-\hypertarget{study-inputs}{%
-\subsubsection{Study inputs}\label{study-inputs}}
+\subsubsection{Study inputs}
+\label{study-inputs}
 
@@
 
-\hypertarget{processor-modules}{%
-\subsubsection{Processor modules}\label{processor-modules}}
+\subsubsection{Processor modules}
+\label{processor-modules}
 
@@
 
-\hypertarget{results}{%
-\section{Results}\label{results}}
+\section{Results}
+\label{results}
 
@@
 
-\includegraphics[width=3.82849in,height=6.85938in]{media/image28.png}
+%\includegraphics[width=3.82849in,height=6.85938in]{media/image28.png}
 
@@
 
-\includegraphics[width=4.29167in,height=7.43818in]{media/image32.png}
+%\includegraphics[width=4.29167in,height=7.43818in]{media/image32.png}
 
@@
 
-\includegraphics[width=6.228in,height=4.72396in]{media/image22.png}
+%\includegraphics[width=6.228in,height=4.72396in]{media/image22.png}
 
@@
 
-\includegraphics[width=6.27083in,height=4.18056in]{media/image34.png}
+%\includegraphics[width=6.27083in,height=4.18056in]{media/image34.png}
 
@@
 
-\includegraphics[width=6.27083in,height=2.09722in]{media/image30.png}
+%\includegraphics[width=6.27083in,height=2.09722in]{media/image30.png}
 
@@
 
-\hypertarget{discussion}{%
-\section{Discussion}\label{discussion}}
+\section{Discussion}
+\label{discussion}
 
@@
 
-\hypertarget{conclusion}{%
-\section{Conclusion}\label{conclusion}}
+\section{Conclusion}
+\label{conclusion}
 
@@
 
-\hypertarget{references}{%
-\section{References}\label{references}}
-
-Abadi, M., Barham, P., Chen, J., Chen, Z., Davis, A., Dean, J., Devin,
-M., Ghemawat, S., Irving, G., Isard, M., Kudlur, M., Levenberg, J.,
-Monga, R., Moore, S., Murray, D. G., Steiner, B., Tucker, P., Vasudevan,
-V., Warden, P., Wicke, M., Yu, Y., Zheng, X.. (2016). TensorFlow: A
-System for Large-Scale Machine Learning TensorFlow: A system for
-large-scale machine learning. \emph{12th USENIX Symposium on Operating
-Systems Design and Implementation (OSDI '16)}, 265--284.
-\href{https://doi.org/10.1038/nn.3331}{{https://doi.org/10.1038/nn.3331}}
-
-Achterberg, H. C., Koek, M., \& Niessen, W. J. (2016). Fastr: A Workflow
-Engine for Advanced Data Flows in Medical Image Analysis.
-\emph{Frontiers in ICT}, 3(August), 1--11.
-\href{https://doi.org/10.3389/fict.2016.00015}{{https://doi.org/10.3389/fict.2016.00015}}
-
-Amstutz, P., Crusoe, M. R., Tijanić, N., Chapman, B., Chilton, J.,
-Heuer, M., Kartashov, A., Leehr, D., Ménager, H., Nedeljkovich, M.,
-Scales, M., Soiland-Reyes, S., Stojanovic, L. (2016). Common workflow
-language, v1. 0. Figshare.
-doi:\href{https://doi.org/10.6084/m9.figshare.3115156.v2}{{10.6084/m9.figshare.3115156.v2}}
-
-Avants, B. B., Tustison, N. J., Song, G., Cook, P. A., Klein, A., \&
-Gee, J. C. (2011). A reproducible evaluation of ANTs similarity metric
-performance in brain image registration. \emph{NeuroImage},
-\emph{54}(3), 2033--2044.
-\href{https://doi.org/10.1016/J.NEUROIMAGE.2010.09.025}{{https://doi.org/10.1016/J.NEUROIMAGE.2010.09.025}}
-
-Book, G. A., Anderson, B. M., Stevens, M. C., Glahn, D. C., Assaf, M.,
-\& Pearlson, G. D. (2013). Neuroinformatics Database (NiDB)--a modular,
-portable database for the storage, analysis, and sharing of neuroimaging
-data. \emph{Neuroinformatics}, \emph{11}(4), 495-505.
-
-Cox, R. W. (1996): AFNI: Software for analysis and visualization of
-functional magnetic resonance neuroimages. \emph{Computers and
-Biomedical Research}, 29:162-173.
-
-Cusack R., Vicente-Grabovetsky A., Mitchell D.J., Wild C.J., Auer T.,
-Linke A.C., Peelle J.E. (2015) Automatic analysis (aa): Efficient
-neuroimaging workflows and parallel processing using Matlab and XML.
-\emph{Frontiers in Neuroinformatics} 8:90.
-
-Das, S., Zijdenbos, A. P., Harlap, J., Vins, D., \& Evans, A. C. (2012).
-LORIS: a web-based data management system for multi-center studies.
-\emph{Frontiers in Neuroinformatics}, 5(January), 1--11.
-\href{https://doi.org/10.3389/fninf.2011.00037}{{https://doi.org/10.3389/fninf.2011.00037}}
-
-Esteban O. (2018) FMRIPrep: a robust preprocessing pipeline for
-functional MRI. \emph{bioRxiv.} 306951;
-doi:\href{https://doi.org/10.1101/306951}{{10.1101/306951}}
-
-Friston K. (2007): Statistical parametric mapping. In:.
-\emph{Statistical Parametric Mapping}. Elsevier. pp 10--31.
-
-Furlani, J. (1991). Modules: Providing a flexible user environment.
-\emph{Proceedings of the Fifth Large Installation Systems Administration
-Conference (LISA V)}, (1), 141--152.
-
-Gorgolewski K.J. et al. (2011), `Nipype: A Flexible, Lightweight and
-Extensible Neuroimaging Data Processing Framework in Python'.
-\emph{Frontiers in Neuroinformatics}, vol. 5.
-
-Gorgolewski K. J. et al. (2016): `The brain imaging data structure, a
-format for organizing and describing outputs of neuroimaging
-experiments'. \emph{Scientific Data}, vol. 3.
-
-Goscinski, W. J., P. McIntosh, U. C. Felzmann, A. Maksimenko, C. J.
-Hall, T. Gureyev, D. Thompson, A. Janke, G. Galloway, N. E. B. Killeen,
-P. Raniga, O. Kaluza, A. Ng, G. Poudel, D. Barnes, T. Nguyen, P.
-Bonnington and G. F. Egan (2014). "The Multi-modal Australian ScienceS
-Imaging and Visualisation Environment (MASSIVE) high performance
-computing infrastructure: applications in neuroscience and
-neuroinformatics research." \emph{Frontiers in Neuroinformatics} 8.
-
-Halchenko, Y., Hanke, M., Poldrack, B., Meyer, K., Debanjum, Alteva, G.,
-\ldots{} Feilong Ma. (2018). Datalad/Datalad 0.10.2. Zenodo.
-https://doi.org/10.5281/zenodo.808846
-
-Kennedy, D. N. (2018). Neuroimaging Neuroinformatics: Sample Size and
-Other Evolutionary Topics. \emph{Neuroinformatics}, 16(2), 149--150.
-\href{https://doi.org/10.1007/s12021-018-9379-8}{{https://doi.org/10.1007/s12021-018-9379-8}}
-
-Marcus D. S. et al. (2007), `The extensible neuroimaging archive
-toolkit'. \emph{Neuroinformatics}, vol. 5, pp. 11--33.
-
-Moore, D., Budd, R., \& Wright, W. (2008). \emph{Professional Python
-Frameworks: Web 2.0 Programming with Django and Turbogears}. John Wiley
-\& Sons.
-
-Paszke, A., Chintala, S., Collobert, R., Kavukcuoglu, K., Farabet, C.,
-Bengio, S., ... \& Mariethoz, J. Pytorch: Tensors and dynamic neural
-networks in python with strong gpu acceleration, may 2017.
-
-Raymond, E. S. (1999). The Cathedral and the Bazaar. O'Reilly Media.
-ISBN 1-56592-724-9. pp. 30.
-
-Scott, A., Courtney, W., Wood, D., De la Garza, R., Lane, S., Wang, R.,
-... \& Calhoun, V. D. (2011). COINS: an innovative informatics and
-neuroimaging tool suite built for large heterogeneous datasets.
-\emph{Frontiers in neuroinformatics}, \emph{5}, 33.
-
-Smith S. M. et al. (2004): Advances in functional and structural MR
-image analysis and implementation as FSL. \emph{NeuroImage} vol. 23, pp.
-S208--S219.
-
-Sudlow C. et al. (2015) UK Biobank: An Open Access Resource for
-Identifying the Causes of a Wide Range of Complex Diseases of Middle and
-Old Age. \emph{PLoS Medicine};12:e1001779.
-
-Schreiber J. et al (2018) `Using a Multi-Petaflop Supercomputer for
-Pushing Neuroimaging Analytics to the Next Level', In: \emph{Proceedings
-of Organisation for Human Brain Mapping 2018}, Singapore, Singapore
-
-Tournier, J. D., Calamante, F., \& Connelly, A. (2010). Improved
-probabilistic streamlines tractography by 2nd order integration over
-fibre orientation distributions. In \emph{Proceedings of the
-international society for magnetic resonance in medicine} (Vol. 18, p.
-1670).
-
-Tournier J.D. et al. (2012): `MRtrix: Diffusion tractography in crossing
-fiber regions'. \emph{International Journal of Imaging Systems and
-Technology}, vol. 22, pp. 53--66.
-
-Thompson P.M. et al. (2014): `The ENIGMA Consortium: large-scale
-collaborative analyses of neuroimaging and genetic data'. \emph{Brain
-Imaging and Behavior}, vol. 8, pp.153--182.
-
-Van Essen D.C. et al. (2012): `The Human Connectome Project: A data
-acquisition perspective'. \emph{NeuroImage}, vol. 62, pp. 2222--2231.
-
-Ward, P. G. D., Ferris, N. J., Raniga, P., Dowe, D. L., Ng, A. C. L.,
-Barnes, D. G., \& Egan, G. F. (2018). Combining images and anatomical
-knowledge to improve automated vein segmentation in MRI. NeuroImage,
-165, 294--305.
-\href{https://doi.org/10.1016/J.NEUROIMAGE.2017.10.049}{{https://doi.org/10.1016/J.NEUROIMAGE.2017.10.049}}
-
-White, T. (2012). \emph{Hadoop: The definitive guide}. O'Reilly Media,
-Inc..
-
-Yacoub, S. M., \& Ammar, H. H. (2004). \emph{Pattern-oriented analysis
-and design: composing patterns to design software systems}.
-Addison-Wesley Professional.
-
-\hypertarget{supplementary-material}{%
-\section{Supplementary Material}\label{supplementary-material}}
-
-\includegraphics[width=5.88542in,height=6.21875in]{media/image24.png}
-
-\textbf{Figure S.1} - First section of the definition of the
-\emph{ArcanaPaper} Study class. ArcanaPaper implements the analysis
-performed for this manuscript. ArcanaPaper is a \emph{MultiStudy} with
-two sub-studies, a T2*-weighted/T1-weighted multi-study and a dMRI
-study. Two default parameters of the global tracking pipeline in the
-dMRI study are overridden to reduce the number of tracks created for
-visualisation purposes. The class inherits from the
-\emph{ImageDisplayMixin} class to include methods to display slices of
-the derived images.
-
-\includegraphics[width=5.89583in,height=5.38542in]{media/image25.png}\textbf{Figure
-S.2 -} Method in ArcanaPaper class to generate Figure 11 of this
-manuscript. SWI, QSM and vein mask derivatives are generated on demand
-if they don't already exist in the repository by the \emph{data} method.
-\emph{display\_slice\_panel} and \emph{save\_or\_show} methods from the
-\emph{nianalysis.plot.ImageDisplayMixin} base class are used to display
-the generated filesets.
-
-\includegraphics[width=5.83333in,height=4.58333in]{media/image31.png}
-
-\textbf{Figure S.3 -} Method in ArcanaPaper class to generate Figure 12
-of this manuscript. FA and ADC derivatives are generated on demand if
-they don't already exist in the repository by the \emph{data} method.
-\emph{display\_slice\_panel} and \emph{save\_or\_show} methods from the
-\emph{nianalysis.plot.ImageDisplayMixin} base class are used to display
-the generated filesets.
-
-\includegraphics[width=5.98958in,height=5.76042in]{media/image26.png}
-
-\textbf{Figure S.4 -} Method in ArcanaPaper class to generate Figure 13
-of this manuscript. Global tracks and FA are derived on demand if they
-don't already exist in the repository by the \emph{data} method. Uses
-the \emph{display\_tcks\_with\_mrview} method in the
-\emph{nianalysis.plot.ImageDisplayMixin} class to display streamlines on
-a background of a fractional anisotropy (FA) map using MRtrix's
-\emph{mrview} command.
-
-\includegraphics[width=6.125in,height=6.78125in]{media/image29.png}
-
-\textbf{Figure S.5 -} Instantiation of the specific study class to a
-dataset stored on the local system. Images for Figures 11, 12 and 13 of
-this manuscript are generated by eponymous methods of the study. Entries
-in the study's data specification are matched to data in the repository
-using \emph{FilesetSelector} objects. The use of \emph{LinearProcessor}
-specifies that derivatives are derived using a single process on the
-local system. Equivalent figures can be generated for alternative
-datasets by specifying a different repository and inputs.
+% Your text comes here. Separate text sections with
+% \section{Section title}
+% \label{sec:1}
+% Text with citations \cite{RefB} and \cite{RefJ}.
+% \subsection{Subsection title}
+% \label{sec:2}
+% as required. Don't forget to give each section
+% and subsection a unique label (see Sect.~\ref{sec:1}).
+% \paragraph{Paragraph headings} Use paragraph headings as needed.
+% \begin{equation}
+% a^2+b^2=c^2
+% \end{equation}
+
+% For one-column wide figures use
+\begin{figure}
+% Use the relevant command to insert your figure file.
+% For example, with the graphicx package use
+  \includegraphics{example.eps}
+% figure caption is below the figure
+\caption{Please write your figure caption here}
+\label{fig:1}       % Give a unique label
+\end{figure}
+%
+% For two-column wide figures use
+\begin{figure*}
+% Use the relevant command to insert your figure file.
+% For example, with the graphicx package use
+  \includegraphics[width=0.75\textwidth]{example.eps}
+% figure caption is below the figure
+\caption{Please write your figure caption here}
+\label{fig:2}       % Give a unique label
+\end{figure*}
+%
+% For tables use
+\begin{table}
+% table caption is above the table
+\caption{Please write your table caption here}
+\label{tab:1}       % Give a unique label
+% For LaTeX tables use
+\begin{tabular}{lll}
+\hline\noalign{\smallskip}
+first & second & third  \\
+\noalign{\smallskip}\hline\noalign{\smallskip}
+number & number & number \\
+number & number & number \\
+\noalign{\smallskip}\hline
+\end{tabular}
+\end{table}
+
+%\begin{acknowledgements}
+%If you'd like to thank anyone, place your comments here
+%and remove the percent signs.
+%\end{acknowledgements}
+
+% BibTeX users please use one of
+%\bibliographystyle{spbasic}      % basic style, author-year citations
+%\bibliographystyle{spmpsci}      % mathematics and physical sciences
+%\bibliographystyle{spphys}       % APS-like style for physics
+%\bibliography{}   % name your BibTeX data base
+
+% Non-BibTeX users please use
+\begin{thebibliography}{}
+%
+% and use \bibitem to create references. Consult the Instructions
+% for authors for reference list style.
+%
+\bibitem{RefJ}
+% Format for Journal Reference
+Author, Article title, Journal, Volume, page numbers (year)
+% Format for books
+\bibitem{RefB}
+Author, Book title, page numbers. Publisher, place (year)
+% etc
+\end{thebibliography}
+
+\end{document}
+% end of file template.tex

### 2018-10-11 examples/manuscript.py

@@ -1,0 +1,46 @@
+from arcana import (Study, StudyMetaClass, AcquiredFilesetSpec, FilesetSpec,
+                    AcquiredFieldSpec, FieldSpec, ParameterSpec, SwitchSpec,
+                    FilesetCollection, XnatRepository, Fileset)
+from arcana.data.file_format.standard import text_format
+from nianalysis.file_format import (
+    nifti_gz_format, dicom_format, nifti_format, analyze_format)
+
+STD_IMAGE_FORMATS = (dicom_format, nifti_format, nifti_gz_format,
+                     analyze_format)
+
+template_repo = XnatRepository('http://central.xnat.org', 'SAMPLE_TEMPLATES')
+template1_default = FilesetCollection(Fileset)
+
+
+class ExampleStudy(Study, metaclass=StudyMetaClass):
+
+    add_data_specs = [
+        # Acquired file sets
+        AcquiredFilesetSpec('acquired_file1', text_format),
+        AcquiredFilesetSpec('acquired_file2', IMAGE_FORMATS),
+        # Acquired fields
+        AcquiredFieldSpec('acquired_field1', int, frequency='per_subject'),
+        AcquiredFieldSpec('acquired_field2', str,),
+        # "Acquired" file set with default value. Useful for standard templates
+        AcquiredFilesetSpec('template1', IMAGE_FORMATS, frequency='per_study',
+                            default=template1_default),
+        # Derived file sets
+        FilesetSpec('derived_file1', text_format, 'pipeline1'),
+        FilesetSpec('derived_file2', nifti_gz_format, 'pipeline1'),
+        FilesetSpec('derived_file3', text_format, 'pipeline2'),
+        FilesetSpec('derived_file4', dicom_format, 'pipeline3'),
+        FilesetSpec('derived_file5', nifti_gz_format, 'pipeline3',
+                    frequency='per_subject'),
+        FilesetSpec('derived_file6', text_format, 'pipeline4',
+                    frequency='per_visit'),
+        # Derived fields
+        FieldSpec('derived_field4', float, 'pipeline2'),
+        FieldSpec('derived_field7', int, 'pipeline4',
+                  frequency='per_study')]
+
+    add_parameter_specs = [
+        # Standard parameters
+        ParameterSpec('parameter1', 10),
+        ParameterSpec('parameter2', 25.8),
+        # Parameters that specify a qualitative change in the analysis
+        SwitchSpec('pipeline_tool', 'toolA', ('toolA', 'toolB'))]

### 2018-10-11 manuscript/manuscript.tex
added all figures to latex document

@@
 \usepackage{booktabs}
-%
+
 % \usepackage{mathptmx}      % use Times fonts if available on your TeX system
@@
 % \newcommand{}{}
+
+\newcommand{\D}{...}
+\newcommand*{\affaddr}[1]{#1}
+\newcommand*{\affmark}[1][*]{\textsuperscript{#1}}
+
 %
@@
 \author{
+	Thomas G. Close\affmark[1,2]\and
+	Phillip G. D. Ward\affmark[1,3,4] \and
+	Francesco Sforazzini\affmark[1] \and
+	Wojtek Goscinski\affmark[6] \and
+	Zhaolin Chen\affmark[1,5] \and
+	Gary F. Egan\affmark[1,3,4]
+}
+
+\authorrunning{
         Thomas G. Close \and
@@
 	Zhaolin Chen  \and
-	Gary F. Egan  \and
+	Gary F. Egan  \and} % if too long for running head
+
+\institute{
+	Thomas G. Close \at
+	 \email{tom.close@monash.edu} \\ \\
+         \affaddr{\affmark[1]Monash Biomedical Imaging, Monash University, Melbourne, Australia} \\
+         \affaddr{\affmark[2]Australian National Imaging Facility, Australia} \\
+         \affaddr{\affmark[3]Australian Research Council Centre of Excellence for integrative Brain Function, Melbourne, Australia} \\
+         \affaddr{\affmark[4]Monash Institute of Cognitive and Clinical Neurosciences, Monash University, Melbourne, Australia} \\
+         \affaddr{\affmark[5]Department of Electrical and Computer Systems Engineering, Monash University, Melbourne, Australia} \\
+         \affaddr{\affmark[6]Monash eResearch Centre, Monash University, Melbourne, Australia} \\
 }
 
-%\authorrunning{Short form of author list} % if too long for running head
-
-\institute{F. Author \at
-              first address \\
-              \email{tom.close@monash.edu}           %  \\
-%             \emph{Present address:} of F. Author  %  if needed
-           \and
-           S. Author \at
-              second address
-}
-
-\date{Received: date / Accepted: date}
+%\date{Received: date / Accepted: date}
 % The correct dates will be entered by the editor
@@
 
-%\includegraphics[width=3.55074in,height=3.16146in]{media/image23.png}
-
-\textbf{Figure 1} - Example study. Blue boxes represent acquired (input)
+\begin{figure*}
+  \begin{center}
+    \includegraphics[width=0.55\textwidth]{figures/example_study}
+  \caption{Example study. Blue boxes represent acquired (input)
 data (filesets or fields) stored in a repository and green derivatives
@@
 derivatives. Arrows represent data flows, i.e., inputs and outputs to
-pipelines.
+pipelines}
+  \end{center}
+\label{fig:example_study}
+\end{figure*}
 
@@
 
-%\includegraphics[width=6.27083in,height=3.15278in]{media/image33.png}
-
-\textbf{Figure 2} - Simplified Unified Modelling Language (UML) diagram
+\begin{figure*}
+  \begin{center}
+    \includegraphics[width=0.9\textwidth]{figures/simplified_arcana_uml}
+  \caption{Unified Modelling Language (UML) diagram
 of information flow in the Arcana framework. Boxes: Python classes,
@@
 intermediate derivatives. After the derivatives are pushed back to the
-repository.
+repository.}
+\end{center}
+\label{fig:simple_uml}
+\end{figure*}
 
@@
 
-%\includegraphics[width=3.86429in,height=4.70313in]{media/image20.png}
-
-\textbf{Figure 6} - Example MultiStudy. Blue boxes represent acquired
+\begin{figure*}
+  \begin{center}
+    \includegraphics[width=0.775\textwidth]{figures/example_multi_study}
+  \caption{Example MultiStudy. Blue boxes represent acquired
 (input) data (filesets or fields) and green derivatives. Orange ovals
@@
 pipeline that generates that derivative in the sub-study will not run
-unless it generates other required derivatives (e.g. \emph{Pipeline 3}).
+unless it generates other required derivatives (e.g. \emph{Pipeline 3} in
+\emph{Sub-Study2})}
+\end{center}
+\label{fig:example_multi_study}
+\end{figure*}
 
@@
 
-%\includegraphics[width=6.27083in,height=4.69444in]{media/image21.png}
-
-\textbf{Figure 7} - Detailed Unified Modelling Language (UML) diagram of
+\begin{figure*}
+  \begin{center}
+    \includegraphics[width=\textwidth]{figures/full_arcana_uml}
+  \caption{Detailed Unified Modelling Language (UML) diagram of
 information flow in the Arcana framework. Boxes: Python classes
@@
 processed, and then the derivatives are pushed back to the repository.
-Repositories can be of plain directories, or BIDS or XNAT repositories.
+Repositories can be of plain directories, or BIDS or XNAT repositories}
+\label{fig:full_uml}
+\end{center}
+\end{figure*}
 
@@
 
-%\includegraphics[width=6.27083in,height=3.94444in]{media/image36.png}\textbf{Figure 8} - Example application of Study class to a dataset stored in an XNAT
-%repository. Once the Study object has been initialised potential
-%derivatives of the Study can be requested, and will be generated and
-%stored in the repository if already present.
+%\includegraphics[width=6.27083in,height=3.94444in]{media/image36.png}
+
+Listing - Example application of Study class to a dataset stored in an XNAT
+repository. Once the Study object has been initialised potential
+derivatives of the Study can be requested, and will be generated and
+stored in the repository if already present.
 
@@
 and per\_study data in \emph{\textless{}root\_dir\textgreater{}/}all/all
-(Table 1).
-
-\begin{longtable}[]{@{}llll@{}}
-\toprule
-& \textbf{Plain-directory} & \textbf{BIDS} &
-\textbf{XNAT}\tabularnewline
-\midrule
-\endhead
-\textbf{Derivatives} & \emph{/subject/visit/study} &
-/derivatives/study/subject/visit &
-/subject/\emph{visit\_study}\tabularnewline
-\textbf{Fields} & \emph{.../}\_\_fields\_\_\emph{.json} &
-\emph{.../}\_\_fields\_\_\emph{.}json & ``custom
-variables''\tabularnewline
-\textbf{Provenance} & \emph{.../}\_\_prov\_\_\emph{/pipeline.}json &
-\emph{.../}\_\_prov\_\_\emph{/pipeline.}json &
-.../scans/\_\_prov\_\_/resources/\emph{pipeline/}prov\emph{.}json\tabularnewline
-\textbf{per\_subject} & \emph{/subject/}all\emph{/study} &
-\emph{/derivatives/study/subject/}all &
-\emph{/subject/}all\_\emph{study}\tabularnewline
-\textbf{per\_visit} & \emph{/}all\emph{/visit/study} &
-\emph{/derivatives/study/}all\emph{/visit} &
-\emph{/}all\emph{/visit\_study}\tabularnewline
-\textbf{per\_study} & \emph{/}all\emph{/}all\emph{/study} &
-\emph{/derivatives/study/}all\emph{/}all &
-\emph{/}all\emph{/}all\_\emph{study}\tabularnewline
-\bottomrule
-\end{longtable}
-
-\textbf{Table 1} - Storage locations of derived data for each repository
+(Table \ref{tbl:repo-structure}).
+
+\begin{table}
+% table caption is above the table
+\caption{Storage locations of derivative and provenance data for each repository
 type. Derivatives are stored in separate namespaces for each Study
 instance to enable multiple analyses on the same datasets with different
-parameterisations. `...' refers to the \emph{Derivatives}
-directory/xnat:MrSession.
+parameterisations. Where `...' = \emph{derivatives}
+directory/XNAT session, \emph{subj} = subject ID, \emph{vis} = visit ID,
+\emph{study} = name of the Study instance, and \emph{pl} = name
+of pipeline.}
+\label{tbl:repo-structure}       % Give a unique label
+% For LaTeX tables use
+\begin{tabular}{llll}
+\hline\noalign{\smallskip}
+\textbf{Type} & Plain-directory & BIDS & XNAT  \\
+\noalign{\smallskip}\hline\noalign{\smallskip}
+\textbf{Deriv.} & /\emph{subj}/\emph{vis}/\emph{study} & /derivatives/\emph{study}/\emph{subj}/\emph{vis} & /\emph{subj}/\emph{vis}\_\emph{study} \\
+\textbf{Fields} & \D/\_\_fields\_\_.json & \D/\_\_fields\_\_.json & ``custom vars.'' \\
+\textbf{Prov.} & \D/\_\_prov\_\_/\emph{pl}.json & \D/\_\_prov\_\_/\emph{pl}.json & \D/\_\_prov\_\_/\emph{pl}/prov\emph{.}json \\
+\noalign{\smallskip}\hline
+\end{tabular}
+\end{table}
 
@@
 
-\textbf{Figure 9} - Example diffusion MRI (dMRI) study, which can derive
+\begin{figure*}
+  \begin{center}
+    \includegraphics[width=0.55\textwidth]{figures/dmri_study}
+  \caption{Example diffusion MRI (dMRI) study, which can derive
 tensor metrics, fractional anisotropy (FA) and apparent diffusion
@@
 branches of analysis can be performed using the same intermediate
-derivatives: FA and ADC and/or streamlines fibre tracking.
+derivatives: FA and ADC and/or streamlines fibre tracking.}
+\end{center}
+\label{fig:dmri_study}
+\end{figure*}
 
@@
 
-\textbf{Figure 10} - Combined T1-weighted/T2*-weighted multi-study,
+\begin{figure*}
+  \begin{center}
+    \includegraphics[width=0.775\textwidth]{figures/t2star_t1_study}
+  \caption{Combined T2*-weighted/T1-weighted multi-study,
 which can derive vein masks by combining Quantitative Susceptibility
@@
 composite-vein image. The brain mask from the T1-weighted sub-study is
-combined with the composite vein image to produce the vein mask.
+combined with the composite vein image to produce the vein mask.}
+  \end{center}
+\label{fig:t2star_t1_study}
+\end{figure*}
 
@@
 
-Figure 11 displays composite vein images and vein masks for the healthy
+Figure \ref{fig:veins} displays composite vein images and vein masks for the healthy
 volunteer along with the SWI and QSM intermediate derivatives and the
@@
 
-\textbf{Figure 11 -} Vein image (\emph{right column}) constructed by
+\begin{figure*}
+  \begin{center}
+    \includegraphics[width=\textwidth]{figures/veins}
+  \caption{Vein image (\emph{right column}) constructed by
 combining susceptibility weighted imaging (SWI) (\emph{left column}),
@@
 \emph{Top row}: sagittal slices. \emph{Middle row}: axial slices.
-\emph{Bottom row}: coronal slices.
-
-Figure 12 displays the FA and ADC maps derived from the diffusion MRI
+\emph{Bottom row}: coronal slices.}
+  \end{center}
+\label{fig:veins}
+\end{figure*}
+
+Figure \ref{fig:fa_adc}  displays the FA and ADC maps derived from the diffusion MRI
 acquisition. The FA map shows high intensity in known white matter
@@
 
-\textbf{Figure 12 -} Fractional Anisotropy (FA) \emph{(top row)} and
+\begin{figure*}
+  \begin{center}
+    \includegraphics[width=\textwidth]{figures/fa_adc}
+  \caption{Fractional Anisotropy (FA) \emph{(top row)} and
 Apparent Diffusion Coefficient (ADC) (\emph{bottom rowI)} derived from
@@
 \emph{Middle column:} coronal midline slices. \emph{Left column}:
-sagittal midline slices.
-
-Figure 12 displays the global tractography derived from the dMRI
+sagittal midline slices.}
+  \end{center}
+\label{fig:fa_adc}
+\end{figure*}
+
+Figure \ref{fig:tractography} displays the global tractography derived from the dMRI
 acquisition. The streamlines follow well known white matter tracts such
@@
 
-\textbf{Figure 13 -} Global tractography performed using the MRtrix
+\begin{figure*}
+  \begin{center}
+    \includegraphics[width=\textwidth]{figures/tractography}
+  \caption{Global tractography performed using the MRtrix
 toolbox. Probabilistic streamlines generated with the iFOD2 algorithm
@@
 slice. \emph{Middle panel:} coronal midline slice. \emph{Left panel}:
-sagittal midline slice.
+sagittal midline slice.}
+  \end{center}
+\label{fig:tractography}
+\end{figure*}
 
@@
 
+\section*{Acknowlegements}
+We would like to acknowledge the generous support of
+
 % Your text comes here. Separate text sections with

### 2018-10-11 paper.py

@@ -21,12 +21,12 @@ class ArcanaPaper(MultiStudy, ImageDisplayMixin,
 
     add_parameter_specs = [
         ParameterSpec(
-            'fig12_13_slice_offset', (4, 0, 0),
-            desc=("Offset the sagittal slices of Figure 11 & 12 so they "
+            'dmri_fig_slice_offset', (4, 0, 0),
+            desc=("Offset the sagittal slices of dMRI figures so they "
                   "intersect a cerebral hemisphere instead of the "
                   "midline between the hemispheres"))]
 
-    def figure11(self, save_path=None, **kwargs):
+    def vein_fig(self, save_path=None, **kwargs):
         """
         Generates an image panel containing the SWI, QSM, vein atlas,
         and vein mask
@@ -54,7 +54,7 @@ class ArcanaPaper(MultiStudy, ImageDisplayMixin,
             # Display or save to file the generated image.
             self.save_or_show(save_path, swi.subject_id, swi.visit_id)
 
-    def figure12(self, save_path=None, **kwargs):
+    def fa_adc_fig(self, save_path=None, **kwargs):
         """
         Generates an image panel containing the derived FA and ADC
         images for each session in the study (typically only one)
@@ -75,12 +75,12 @@ class ArcanaPaper(MultiStudy, ImageDisplayMixin,
             self.display_slice_panel(
                 (fa, adc),
                 row_kwargs=({'vmax': 1.0}, {}),
-                offset=self.parameter('fig12_13_slice_offset'),
+                offset=self.parameter('dmri_fig_slice_offset'),
                 **kwargs)
             # Display or save to file the generated image.
             self.save_or_show(save_path, fa.subject_id, fa.visit_id)
 
-    def figure13(self, save_path=None, **kwargs):
+    def tractography_fig(self, save_path=None, **kwargs):
         """
         Generates dMRI tractography streamlines seeded from without the
         white matter.
@@ -106,7 +106,7 @@ class ArcanaPaper(MultiStudy, ImageDisplayMixin,
             # MRtrix package
             self.display_tcks_with_mrview(
                 tcks=(tck,), backgrounds=(fa,),
-                offset=self.parameter('fig11_12_slice_offset'),
+                offset=self.parameter('tractography_fig_slice_offset'),
                 **kwargs)
             # Display or save to file the generated image.
[…]

### 2018-10-11 manuscript/manuscript.tex
added data_spec listing

@@
 %
+\usepackage{listings}
 \usepackage{graphicx}
+\usepackage{longtable}
 \usepackage{hyperref}
-\usepackage{longtable}
 \usepackage{booktabs}
+
+\lstset{
+    basicstyle=\footnotesize
+}
 
@@
 neuroimaging analyses. \emph{Abstraction of Repository-Centric ANAlysis
-(Arcana)} (http://arcana.readthedocs.io) is a Python framework for
+(Arcana)} \\(\href{http://arcana.readthedocs.io}{http://arcana.readthedocs.io}) is a Python framework for
 designing complex workflows in which modular Nipype pipelines operate on
@@
 
-\textbf{Figure 3} - Example data and parameter specifications. The data
+\begin{figure}
+\lstinputlisting[language=Python]{listings/data_spec.py}
+\caption{Example data and parameter specifications. The data
 specification specifies two ``acquired'' file sets, `one' and `ten' and
@@
 specifications specify a name and default value for free parameters of
-the Study class.
+the Study class}
+\label{list:data_spec}
+\end{figure}
 
@@
 proposed format for Nipype v2.0
-(\href{https://github.com/nipy/nipype/issues/2539}{https://github.com/nipy/nipype/issues/2539}),
+(\href{http://github.com/nipy/nipype/issues/2539}{http://github.com/nipy/nipype/issues/2539}),
 and will be updated as Nipype v2.0 is developed and upstream
 functionality becomes available. Workflow nodes are created from Nipype
-interfaces using the \emph{Pipeline.add(name, interface)} method of the
+interfaces using the \emph{add(name, interface)} method of the
 Pipeline should be used. Once created, the inputs of the node can be set
 explicitly via the node's \emph{inputs} attribute, connected to other
-nodes with the \emph{Pipeline.connect(out\_node, out\_node\_output,
+nodes with the \emph{connect(out\_node, out\_node\_output,
 in\_node, in\_node\_input)} method, or connected to inputs of the
 pipeline. Pipeline inputs and outputs are connected to nodes using the
-\emph{Pipeline.add\_input(spec\_name, node, node\_input)} and
-\emph{Pipeline.add\_output(spec\_name, node, node\_output)} methods,
+\emph{add\_input(spec\_name, node, node\_input)} and
+\emph{add\_output(spec\_name, node, node\_output)} methods,
 respectively.
@@
 frequent data a join node is used. Join nodes that join over subjects or
-visits are created with \emph{Pipeline.add}\_\emph{join\_subjects(name,
-interface, joinfield)} and \emph{Pipeline.add\_join\_visits(name,
+visits are created with \emph{add}\_\emph{join\_subjects(name,
+interface, joinfield)} and \emph{add\_join\_visits(name,
 interface, joinfield)} respectively. As in the underlying Nipype, the
@@
 required by a node they can be connected to the implicit iterator nodes
-with \emph{Pipeline.connect\_subject\_id(node, name)} and
-\emph{Pipeline.connect\_visit\_id} respectively. Note that expansion
+with \emph{connect\_subject\_id(node, name)} and
+\emph{connect\_visit\_id} respectively. Note that expansion
 over iterator sources is handled implicitly by Nipype when nodes with
@@
 Study parameters can be accessed during pipeline construction with the
-\emph{Study.parameter(name)} method. If conditional logic is included in
+\emph{parameter(name)} method. If conditional logic is included in
 the workflow construction that alters the pipeline inputs, outputs or
@@
 parameter. The analysis branch designated by a switch value should be
-tested with \emph{Study.branch(name, ref\_value)} method.
+tested with \emph{branch(name, ref\_value)} method.
 
@@
 unless it generates other required derivatives (e.g. \emph{Pipeline 3} in
-\emph{Sub-Study2})}
+\emph{Sub-Study 2})}
 \end{center}
@@
 per\_subject data for `subj1' would be stored at
-\emph{\textless{}root-dir\textgreater{}/subj1/}all, per\_visit data for
-`visit1' in \emph{\textless{}root-dir\textgreater{}/}all\emph{/visit1},
-and per\_study data in \emph{\textless{}root\_dir\textgreater{}/}all/all
+\emph{\textless{}root\textgreater{}/subj1/}all, per\_visit data for
+`visit1' in \emph{\textless{}root\textgreater{}/}all\emph{/visit1},
+and per\_study data in \emph{\textless{}root\textgreater{}/}all/all
 (Table \ref{tbl:repo-structure}).
@@
 % table caption is above the table
-\caption{Storage locations of derivative and provenance data for each repository
+\caption{Storage locations of derived data for each repository
 type. Derivatives are stored in separate namespaces for each Study
 instance to enable multiple analyses on the same datasets with different
-parameterisations. Where `...' = \emph{derivatives}
-directory/XNAT session, \emph{subj} = subject ID, \emph{vis} = visit ID,
+parameterisations. Where `...' is the location of the
+directory or MrSession that holds the derivatives, \emph{subj} = subject ID, \emph{vis} = visit ID,
 \emph{study} = name of the Study instance, and \emph{pl} = name
@@
 \noalign{\smallskip}\hline\noalign{\smallskip}
-\textbf{Deriv.} & /\emph{subj}/\emph{vis}/\emph{study} & /derivatives/\emph{study}/\emph{subj}/\emph{vis} & /\emph{subj}/\emph{vis}\_\emph{study} \\
-\textbf{Fields} & \D/\_\_fields\_\_.json & \D/\_\_fields\_\_.json & ``custom vars.'' \\
-\textbf{Prov.} & \D/\_\_prov\_\_/\emph{pl}.json & \D/\_\_prov\_\_/\emph{pl}.json & \D/\_\_prov\_\_/\emph{pl}/prov\emph{.}json \\
+\textbf{Derivatives} & /\emph{subj}/\emph{vis}/\emph{study} & /derivatives/\emph{study}/\emph{subj}/\emph{vis} & /\emph{subj}/\emph{vis}\_\emph{study}\\
+\textbf{Fields} & \D/\_\_fields\_\_.json & \D/\_\_fields\_\_.json & MrSession XML \\ 
+\textbf{Provenance} & \D/\_\_prov\_\_/\emph{pl}.json & \D/\_\_prov\_\_/\emph{pl}.json & \D/\_\_prov\_\_/\emph{pl}.json \\
 \noalign{\smallskip}\hline

### 2018-10-11 manuscript/listings/data_spec.py

@@ -1,15 +1,22 @@
-from arcana import (Study, StudyMetaClass, AcquiredFilesetSpec, FilesetSpec,
-                    AcquiredFieldSpec, FieldSpec, ParameterSpec, SwitchSpec,
-                    FilesetCollection, XnatRepository, Fileset)
+import os
+from arcana import (
+    Study, StudyMetaClass, AcquiredFilesetSpec, FilesetSpec,
+    AcquiredFieldSpec, FieldSpec, ParameterSpec, SwitchSpec,
+    FilesetSelector, XnatRepository)
 from arcana.data.file_format.standard import text_format
 from nianalysis.file_format import (
     nifti_gz_format, dicom_format, nifti_format, analyze_format)
 
-STD_IMAGE_FORMATS = (dicom_format, nifti_format, nifti_gz_format,
-                     analyze_format)
+IMAGE_FORMATS = (dicom_format, nifti_format, nifti_gz_format,
+                 analyze_format)
 
-template_repo = XnatRepository('http://central.xnat.org', 'SAMPLE_TEMPLATES')
-template1_default = FilesetCollection(Fileset('sample_atlas', ))
+atlas_repo = XnatRepository(
+    'http://central.xnat.org', 'SAMPLE_TEMPLATES',
+    os.path.expanduser(os.path.join('~', 'work')))
+
+atlas = FilesetSelector(
+    'an_atlas', nifti_gz_format,
+    'an_atlas', frequency='per_study').match(atlas_repo.tree())
 
 
 class ExampleStudy(Study, metaclass=StudyMetaClass):
@@ -19,11 +26,13 @@ class ExampleStudy(Study, metaclass=StudyMetaClass):
         AcquiredFilesetSpec('acquired_file1', text_format),
         AcquiredFilesetSpec('acquired_file2', IMAGE_FORMATS),
         # Acquired fields
-        AcquiredFieldSpec('acquired_field1', int, frequency='per_subject'),
+        AcquiredFieldSpec('acquired_field1', int,
+                          frequency='per_subject'),
         AcquiredFieldSpec('acquired_field2', str,),
-        # "Acquired" file set with default value. Useful for standard templates
-        AcquiredFilesetSpec('template1', IMAGE_FORMATS, frequency='per_study',
-                            default=template1_default),
+        # "Acquired" file set with default value. Useful for
+        # standard templates
+        AcquiredFilesetSpec('template1', IMAGE_FORMATS,
[…]

### 2018-10-12 manuscript/manuscript.tex
porting references to bib tex

@@
 \usepackage{booktabs}
+\usepackage{color}
+
+\definecolor{commentcolour}{rgb}{0.4,0.4,0.4}
+\definecolor{keywordcolour}{rgb}{0.8,0.4,0.4}
+\definecolor{stringcolour}{rgb}{0.1,0.1,0.5}
 
 \lstset{
-    basicstyle=\footnotesize
+    basicstyle=\footnotesize,
+%  captionpos=b,                    % sets the caption-position to bottom
+    language=Python,                 % the language of the code
+    showstringspaces=false,          % underline spaces within strings only
+    stringstyle=\color{stringcolour},     % string literal style
+    commentstyle=\color{commentcolour},    % comment style
+    keywordstyle=\color{keywordcolour}\bfseries,       % keyword style
 }
@@
 readily available in alternative workflow frameworks (Cusack et. al.
-2015; Achterberg et. al. 2016; Amstutz et. al. 2016), and has been used
+2015; \cite{achterberg_fastr:_2016}; Amstutz et. al. 2016), and has been used
 to implement workflows that are robust to differences in fMRI protocols
@@
 
-%\includegraphics[width=5.74851in,height=6.07813in]{media/image27.png}
-
 \begin{figure}
-\lstinputlisting[language=Python]{listings/data_spec.py}
+\lstinputlisting[language=Python, firstline=2, lastline=57]{listings/example_study.py}
 \caption{Example data and parameter specifications. The data
@@
 
-%\includegraphics[width=5.33854in,height=4.21623in]{media/image35.png}
-
-\textbf{Figure 4} - Example pipeline constructor method. Pipelines are
+\begin{figure}
+\lstinputlisting[language=Python, firstline=58, lastline=108]{listings/example_study.py}
+\caption{Example pipeline constructor method. Pipelines are
 created using the \emph{create\_pipeline} method of the Study class.
 Pipeline objects are thin wrappers around Nipype workflows to allow for
-namespace management.
+namespace management}
+\label{list:pipeline_constructor}
+\end{figure}
 
@@
 
-For convenience when the pipeline to construct only consists of a single
-node, the \emph{Study.pipeline\_constructor} classmethod to create the
-method (Figure 5).
-
-%\includegraphics[width=6.27083in,height=2in]{media/image7.png}
-
-\textbf{Figure 5} - Example basic constructor defined using the
-\emph{Study.pipeline\_constructor} convenience method.
-
 \subsubsection{Extension and specialisation by class inheritance}
@@
 
-%\includegraphics[width=6.27083in,height=3.94444in]{media/image36.png}
-
-Listing - Example application of Study class to a dataset stored in an XNAT
+\begin{figure}
+\lstinputlisting[language=Python]{listings/example_application.py}
+\caption{Example application of Study class to a dataset stored in an XNAT
 repository. Once the Study object has been initialised potential
 derivatives of the Study can be requested, and will be generated and
-stored in the repository if already present.
+stored in the repository if already present.}
+\label{list:study_application}
+\end{figure}
 
@@
 \begin{table}
-% table caption is above the table
 \caption{Storage locations of derived data for each repository
@@
 of pipeline.}
-\label{tbl:repo-structure}       % Give a unique label
-% For LaTeX tables use
+\label{tbl:repo-structure} 
 \begin{tabular}{llll}
@@
 
-\begin{longtable}[]{@{}ll@{}}
-\toprule
-\textbf{Method name} & \textbf{Function}\tabularnewline
-\midrule
-\endhead
+\begin{table}
+\caption{Abstract methods in the base Repository class that
+need to be implemented by platform-specific sub-classes.}
+\label{tbl:abstract-repo-methods} 
+\begin{tabular}{ll}
+\hline\noalign{\smallskip}
+\textbf{Method name} & Function \\
+\noalign{\smallskip}\hline\noalign{\smallskip}
 find\_data() & Queries repository to find all existing filesets and
-fields and registers them with the
-\emph{Repository.found\_fileset(fileset)} and
-\emph{Repository.found\_field(field)} methods
-respectively.\tabularnewline
-get\_fileset(Fileset) & Caches the files in a Fileset locally and
-returns the path to the primary file or directory in the
-cache.\tabularnewline
+fields \\
+get\_fileset(Fileset) & Caches file-set (if necessary) and returns the file path. \\
 get\_field(Field) & Retrieves and returns the value of the field from
-the repository\tabularnewline
-put\_fileset(Fileset) & Inserts the files in the Fileset into the
-repository and updates the local cache.\tabularnewline
-put\_field(Field) & Inserts the value of the Field into the
-repository\tabularnewline
-connect() & Opens a connection to the repository (optional). Called by
-methods in the base class before entering outer processing
-loops.\tabularnewline
-disconnect() & Closes connection to repository opened by
-\emph{connect()} method (optional)\tabularnewline
-\bottomrule
-\end{longtable}
-
-\textbf{Table 2} - Abstract methods in the base Repository class that
-need to be implemented by platform-specific sub-classes.
+the repository \\
+put\_fileset(Fileset) & Inserts file-set into the repository and updates cache. \\
+put\_field(Field) & Inserts the value of the Field into the repository \\
+connect() & Opens a connection to the repository (optional). \\
+disconnect() & Closes connection to repository (optional)\\
+\noalign{\smallskip}\hline
+\end{tabular}
+\end{table}
 
@@
 
-\begin{longtable}[]{@{}ll@{}}
-\toprule
-\textbf{\emph{Repocess} flag value} & \textbf{Behaviour when mismatching
-derivatives are found}\tabularnewline
-\midrule
-\endhead
-False (default) & An exception will be raised\tabularnewline
-True & Mismatching derivatives will be reprocessed\tabularnewline
-`Ignore' & Mismatches will be ignored\tabularnewline
-`ignore\_versions' & Version mismatches will be ignored, other
-mismatches cause an exception to be raised\tabularnewline
-`ignore\_versions\_true' & version mismatches will be ignored, other
-mismatches will cause the derivative to be reprocessed\tabularnewline
-\bottomrule
-\end{longtable}
-
-\textbf{Table 3} - Effect of the \emph{reprocess} flag value on the
+\begin{table}
+\caption{Effect of the \emph{reprocess} flag value on the
 behaviour of the study when existing derivatives are found that were
-derived with mismatching inputs and parameters.
+derived with mismatching inputs and parameters.}
+\label{tbl:reprocess-flag} 
+\begin{tabular}{ll}
+\hline\noalign{\smallskip}
+\textbf{Reprocess value} & \textbf{Behaviour on provenance mismatch} \\
+\noalign{\smallskip}\hline\noalign{\smallskip}
+False (default) & Raises an exception \\
+True & Mismatching derivatives will be reprocessed \\
+`ignore' & Mismatches are ignored \\
+`ignore\_versions' & Ignore versions, otherwise raise exception \\
+`ignore\_versions\_true' & Ignore versions, otherwise the derivative will be reprocessed \\
+\noalign{\smallskip}\hline
+\end{tabular}
+\end{table}
 
@@
 improving code quality and efficiency of development in a variety of
-contexts (Moore et. al. 2008; White 2012; Abadi et. al. 2016). By
+contexts (Moore et. al. 2008; White 2012; \cite{abadi_tensorflow:_2016}). By
 factoring out common elements, only features that are specific to the
@@
 
-\section*{Acknowlegements}
-We would like to acknowledge the generous support of
-
-% Your text comes here. Separate text sections with
-% \section{Section title}
-% \label{sec:1}
-% Text with citations \cite{RefB} and \cite{RefJ}.
-% \subsection{Subsection title}
-% \label{sec:2}
-% as required. Don't forget to give each section
-% and subsection a unique label (see Sect.~\ref{sec:1}).
-% \paragraph{Paragraph headings} Use paragraph headings as needed.
-% \begin{equation}
-% a^2+b^2=c^2
-% \end{equation}
-
-% For one-column wide figures use
-\begin{figure}
-% Use the relevant command to insert your figure file.
-% For example, with the graphicx package use
-  \includegraphics{example.eps}
-% figure caption is below the figure
-\caption{Please write your figure caption here}
-\label{fig:1}       % Give a unique label
-\end{figure}
-%
-% For two-column wide figures use
-\begin{figure*}
-% Use the relevant command to insert your figure file.
-% For example, with the graphicx package use
-  \includegraphics[width=0.75\textwidth]{example.eps}
-% figure caption is below the figure
-\caption{Please write your figure caption here}
-\label{fig:2}       % Give a unique label
-\end{figure*}
-%
-% For tables use
-\begin{table}
-% table caption is above the table
-\caption{Please write your table caption here}
-\label{tab:1}       % Give a unique label
-% For LaTeX tables use
-\begin{tabular}{lll}
-\hline\noalign{\smallskip}
-first & second & third  \\
-\noalign{\smallskip}\hline\noalign{\smallskip}
-number & number & number \\
-number & number & number \\
-\noalign{\smallskip}\hline
-\end{tabular}
-\end{table}
-
-%\begin{acknowledgements}
-%If you'd like to thank anyone, place your comments here
-%and remove the percent signs.
-%\end{acknowledgements}
+\begin{acknowledgements}
+The authors acknowledge the facilities and scientific and technical assistance
+of the National Imaging Facility, a National Collaborative Research
+Infrastructure Strategy (NCRIS) capability, at Monash Biomedical Imaging,
+Monash University. \textbf{Salary support for me ??} Early versions of the software described in the manuscript
+were informed by existing software written Parnesh Raniga while
+employed at Monash Biomedical Imaging.
+\end{acknowledgements}
 
 % BibTeX users please use one of
-%\bibliographystyle{spbasic}      % basic style, author-year citations
+\bibliographystyle{spbasic}      % basic style, author-year citations
 %\bibliographystyle{spmpsci}      % mathematics and physical sciences
 %\bibliographystyle{spphys}       % APS-like style for physics
-%\bibliography{}   % name your BibTeX data base
+\bibliography{arcana}   % name your BibTeX data base
 
 % Non-BibTeX users please use
-\begin{thebibliography}{}
+%\begin{thebibliography}{}
 %
@@
 %
-\bibitem{RefJ}
+%\bibitem{RefJ}
 % Format for Journal Reference
-Author, Article title, Journal, Volume, page numbers (year)
+%Author, Article title, Journal, Volume, page numbers (year)
 % Format for books
-\bibitem{RefB}
-Author, Book title, page numbers. Publisher, place (year)
+%\bibitem{RefB}
+%Author, Book title, page numbers. Publisher, place (year)
 % etc
-\end{thebibliography}
+%\end{thebibliography}
 

### 2018-10-12 manuscript/listings/data_spec.py

@@ -1,56 +1,0 @@
-import os
-from arcana import (
-    Study, StudyMetaClass, AcquiredFilesetSpec, FilesetSpec,
-    AcquiredFieldSpec, FieldSpec, ParameterSpec, SwitchSpec,
-    FilesetSelector, XnatRepository)
-from arcana.data.file_format.standard import text_format
-from nianalysis.file_format import (
-    nifti_gz_format, dicom_format, nifti_format, analyze_format)
-
-IMAGE_FORMATS = (dicom_format, nifti_format, nifti_gz_format,
-                 analyze_format)
-
-atlas_repo = XnatRepository(
-    'http://central.xnat.org', 'SAMPLE_TEMPLATES',
-    os.path.expanduser(os.path.join('~', 'work')))
-
-atlas = FilesetSelector(
-    'an_atlas', nifti_gz_format,
-    'an_atlas', frequency='per_study').match(atlas_repo.tree())
-
-
-class ExampleStudy(Study, metaclass=StudyMetaClass):
-
-    add_data_specs = [
-        # Acquired file sets
-        AcquiredFilesetSpec('acquired_file1', text_format),
-        AcquiredFilesetSpec('acquired_file2', IMAGE_FORMATS),
-        # Acquired fields
-        AcquiredFieldSpec('acquired_field1', int,
-                          frequency='per_subject'),
-        AcquiredFieldSpec('acquired_field2', str,),
-        # "Acquired" file set with default value. Useful for
-        # standard templates
-        AcquiredFilesetSpec('template1', IMAGE_FORMATS,
-                            frequency='per_study', default=atlas),
-        # Derived file sets
-        FilesetSpec('derived_file1', text_format, 'pipeline1'),
-        FilesetSpec('derived_file2', nifti_gz_format, 'pipeline1'),
-        FilesetSpec('derived_file3', text_format, 'pipeline2'),
-        FilesetSpec('derived_file4', dicom_format, 'pipeline3'),
-        FilesetSpec('derived_file5', nifti_gz_format, 'pipeline3',
-                    frequency='per_subject'),
-        FilesetSpec('derived_file6', text_format, 'pipeline4',
-                    frequency='per_visit'),
-        # Derived fields
-        FieldSpec('derived_field4', float, 'pipeline2'),
-        FieldSpec('derived_field7', int, 'pipeline4',
-                  frequency='per_study')]
-
-    add_parameter_specs = [
-        # Standard parameters
[…]

### 2018-10-12 manuscript/listings/example_application.py

@@ -1,0 +1,47 @@
+#!/usr/bin/env python3
+import os.path as op
+from arcana import (
+    FilesetSelector, FieldSelector, XnatRepository,
+    SlurmProcessor)
+from .example_study import ExampleStudy
+from nianalysis.file_format import dicom_format
+
+# Create study object that accesses an XNAT repository
+# and submits jobs to a SLURM scheduler
+study = ExampleStudy(
+    # Give a name to this analysis to
+    # differentiate it from other analyses
+    # performed on the same data
+    name='example',
+    # Set up connection to XNAT repository
+    repository=XnatRepository(
+        project_id='SAMPLE_PROJECT',
+        server='https://central.xnat.org',
+        cache_dir=op.expanduser(
+            op.join('~', 'xnat-cache'))),
+    # Specify to use the SLURM scheduler
+    runner=SlurmProcessor(
+        work_dir=op.expanduser('~/work')),
+    # Link files and fields in the repository
+    # to entries in the data specification
+    inputs={
+        'acquired1_file': FilesetSelector(
+            '.*mprage.*', dicom_format, is_regex=True),
+        'acquired_file2': FilesetSelector(
+            'SWI_Images', dicom_format),
+        'acquired_field1': FieldSelector(
+            'YOB', int, frequency='per_subject'),
+        'acquired_field2': FieldSelector(
+            'weight', float)},
+    # Specify parameters specific to this
+    # analysis
+    parameters={'parameter1': 55.0,
+                'pipeline_tool': 'toolB'})
+
+# Generate whole brain tracks and return path to
+# a cached dataset
+derived5 = study.data('whole_brain_tracks')
+print("The \"derived5\" fileset for the second visit "
+      "of subject 'PILOT1' were produced at:\n{}"
+      .format(derived5.path(subject_id='PILOT1',
+                            visit_id=1)))

### 2018-10-12 manuscript/listings/example_study.py

@@ -1,0 +1,108 @@
+import os
+from arcana import (
+    Study, StudyMetaClass, AcquiredFilesetSpec, FilesetSpec,
+    AcquiredFieldSpec, FieldSpec, ParameterSpec, SwitchSpec,
+    FilesetSelector, XnatRepository)
+from nianalysis.file_format import (
+    nifti_gz_format, dicom_format, nifti_format, analyze_format,
+    gif_format, text_format, text_mat_format)
+
+STD_IMAGE_FORMATS = (dicom_format, nifti_format, nifti_gz_format,
+                     analyze_format)
+
+atlas_repo = XnatRepository(
+    'http://central.xnat.org', 'SAMPLE_TEMPLATES',
+    os.path.expanduser(os.path.join('~', 'xnat-cache')))
+
+atlas = FilesetSelector(
+    'an_atlas', nifti_gz_format,
+    'an_atlas', frequency='per_study').match(atlas_repo.tree())
+
+
+class ExampleStudy(Study, metaclass=StudyMetaClass):
+
+    add_data_specs = [
+        # Acquired file sets
+        AcquiredFilesetSpec('acquired_file1', text_format),
+        AcquiredFilesetSpec('acquired_file2', STD_IMAGE_FORMATS),
+        # Acquired fields
+        AcquiredFieldSpec('acquired_field1', int,
+                          frequency='per_subject'),
+        AcquiredFieldSpec('acquired_field2', float),
+        # "Acquired" file set with default value. Useful for
+        # standard templates
+        AcquiredFilesetSpec('atlas1', STD_IMAGE_FORMATS,
+                            frequency='per_study', default=atlas),
+        # Derived file sets
+        FilesetSpec('derived_file1', text_format, 'pipeline1'),
+        FilesetSpec('derived_file2', nifti_gz_format, 'pipeline1'),
+        FilesetSpec('derived_file3', text_mat_format, 'pipeline2'),
+        FilesetSpec('derived_file4', dicom_format, 'pipeline3'),
+        FilesetSpec('derived_file5', nifti_gz_format, 'pipeline3',
+                    frequency='per_subject'),
+        FilesetSpec('derived_file6', text_format, 'pipeline4',
+                    frequency='per_visit'),
+        # Derived fields
+        FieldSpec('derived_field1', float, 'pipeline2'),
+        FieldSpec('derived_field2', int, 'pipeline4',
+                  frequency='per_study')]
+
+    add_parameter_specs = [
[…]

### 2018-10-12 manuscript/manuscript.tex
first round of automated citation insertion

@@
 Despite the availability of well-established neuroimaging analysis
-packages (Cox 1996; Smith et. al. 2004; Friston et. al. 2007; Tournier
+packages (Cox 1996; \cite{smith_advances_2004}; \cite{friston_statistical_2007}; Tournier
 et. al. 2012), the arcana of neuroimaging analysis is substantial due to
 the range of available tools, tuneable parameters, and imaging sequences
-involved (Cusack et. al. 2015). The distribution of complete
+involved (\cite{cusack_automatic_2015}). The distribution of complete
 ``end-to-end'' workflows, from acquired data to publication results, is
@@
 A barrier to designing portable and complete workflows is the
-heterogeneity of data storage conventions (Marcus et. al. 2007; Das et.
-al. 2011; Gorgolewski et. al. 2016). To address this, the emerging Brain
-Imaging Data Standard (BIDS) (Gorgolewski et. al. 2016) provides a way
+heterogeneity of data storage conventions (\cite{marcus_extensible_2007}; Das et.
+al. 2011; \cite{gorgolewski_brain_2016}). To address this, the emerging Brain
+Imaging Data Standard (BIDS) (\cite{gorgolewski_brain_2016}) provides a way
 to standardise the storage of neuroimaging data in file system
@@
 readily available in alternative workflow frameworks (Cusack et. al.
-2015; \cite{achterberg_fastr:_2016}; Amstutz et. al. 2016), and has been used
+2015; \cite{achterberg_fastr:_2016}; \cite{amstutz_common_2016}), and has been used
 to implement workflows that are robust to differences in fMRI protocols
@@
 The trend towards large multi-site and multi-contrast datasets collected
-over a number of years (Van Essen et. al. 2012; Thompson et. al. 2014;
-Sudlow et. al. 2015) presents additional challenges to workflow design.
+over a number of years (Van Essen et. al. 2012; \cite{thompson_enigma_2014};
+\cite{sudlow_uk_2015}) presents additional challenges to workflow design.
 Analysis packages are constantly being developed and improved, so the
@@
 time. Therefore, it is challenging to ensure workflows are applied
-consistently over the course of long studies (Cusack et. al. 2015).
+consistently over the course of long studies (\cite{cusack_automatic_2015}).
 
@@
 making the reuse of intermediate derivatives a practical requirement for
-some large studies (Schreiber et. al. 2018).
+some large studies (\cite{schreiber_using_2018}).
 
@@
 specify a qualitative change in the analysis, for example using ANTs
-registration (Avants et. al. 2011) instead of FSL registration (Smith
+registration (\cite{avants_reproducible_2011}) instead of FSL registration (Smith
 et. al. 2004), are specified by the \emph{SwitchSpec} subtype.
@@
 well as global tractography using streamlines tracking from the MRtrix
-toolbox (Tournier et. al. 2010; Tournier et. al. 2012) (Figure 9).
+toolbox (\cite{tournier_improved_2010}; \cite{tournier_mrtrix:_2012}) (Figure 9).
 
@@
 improving code quality and efficiency of development in a variety of
-contexts (Moore et. al. 2008; White 2012; \cite{abadi_tensorflow:_2016}). By
+contexts (\cite{moore_professional_2008}; White 2012; \cite{abadi_tensorflow:_2016}). By
 factoring out common elements, only features that are specific to the

### 2018-10-12 manuscript/manuscript.tex
more automated replacing of citations

@@
 Despite the availability of well-established neuroimaging analysis
-packages (Cox 1996; \cite{smith_advances_2004}; \cite{friston_statistical_2007}; Tournier
-et. al. 2012), the arcana of neuroimaging analysis is substantial due to
+packages (\cite{cox_afni:_1996}; \cite{smith_advances_2004}; \cite{friston_statistical_2007};
+Tournier et. al. 2012), the arcana of neuroimaging analysis is substantial due to
 the range of available tools, tuneable parameters, and imaging sequences
@@
 necessary for routine reproduction because of the effort required to
-accurately exactly reimplement such analyses (Kennedy 2018). It is also
+accurately exactly reimplement such analyses (\cite{kennedy_neuroimaging_2018}). It is also
 difficult to adapt existing workflows to new studies without detailed
@@
 (https://bids-apps.neuroimaging.io). However, for research groups with
-sufficient informatics support, software-managed repositories (Marcus
-et. al. 2007; Das et. al. 2011) can provide additional features, such as
+sufficient informatics support, software-managed repositories (Marcus et. al. 2007; Das et. al. 2011) can provide additional features, such as
 flexible access-control and automated pipelines. Therefore, for
@@
 While neuroimaging analyses are generally amenable to standardisation
-(Kennedy 2018), minor modifications are often required to accommodate
+(\cite{kennedy_neuroimaging_2018}), minor modifications are often required to accommodate
 idiosyncrasies of the acquisition protocols in use at different sites
@@
 Programmatic construction allows for rich control-flow logic that is not
-readily available in alternative workflow frameworks (Cusack et. al.
-2015; \cite{achterberg_fastr:_2016}; \cite{amstutz_common_2016}), and has been used
+readily available in alternative workflow frameworks (Cusack et. al. 2015; \cite{achterberg_fastr:_2016}; \cite{amstutz_common_2016}), and has been used
 to implement workflows that are robust to differences in fMRI protocols
@@
 The trend towards large multi-site and multi-contrast datasets collected
-over a number of years (Van Essen et. al. 2012; \cite{thompson_enigma_2014};
+over a number of years (Van et. al. 2012; \cite{thompson_enigma_2014};
 \cite{sudlow_uk_2015}) presents additional challenges to workflow design.
@@
 implementation of analysis suites for T1, T2* and diffusion weighted MRI
-(dMRI) data and the application of dMRI tractogram (Tournier 2012) and
-composite vein image (Ward 2018) workflows to data collected from a
+(dMRI) data and the application of dMRI tractogram (\cite{tournier_mrtrix:_2012}) and
+composite vein image (\cite{ward_combining_2018}) workflows to data collected from a
 healthy subject.
@@
 specify a qualitative change in the analysis, for example using ANTs
-registration (\cite{avants_reproducible_2011}) instead of FSL registration (Smith
-et. al. 2004), are specified by the \emph{SwitchSpec} subtype.
+registration (\cite{avants_reproducible_2011}) instead of FSL registration (Smith et. al. 2004), are specified by the \emph{SwitchSpec} subtype.
 SwitchSpecs take a name, default value and a list of accepted values at
@@
 Software versions are managed by the processor if environment modules
-(Furlani 1991) are installed on the system. These are loaded and
+(\cite{furlani_modules:_1991}) are installed on the system. These are loaded and
 unloaded before the interface of a workflow node is run based on the
@@
 contrasts derived from the T2*-weighted acquisition with an vein atlas
-registered to the T1-weighted acquisition (Ward 2018) (Figure 10).
+registered to the T1-weighted acquisition (\cite{ward_combining_2018}) (Figure 10).
 
@@
 \emph{SlurmProcessor} to submit jobs to the the MASSIVE HPC cluster
-(Goscinski 2014) in order to generate the figures.
+(\cite{goscinski_multi-modal_2014}) in order to generate the figures.
 
@@
 input vein atlas. The derived vein images are comparable to those
-generated by the original implementation (Ward 2018). The complete
+generated by the original implementation (\cite{ward_combining_2018}). The complete
 workflow took ?? min to complete over ?? compute cores.
@@
 improving code quality and efficiency of development in a variety of
-contexts (\cite{moore_professional_2008}; White 2012; \cite{abadi_tensorflow:_2016}). By
+contexts (\cite{moore_professional_2008}; \cite{white_hadoop:_2012}; \cite{abadi_tensorflow:_2016}). By
 factoring out common elements, only features that are specific to the
@@
 \href{https://en.wikipedia.org/wiki/Software_bug}{bugs} are shallow"
-(Raymond 1999). Given the size of the neuroimaging research community,
+(\cite{raymond_cathedral_1999}). Given the size of the neuroimaging research community,
 there are a large number of potential beta-testers and co-developers.
@@
 bridge between the two communities of users and developers. Alternative
-data storage systems (Book et. al. 2009; Das et. al. 2011, Scott et. al
-2011), can be integrated into Arcana by overriding a small number of
+data storage systems (Book et. al. 2009; Das et. al. 2011, Scott et. al 2011), can be integrated into Arcana by overriding a small number of
 methods from the Repository abstract base class. Repository modules
-could also be created for data portals such as \emph{DataLad} (Halchenko
-2018) in order to take advantage of the range of platforms they support.
+could also be created for data portals such as \emph{DataLad} (Halchenko et. al. 2018) in order to take advantage of the range of platforms they support.
 Implementing analyses in Arcana therefore enables researchers and
@@
 throughout the analysis is important to avoid introducing biases due to
-algorithm updates. In systems with environment modules (Furlani 1991)
+algorithm updates. In systems with environment modules (\cite{furlani_modules:_1991})
 installed, Arcana loads and unloads the required modules before and

### 2018-10-12 manuscript/manuscript.tex
more citation insertion

@@
 packages (\cite{cox_afni:_1996}; \cite{smith_advances_2004}; \cite{friston_statistical_2007};
-Tournier et. al. 2012), the arcana of neuroimaging analysis is substantial due to
+\cite{tournier_mrtrix:_2012}), the arcana of neuroimaging analysis is substantial due to
 the range of available tools, tuneable parameters, and imaging sequences
@@
 (https://bids-apps.neuroimaging.io). However, for research groups with
-sufficient informatics support, software-managed repositories (Marcus et. al. 2007; Das et. al. 2011) can provide additional features, such as
+sufficient informatics support, software-managed repositories (\cite{marcus_extensible_2007}; Das et. al. 2011) can provide additional features, such as
 flexible access-control and automated pipelines. Therefore, for
@@
 Programmatic construction allows for rich control-flow logic that is not
-readily available in alternative workflow frameworks (Cusack et. al. 2015; \cite{achterberg_fastr:_2016}; \cite{amstutz_common_2016}), and has been used
+readily available in alternative workflow frameworks (\cite{cusack_automatic_2015}; \cite{achterberg_fastr:_2016}; \cite{amstutz_common_2016}), and has been used
 to implement workflows that are robust to differences in fMRI protocols
@@
 specify a qualitative change in the analysis, for example using ANTs
-registration (\cite{avants_reproducible_2011}) instead of FSL registration (Smith et. al. 2004), are specified by the \emph{SwitchSpec} subtype.
+registration (\cite{avants_reproducible_2011}) instead of FSL registration (\cite{smith_advances_2004}), are specified by the \emph{SwitchSpec} subtype.
 SwitchSpecs take a name, default value and a list of accepted values at

### 2018-10-12 manuscript/manuscript.tex
finished inserting references

--- 2018-10-12 manuscript/manuscript.tex
@@
 Despite the availability of well-established neuroimaging analysis
-packages (Cox 1996; \cite{smith_advances_2004}; \cite{friston_statistical_2007}; Tournier
-et. al. 2012), the arcana of neuroimaging analysis is substantial due to
+packages \cite{cox_afni:_1996,smith_advances_2004,friston_statistical_2007,tournier_mrtrix:_2012}, the arcana of neuroimaging analysis is substantial due to
 the range of available tools, tuneable parameters, and imaging sequences
-involved (\cite{cusack_automatic_2015}). The distribution of complete
+involved \cite{cusack_automatic_2015}. The distribution of complete
 ``end-to-end'' workflows, from acquired data to publication results, is
 necessary for routine reproduction because of the effort required to
-accurately exactly reimplement such analyses (Kennedy 2018). It is also
+accurately exactly reimplement such analyses \cite{kennedy_neuroimaging_2018}. It is also
 difficult to adapt existing workflows to new studies without detailed
@@
 A barrier to designing portable and complete workflows is the
-heterogeneity of data storage conventions (\cite{marcus_extensible_2007}; Das et.
-al. 2011; \cite{gorgolewski_brain_2016}). To address this, the emerging Brain
-Imaging Data Standard (BIDS) (\cite{gorgolewski_brain_2016}) provides a way
+heterogeneity of data storage conventions \cite{marcus_extensible_2007,das_loris:_2012,gorgolewski_brain_2016}.
+To address this, the emerging Brain
+Imaging Data Standard (BIDS) \cite{gorgolewski_brain_2016} provides a way
 to standardise the storage of neuroimaging data in file system
@@
 (https://bids-apps.neuroimaging.io). However, for research groups with
-sufficient informatics support, software-managed repositories (Marcus
-et. al. 2007; Das et. al. 2011) can provide additional features, such as
+sufficient informatics support, software-managed repositories \cite{marcus_extensible_2007,das_loris:_2012} can provide additional features, such as
 flexible access-control and automated pipelines. Therefore, for
@@
 While neuroimaging analyses are generally amenable to standardisation
-(Kennedy 2018), minor modifications are often required to accommodate
+\cite{kennedy_neuroimaging_2018}, minor modifications are often required to accommodate
 idiosyncrasies of the acquisition protocols in use at different sites
-(Esteban et al. 2018). Therefore, workflows may require conditional
+\cite{esteban_fmriprep:_2018}. Therefore, workflows may require conditional
 logic in construction or execution to be portable. Nipype is a flexible
 Python framework for neuroimaging analysis in which workflows are
-constructed programmatically in Python (Gorgolewski et al. 2011).
+constructed programmatically in Python \cite{gorgolewski_nipype:_2011}.
 Programmatic construction allows for rich control-flow logic that is not
-readily available in alternative workflow frameworks (Cusack et. al.
-2015; \cite{achterberg_fastr:_2016}; \cite{amstutz_common_2016}), and has been used
+readily available in alternative workflow frameworks \cite{cusack_automatic_2015,achterberg_fastr:_2016,amstutz_common_2016}, and has been used
 to implement workflows that are robust to differences in fMRI protocols
-across a large number of sites (Esteban et al. 2018).
+across a large number of sites \cite{esteban_fmriprep:_2018}.
 
 The trend towards large multi-site and multi-contrast datasets collected
-over a number of years (Van Essen et. al. 2012; \cite{thompson_enigma_2014};
-\cite{sudlow_uk_2015}) presents additional challenges to workflow design.
+over a number of years \cite{van_essen_human_2012,thompson_enigma_2014,sudlow_uk_2015}
+presents additional challenges to workflow design.
 Analysis packages are constantly being developed and improved, so the
@@
 time. Therefore, it is challenging to ensure workflows are applied
-consistently over the course of long studies (\cite{cusack_automatic_2015}).
+consistently over the course of long studies \cite{cusack_automatic_2015}.
 
@@
 making the reuse of intermediate derivatives a practical requirement for
-some large studies (\cite{schreiber_using_2018}).
+some large studies \cite{schreiber_using_2018}.
 
@@
 neuroimaging analyses. \emph{Abstraction of Repository-Centric ANAlysis
-(Arcana)} \\(\href{http://arcana.readthedocs.io}{http://arcana.readthedocs.io}) is a Python framework for
+(Arcana)} \\(\href{http://arcana.readthedocs.io}{http://arcana.readthedocs.io} is a Python framework for
 designing complex workflows in which modular Nipype pipelines operate on
@@
 implementation of analysis suites for T1, T2* and diffusion weighted MRI
-(dMRI) data and the application of dMRI tractogram (Tournier 2012) and
-composite vein image (Ward 2018) workflows to data collected from a
+(dMRI) data and the application of dMRI tractogram \cite{tournier_mrtrix:_2012} and
+composite vein image \cite{ward_combining_2018} workflows to data collected from a
 healthy subject.
@@
 specify a qualitative change in the analysis, for example using ANTs
-registration (\cite{avants_reproducible_2011}) instead of FSL registration (Smith
-et. al. 2004), are specified by the \emph{SwitchSpec} subtype.
+registration \cite{avants_reproducible_2011} instead of FSL registration \cite{smith_advances_2004}, are specified by the \emph{SwitchSpec} subtype.
 SwitchSpecs take a name, default value and a list of accepted values at
@@
 requirements can be used by the Processor to configure environment
-modules (Furlani, J. 1991) if present, to ensure the required software
+modules \cite{furlani_modules:_1991} if present, to ensure the required software
 packages are available. Similarly, the expected memory requirements and
@@
 (Figure 2). There are currently three supported repository types, XNAT
-(Marcus et al. 2007), BIDS (Gorgolewski et al. 2016) and a simple
+\cite{marcus_extensible_2007}, BIDS \cite{gorgolewski_brain_2016} and a simple
 ``directory'' format, which are encapsulated by \emph{XnatRepository},
@@
 Software versions are managed by the processor if environment modules
-(Furlani 1991) are installed on the system. These are loaded and
+\cite{furlani_modules:_1991} are installed on the system. These are loaded and
 unloaded before the interface of a workflow node is run based on the
 requirements specified for the node during construction of the pipeline
-(see \emph{Pipeline constructors}). Maps from requirement names to
+(see \emph{Pipeline constructors}. Maps from requirement names to
 module names in the processing environment can be passed to the
@@
 well as global tractography using streamlines tracking from the MRtrix
-toolbox (\cite{tournier_improved_2010}; \cite{tournier_mrtrix:_2012}) (Figure 9).
-
-%\includegraphics[width=3.82849in,height=6.85938in]{media/image28.png}
+toolbox \cite{tournier_improved_2010,tournier_mrtrix:_2012} (Figure 9).
 
@@
 contrasts derived from the T2*-weighted acquisition with an vein atlas
-registered to the T1-weighted acquisition (Ward 2018) (Figure 10).
-
-%\includegraphics[width=4.29167in,height=7.43818in]{media/image32.png}
+registered to the T1-weighted acquisition \cite{ward_combining_2018} (Figure 10).
 
@@
 \emph{SlurmProcessor} to submit jobs to the the MASSIVE HPC cluster
-(Goscinski 2014) in order to generate the figures.
+\cite{goscinski_multi-modal_2014} in order to generate the figures.
 
@@
 input vein atlas. The derived vein images are comparable to those
-generated by the original implementation (Ward 2018). The complete
+generated by the original implementation \cite{ward_combining_2018}. The complete
 workflow took ?? min to complete over ?? compute cores.
-
-%\includegraphics[width=6.228in,height=4.72396in]{media/image22.png}
 
@@
 
-%\includegraphics[width=6.27083in,height=4.18056in]{media/image34.png}
-
 \begin{figure*}
@@
 produce the tractography results from ?? to ??.
-
-%\includegraphics[width=6.27083in,height=2.09722in]{media/image30.png}
 
@@
 
-Software frameworks (Yacoub and Ammar 2004) have been successful in
+Software frameworks \cite{yacoub_pattern-oriented_2004} have been successful in
 improving code quality and efficiency of development in a variety of
-contexts (\cite{moore_professional_2008}; White 2012; \cite{abadi_tensorflow:_2016}). By
+contexts \cite{moore_professional_2008,white_hadoop:_2012,abadi_tensorflow:_2016}. By
 factoring out common elements, only features that are specific to the
@@
 \href{https://en.wikipedia.org/wiki/Software_bug}{bugs} are shallow"
-(Raymond 1999). Given the size of the neuroimaging research community,
+\cite{raymond_cathedral_1999}. Given the size of the neuroimaging research community,
 there are a large number of potential beta-testers and co-developers.
@@
 bridge between the two communities of users and developers. Alternative
-data storage systems (Book et. al. 2009; Das et. al. 2011, Scott et. al
-2011), can be integrated into Arcana by overriding a small number of
+data storage systems \cite{,scott_coins:_2011,das_loris:_2012,book_neuroinformatics_2013}, can be integrated into Arcana by overriding a small number of
 methods from the Repository abstract base class. Repository modules
-could also be created for data portals such as \emph{DataLad} (Halchenko
-2018) in order to take advantage of the range of platforms they support.
+could also be created for data portals such as \emph{DataLad} \cite{yaroslav_halchenko_datalad/datalad_2018} in order to take advantage of the range of platforms they support.
 Implementing analyses in Arcana therefore enables researchers and
@@
 throughout the analysis is important to avoid introducing biases due to
-algorithm updates. In systems with environment modules (Furlani 1991)
+algorithm updates. In systems with environment modules \cite{furlani_modules:_1991}
 installed, Arcana loads and unloads the required modules before and
@@
 
-% Non-BibTeX users please use
-%\begin{thebibliography}{}
-%
-% and use \bibitem to create references. Consult the Instructions
-% for authors for reference list style.
-%
-%\bibitem{RefJ}
-% Format for Journal Reference
-%Author, Article title, Journal, Volume, page numbers (year)
-% Format for books
-%\bibitem{RefB}
-%Author, Book title, page numbers. Publisher, place (year)
-% etc
-%\end{thebibliography}
-
 \end{document}

### 2018-10-13 manuscript/manuscript.tex
touched up manuscript listings

@@
 %
+\usepackage{natbib}
 \usepackage{listings}
@@
     basicstyle=\footnotesize,
-%  captionpos=b,                    % sets the caption-position to bottom
+    captionpos=b,                    % sets the caption-position to bottom
     language=Python,                 % the language of the code
@@
 \author{
-	Thomas G. Close\affmark[1,2]\and
+	Thomas G. Close\affmark[1,2]*\and
 	Phillip G. D. Ward\affmark[1,3,4] \and
@@
 Despite the availability of well-established neuroimaging analysis
-packages \cite{cox_afni:_1996,smith_advances_2004,friston_statistical_2007,tournier_mrtrix:_2012}, the arcana of neuroimaging analysis is substantial due to
+packages \citep{cox_afni:_1996,smith_advances_2004,friston_statistical_2007,tournier_mrtrix:_2012}, the arcana of neuroimaging analysis is substantial due to
 the range of available tools, tuneable parameters, and imaging sequences
-involved \cite{cusack_automatic_2015}. The distribution of complete
+involved \citep{cusack_automatic_2015}. The distribution of complete
 ``end-to-end'' workflows, from acquired data to publication results, is
 necessary for routine reproduction because of the effort required to
-accurately exactly reimplement such analyses \cite{kennedy_neuroimaging_2018}. It is also
+accurately exactly reimplement such analyses \citep{kennedy_neuroimaging_2018}. It is also
 difficult to adapt existing workflows to new studies without detailed
@@
 A barrier to designing portable and complete workflows is the
-heterogeneity of data storage conventions \cite{marcus_extensible_2007,das_loris:_2012,gorgolewski_brain_2016}.
+heterogeneity of data storage conventions \citep{marcus_extensible_2007,das_loris:_2012,gorgolewski_brain_2016}.
 To address this, the emerging Brain
-Imaging Data Standard (BIDS) \cite{gorgolewski_brain_2016} provides a way
+Imaging Data Standard (BIDS) \citep{gorgolewski_brain_2016} provides a way
 to standardise the storage of neuroimaging data in file system
@@
 (https://bids-apps.neuroimaging.io). However, for research groups with
-sufficient informatics support, software-managed repositories \cite{marcus_extensible_2007,das_loris:_2012} can provide additional features, such as
+sufficient informatics support, software-managed repositories \citep{marcus_extensible_2007,das_loris:_2012} can provide additional features, such as
 flexible access-control and automated pipelines. Therefore, for
@@
 While neuroimaging analyses are generally amenable to standardisation
-\cite{kennedy_neuroimaging_2018}, minor modifications are often required to accommodate
+\citep{kennedy_neuroimaging_2018}, minor modifications are often required to accommodate
 idiosyncrasies of the acquisition protocols in use at different sites
-\cite{esteban_fmriprep:_2018}. Therefore, workflows may require conditional
+\citep{esteban_fmriprep:_2018}. Therefore, workflows may require conditional
 logic in construction or execution to be portable. Nipype is a flexible
 Python framework for neuroimaging analysis in which workflows are
-constructed programmatically in Python \cite{gorgolewski_nipype:_2011}.
+constructed programmatically in Python \citep{gorgolewski_nipype:_2011}.
 Programmatic construction allows for rich control-flow logic that is not
-readily available in alternative workflow frameworks \cite{cusack_automatic_2015,achterberg_fastr:_2016,amstutz_common_2016}, and has been used
+readily available in alternative workflow frameworks \citep{cusack_automatic_2015,achterberg_fastr:_2016,amstutz_common_2016}, and has been used
 to implement workflows that are robust to differences in fMRI protocols
-across a large number of sites \cite{esteban_fmriprep:_2018}.
+across a large number of sites \citep{esteban_fmriprep:_2018}.
 
 The trend towards large multi-site and multi-contrast datasets collected
-over a number of years \cite{van_essen_human_2012,thompson_enigma_2014,sudlow_uk_2015}
+over a number of years \citep{van_essen_human_2012,thompson_enigma_2014,sudlow_uk_2015}
 presents additional challenges to workflow design.
@@
 time. Therefore, it is challenging to ensure workflows are applied
-consistently over the course of long studies \cite{cusack_automatic_2015}.
+consistently over the course of long studies \citep{cusack_automatic_2015}.
 
@@
 making the reuse of intermediate derivatives a practical requirement for
-some large studies \cite{schreiber_using_2018}.
+some large studies \citep{schreiber_using_2018}.
 
@@
 implementation of analysis suites for T1, T2* and diffusion weighted MRI
-(dMRI) data and the application of dMRI tractogram \cite{tournier_mrtrix:_2012} and
-composite vein image \cite{ward_combining_2018} workflows to data collected from a
+(dMRI) data and the application of dMRI tractogram \citep{tournier_mrtrix:_2012} and
+composite vein image \citep{ward_combining_2018} workflows to data collected from a
 healthy subject.
@@
 \begin{figure}
-\lstinputlisting[language=Python, firstline=2, lastline=57]{listings/example_study.py}
+\lstinputlisting[language=Python, firstline=2, lastline=58]{listings/example_study.py}
 \caption{Example data and parameter specifications. The data
@@
 the Study class by providing a list of \emph{ParameterSpec} objects to
-the \emph{add\_parameter\_specs} class attribute. ParameterSpec objects
+the \emph{add\_param\_specs} class attribute. ParameterSpec objects
 are initialised with a name and default value. Special parameters that
 specify a qualitative change in the analysis, for example using ANTs
-registration \cite{avants_reproducible_2011} instead of FSL registration \cite{smith_advances_2004}, are specified by the \emph{SwitchSpec} subtype.
+registration \citep{avants_reproducible_2011} instead of FSL registration
+\citep{smith_advances_2004}, are specified by the \emph{SwitchSpec} subtype.
 SwitchSpecs take a name, default value and a list of accepted values at
@@
 \begin{figure}
-\lstinputlisting[language=Python, firstline=58, lastline=108]{listings/example_study.py}
+\lstinputlisting[language=Python, firstline=59]{listings/example_study.py}
 \caption{Example pipeline constructor method. Pipelines are
@@
 requirements can be used by the Processor to configure environment
-modules \cite{furlani_modules:_1991} if present, to ensure the required software
+modules \citep{furlani_modules:_1991} if present, to ensure the required software
 packages are available. Similarly, the expected memory requirements and
@@
 method resolution order (MRO) and adding specifications from their
-\emph{add\_data\_specs}, \emph{add\_parameter\_specs} attributes,
+\emph{add\_data\_specs}, \emph{add\_param\_specs} attributes,
 overriding previously added specifications with matching names. Note
@@
 class, additional data and parameter specifications can be added to the
-class via \emph{add\_data\_specs} and \emph{add\_parameter\_specs}
+class via \emph{add\_data\_specs} and \emph{add\_param\_specs}
 respectively for additional analysis not included in the sub-studies.
@@
 (Figure 2). There are currently three supported repository types, XNAT
-\cite{marcus_extensible_2007}, BIDS \cite{gorgolewski_brain_2016} and a simple
+\citep{marcus_extensible_2007}, BIDS \citep{gorgolewski_brain_2016} and a simple
 ``directory'' format, which are encapsulated by \emph{XnatRepository},
@@
 \hline\noalign{\smallskip}
-\textbf{Type} & Plain-directory & BIDS & XNAT  \\
+\textbf{Type} & \textbf{Plain-directory} & \textbf{BIDS} & \textbf{XNAT}  \\
 \noalign{\smallskip}\hline\noalign{\smallskip}
@@
 \hline\noalign{\smallskip}
-\textbf{Method name} & Function \\
+\textbf{Method name} & \textbf{Function} \\
 \noalign{\smallskip}\hline\noalign{\smallskip}
@@
 Software versions are managed by the processor if environment modules
-\cite{furlani_modules:_1991} are installed on the system. These are loaded and
+\citep{furlani_modules:_1991} are installed on the system. These are loaded and
 unloaded before the interface of a workflow node is run based on the
@@
 Study classes for T1, T2* and diffusion weighted MRI data have been
-implemented as part of the \emph{Biomedical imAgiNg ANAlysis (Banana)}
-package
-(\href{https://github.com/MonashBI/banana}{{http://github.com/MonashBI/banana}};
+implemented as part of the \emph{Biomedical imAgiNg ANAlysis (Banana)} package \\
+(\href{https://github.com/MonashBI/banana}{{http://github.com/MonashBI/banana}} and
 \href{http://pypi.org./project/banana}{{http://pypi.org./project/banana}}).
@@
 well as global tractography using streamlines tracking from the MRtrix
-toolbox \cite{tournier_improved_2010,tournier_mrtrix:_2012} (Figure 9).
+toolbox \citep{tournier_improved_2010,tournier_mrtrix:_2012} (Figure 9).
 
@@
 contrasts derived from the T2*-weighted acquisition with an vein atlas
-registered to the T1-weighted acquisition \cite{ward_combining_2018} (Figure 10).
+registered to the T1-weighted acquisition \citep{ward_combining_2018} (Figure 10).
 
@@
 \emph{SlurmProcessor} to submit jobs to the the MASSIVE HPC cluster
-\cite{goscinski_multi-modal_2014} in order to generate the figures.
+\citep{goscinski_multi-modal_2014} in order to generate the figures.
 
@@
 input vein atlas. The derived vein images are comparable to those
-generated by the original implementation \cite{ward_combining_2018}. The complete
+generated by the original implementation \citep{ward_combining_2018}. The complete
 workflow took ?? min to complete over ?? compute cores.
@@
 
-Software frameworks \cite{yacoub_pattern-oriented_2004} have been successful in
+Software frameworks \citep{yacoub_pattern-oriented_2004} have been successful in
 improving code quality and efficiency of development in a variety of
-contexts \cite{moore_professional_2008,white_hadoop:_2012,abadi_tensorflow:_2016}. By
+contexts \citep{moore_professional_2008,white_hadoop:_2012,abadi_tensorflow:_2016}. By
 factoring out common elements, only features that are specific to the
@@
 \href{https://en.wikipedia.org/wiki/Software_bug}{bugs} are shallow"
-\cite{raymond_cathedral_1999}. Given the size of the neuroimaging research community,
+\citep{raymond_cathedral_1999}. Given the size of the neuroimaging research community,
 there are a large number of potential beta-testers and co-developers.
@@
 bridge between the two communities of users and developers. Alternative
-data storage systems \cite{,scott_coins:_2011,das_loris:_2012,book_neuroinformatics_2013}, can be integrated into Arcana by overriding a small number of
+data storage systems \citep{,scott_coins:_2011,das_loris:_2012,book_neuroinformatics_2013}, can be integrated into Arcana by overriding a small number of
 methods from the Repository abstract base class. Repository modules
-could also be created for data portals such as \emph{DataLad} \cite{yaroslav_halchenko_datalad/datalad_2018} in order to take advantage of the range of platforms they support.
+could also be created for data portals such as \emph{DataLad} \citep{yaroslav_halchenko_datalad/datalad_2018} in order to take advantage of the range of platforms they support.
 Implementing analyses in Arcana therefore enables researchers and
@@
 throughout the analysis is important to avoid introducing biases due to
-algorithm updates. In systems with environment modules \cite{furlani_modules:_1991}
+algorithm updates. In systems with environment modules \citep{furlani_modules:_1991}
 installed, Arcana loads and unloads the required modules before and

### 2018-10-13 examples/manuscript.py

@@ -38,7 +38,7 @@ class ExampleStudy(Study, metaclass=StudyMetaClass):
         FieldSpec('derived_field7', int, 'pipeline4',
                   frequency='per_study')]
 
-    add_parameter_specs = [
+    add_param_specs = [
         # Standard parameters
         ParameterSpec('parameter1', 10),
         ParameterSpec('parameter2', 25.8),

### 2018-10-13 manuscript/listings/example_application.py

@@ -2,7 +2,7 @@
 import os.path as op
 from arcana import (
     FilesetSelector, FieldSelector, XnatRepository,
-    SlurmProcessor)
+    SlurmProcessor, ModulesEnvironment)
 from .example_study import ExampleStudy
 from nianalysis.file_format import dicom_format
 
@@ -19,9 +19,16 @@ study = ExampleStudy(
         server='https://central.xnat.org',
         cache_dir=op.expanduser(
             op.join('~', 'xnat-cache'))),
-    # Specify to use the SLURM scheduler
-    runner=SlurmProcessor(
+    # Specify the use the SLURM scheduler to submit
+    # nodes as jobs using Nipype's SlurmGraphPlugin
+    processor=SlurmProcessor(
         work_dir=op.expanduser('~/work')),
+    # Specify the use of environment modules to
+    # satisfy software requirements. Non-standard
+    # package names explicitly mapped to approp. reqs.
+    environment=ModulesEnvironment(
+        packages_map={
+            'Package1_Parallel': package1_req}),
     # Link files and fields in the repository
     # to entries in the data specification
     inputs={

### 2018-10-13 manuscript/listings/example_study.py

@@ -5,18 +5,19 @@ from arcana import (
     FilesetSelector, XnatRepository)
 from nianalysis.file_format import (
     nifti_gz_format, dicom_format, nifti_format, analyze_format,
-    gif_format, text_format, text_mat_format)
+    text_format, text_mat_format)
 
 STD_IMAGE_FORMATS = (dicom_format, nifti_format, nifti_gz_format,
                      analyze_format)
 
-atlas_repo = XnatRepository(
-    'http://central.xnat.org', 'SAMPLE_TEMPLATES',
-    os.path.expanduser(os.path.join('~', 'xnat-cache')))
-
-atlas = FilesetSelector(
-    'an_atlas', nifti_gz_format,
-    'an_atlas', frequency='per_study').match(atlas_repo.tree())
+# Select a Fileset collection to use as a default for template1
+template_repo = XnatRepository(
+    server='http://central.xnat.org', project_id='TEMPLATES',
+    cache=os.path.expanduser(os.path.join('~', 'xnat-cache')))
+template_selector = FilesetSelector(
+    name='template1_default', format=nifti_gz_format,
+    pattern='MNI152_T1', frequency='per_study')
+template_collectn = template_selector.match(template_repo.tree())
 
 
 class ExampleStudy(Study, metaclass=StudyMetaClass):
@@ -31,8 +32,9 @@ class ExampleStudy(Study, metaclass=StudyMetaClass):
         AcquiredFieldSpec('acquired_field2', float),
         # "Acquired" file set with default value. Useful for
         # standard templates
-        AcquiredFilesetSpec('atlas1', STD_IMAGE_FORMATS,
-                            frequency='per_study', default=atlas),
+        AcquiredFilesetSpec('template1', STD_IMAGE_FORMATS,
+                            frequency='per_study',
+                            default=template_collectn),
         # Derived file sets
         FilesetSpec('derived_file1', text_format, 'pipeline1'),
         FilesetSpec('derived_file2', nifti_gz_format, 'pipeline1'),
@@ -47,7 +49,7 @@ class ExampleStudy(Study, metaclass=StudyMetaClass):
         FieldSpec('derived_field2', int, 'pipeline4',
                   frequency='per_study')]
 
-    add_parameter_specs = [
+    add_param_specs = [
         # Standard parameters
         ParameterSpec('parameter1', 10),
         ParameterSpec('parameter2', 25.8),
[…]

### 2018-10-13 paper.py

@@ -19,7 +19,7 @@ class ArcanaPaper(MultiStudy, ImageDisplayMixin,
 #         SubStudySpec('t2star', T2starwT1wStudy),
         SubStudySpec('dmri', DiffusionStudy)]
 
-    add_parameter_specs = [
+    add_param_specs = [
         ParameterSpec(
             'dmri_fig_slice_offset', (4, 0, 0),
             desc=("Offset the sagittal slices of dMRI figures so they "

### 2018-10-13 manuscript/manuscript.tex
finished port to latex document

@@
 
-\section{Introduction}
+\section*{Introduction}
 \label{intro}
@@
 
-\section{Methods}
+\section*{Methods}
 \label{methods}
 
-\subsection{Framework overview}
+\subsection*{Framework overview}
 \label{framework-overview}
@@
 linked together by the \emph{data specification} \emph{table} of the
-Study class (Figure 1). Likewise, free parameters used in pipeline
+Study class (Figure \ref{fig:example_study}). Likewise, free parameters used in pipeline
 construction are defined in the class' \emph{parameter specification}
@@
 \begin{figure*}
-  \begin{center}
+    \centering
     \includegraphics[width=0.55\textwidth]{figures/example_study}
@@
 pipelines}
-  \end{center}
 \label{fig:example_study}
@@
 stored back in the repository for reuse by subsequent analyses (Figure
-2). Input data to the study are also stored in the repository, and are
+\ref{fig:simple_uml}). Input data to the study are also stored in the repository, and are
 matched against entries in the class' data specification table using
@@
 \begin{figure*}
-  \begin{center}
+    \centering
     \includegraphics[width=0.9\textwidth]{figures/simplified_arcana_uml}
@@
 repository.}
-\end{center}
 \label{fig:simple_uml}
@@
 
-\subsection{Analysis design: Study classes}
+\subsection*{Analysis design: Study classes}
 \label{analysis-design-study-classes}
@@
 
-\subsubsection{Data and parameter specification
+\subsubsection*{Data and parameter specification
 tables}
@@
 a Study class via the \emph{add\_data\_specs} class attribute as a list
-of named \emph{FilesetSpec} and \emph{FieldSpec} objects (Figure 3).
+of named \emph{FilesetSpec} and \emph{FieldSpec} objects (Figure \ref{fig:data_spec}).
 Specifications for acquired data (i.e. input data to the study) are
@@
 the Study class}
-\label{list:data_spec}
+\label{fig:data_spec}
 \end{figure}
@@
 
-\subsubsection{Workflow design}
+\subsubsection*{Workflow design}
 \label{workflow-design}
@@
 be created in constructor methods using the \emph{Study.new\_pipeline}
-method (Figure 4).
+method (Figure \ref{fig:pipeline_constructor}).
 
@@
 namespace management}
-\label{list:pipeline_constructor}
+\label{fig:pipeline_constructor}
 \end{figure}
@@
 
-\subsubsection{Extension and specialisation by class inheritance}
+\subsubsection*{Extension and specialisation by class inheritance}
 \label{extension-and-specialisation-by-class-inheritance}
@@
 
-\subsubsection{Implementing multi-modal
+\subsubsection*{Implementing multi-modal
 studies}
@@
 are joined by mapping them to a common entry in the specification table
-of the MultiStudy (Figure 6). This enables derivatives from one
+of the MultiStudy (Figure \ref{fig:example_multi_study}). This enables derivatives from one
 sub-study (e.g. brain extracted T1-weighted anatomical) to be referenced
@@
 \begin{figure*}
-  \begin{center}
+  \centering
     \includegraphics[width=0.775\textwidth]{figures/example_multi_study}
@@
 spec in the global space onto data specifications the multiple sub-study
-namespaces (e.g. \emph{Derived 1, 2 \& 3}). There are no restrictions
+namespaces (e.g. \emph{Derived} \emph{1}, \emph{2} and \emph{3}).
+There are no restrictions
 between mapping acquired and derivative specifications: both acquired
@@
 \emph{Sub-Study 2})}
-\end{center}
 \label{fig:example_multi_study}
@@
 
-\hypertarget{analysis-application-study-instances}{%
-\subsection{Analysis application: Study
-instances}\label{analysis-application-study-instances}}
+\subsection*{Analysis application: Study instances}
+\label{analysis-application-study-instances}
 
@@
 the construction of analysis workflows, the execution of the workflows,
-and the flow of data to and from the repository (Figure 7).
+and the flow of data to and from the repository (Figure \ref{fig:full_uml}).
 
 \begin{figure*}
-  \begin{center}
+	\centering
     \includegraphics[width=\textwidth]{figures/full_arcana_uml}
@@
 on a Study subclass constructs the requisite pipelines (as specified in
-\emph{Study.data\_specs}) to produce the requested data, and sends them
+\emph{data\_specs}) to produce the requested data, and sends them
 to the \emph{Processor} to be processed. Data is selected by
@@
 \label{fig:full_uml}
-\end{center}
 \end{figure*}
@@
 Repository and Processor modules and a list of \emph{Selector} objects
-to select input datasets from the repository (Figure 8).
+to select input datasets from the repository (Figure \ref{fig:study_application}).
 
@@
 stored in the repository if already present.}
-\label{list:study_application}
+\label{fig:study_application}
 \end{figure}
 
-\hypertarget{repository-modules}{%
-\subsubsection{Repository modules}\label{repository-modules}}
+\subsubsection*{Repository modules}\label{repository-modules}
 
@@
 repositories and repository types at analysis ``application time''
-(Figure 2). There are currently three supported repository types, XNAT
+(Figure \ref{fig:simple_uml}). There are currently three supported repository types, XNAT
 \citep{marcus_extensible_2007}, BIDS \citep{gorgolewski_brain_2016} and a simple
@@
 \emph{\textless{}primary-session-name\textgreater{}\_\textless{}study-name\textgreater{}}
-(Table 1).
+(Table \ref{tbl:repo-structure}).
 
@@
 implemented by extending the Repository abstract base class and
-implementing a small set of methods (Table 2).
+implementing a small set of methods (Table \ref{tbl:abstract-repo-methods}).
 
@@
 
-\subsubsection{Study inputs}
+\subsubsection*{Study inputs}
 \label{study-inputs}
@@
 
-\subsubsection{Processor modules}
+\subsubsection*{Processor modules}
 \label{processor-modules}
@@
 to derive derivatives requested from the data specification by the
-\emph{Study.data(name{[}, name,...{]})} method (Figure 2). The first
+\emph{Study.data(name{[}, name,...{]})} method (Figure \ref{fig:simple_uml}). The first
 step in this procedure is to query the repository tree for all data and
@@
 study is determined by the \emph{reprocess} flag, which is passed to the
-Study on initialisation (Table 3).
+Study on initialisation (Table \ref{tbl:reprocess-flag}).
 
@@
 
-\section{Results}
+\section*{Results}
 \label{results}
@@
 well as global tractography using streamlines tracking from the MRtrix
-toolbox \citep{tournier_improved_2010,tournier_mrtrix:_2012} (Figure 9).
+toolbox \citep{tournier_improved_2010,tournier_mrtrix:_2012} (Figure \ref{fig:dmri_study}).
 
 \begin{figure*}
-  \begin{center}
+	\centering
     \includegraphics[width=0.55\textwidth]{figures/dmri_study}
@@
 derivatives: FA and ADC and/or streamlines fibre tracking.}
-\end{center}
 \label{fig:dmri_study}
@@
 contrasts derived from the T2*-weighted acquisition with an vein atlas
-registered to the T1-weighted acquisition \citep{ward_combining_2018} (Figure 10).
+registered to the T1-weighted acquisition \citep{ward_combining_2018} (Figure \ref{fig:t2star_t1_study}).
 
 \begin{figure*}
-  \begin{center}
+	\centering
     \includegraphics[width=0.775\textwidth]{figures/t2star_t1_study}
@@
 combined with the composite vein image to produce the vein mask.}
-  \end{center}
 \label{fig:t2star_t1_study}
@@
 turn into a single MultiStudy class for the results section of this
-manuscript\emph{, ArcanaPaper}, (Figure S.1-5). Methods are implemented
-in ArcanaPaper to generate and display the derivative images in Figures
-11, 12, and 13.
+manuscript\emph{, ArcanaPaper}, (Supplementary material). Methods are
+implemented in ArcanaPaper to generate and display the derivative
+images in Figure \ref{fig:veins}, \ref{fig:fa_adc} and \ref{fig:tractography}.
 
@@
 directions with b=1500 mm2/s and 3 b=0, bandwidth=781Hz/pixel)
-(\textbf{cite Lifespan paper ??}). Methods for Figure 11, 12, and 13 in
+(\textbf{cite Lifespan paper ??}). Methods for Figure \ref{fig:veins}, \ref{fig:fa_acs},
+and \ref{fig:tractography} in
 the ArcanaPaper class were applied to the acquired dataset to using the
@@
 \begin{figure*}
-  \begin{center}
+    \centering
     \includegraphics[width=\textwidth]{figures/veins}
@@
 \emph{Bottom row}: coronal slices.}
-  \end{center}
 \label{fig:veins}
@@
 \begin{figure*}
-  \begin{center}
+    \centering
     \includegraphics[width=\textwidth]{figures/fa_adc}
@@
 sagittal midline slices.}
-  \end{center}
 \label{fig:fa_adc}
@@
 \begin{figure*}
-  \begin{center}
+    \centering
     \includegraphics[width=\textwidth]{figures/tractography}
@@
 sagittal midline slice.}
-  \end{center}
 \label{fig:tractography}
@@
 
-\section{Discussion}
+\section*{Discussion}
 \label{discussion}
@@
 since such classes can be applied to alternate datasets in order to
-reproduce the exact analysis. The \emph{ArcanaPaper} class (Figure
-S.1-5), which contains methods to generate all figures in the Results
-section of this manuscript, is an example of this approach.
+reproduce the exact analysis. The \emph{ArcanaPaper} class
+(Supplementary material), which contains methods to generate all figures
+in the Results section of this manuscript, is an example of this approach.
 
@@
 bridge between the two communities of users and developers. Alternative
-data storage systems \citep{,scott_coins:_2011,das_loris:_2012,book_neuroinformatics_2013}, can be integrated into Arcana by overriding a small number of
+data storage systems \citep{scott_coins:_2011,das_loris:_2012,book_neuroinformatics_2013}, can be integrated into Arcana by overriding a small number of
 methods from the Repository abstract base class. Repository modules
@@
 preprocessed dMRI shared between tensor and fibre tracking workflows
-(Figures 12 and 13), processing time as well as time required for manual
+(Figure \ref{fig:fa_adc} and \ref{fig:tractography}), processing time as
+well as time required for manual
 QC is minimised. Given analyses implemented in Arcana are also able to
@@
 
-\section{Conclusion}
+\section*{Conclusion}
 \label{conclusion}
@@
 
-% BibTeX users please use one of
-\bibliographystyle{spbasic}      % basic style, author-year citations
-%\bibliographystyle{spmpsci}      % mathematics and physical sciences
-%\bibliographystyle{spphys}       % APS-like style for physics
-\bibliography{arcana}   % name your BibTeX data base
+\bibliographystyle{spbasic} 
+\bibliography{arcana}
 
 \end{document}
-% end of file template.tex

### 2018-10-15 manuscript/manuscript.tex
touched up manuscript and examples

@@
 defining a method in the class that constructs and returns a
-\emph{Pipeline} object, and referencing that method in the class' data
-specification table. Pipeline objects are thin wrappers around Nipype
-workflows, which manage the namespaces of the workflow nodes, and should
-be created in constructor methods using the \emph{Study.new\_pipeline}
-method (Figure \ref{fig:pipeline_constructor}).
+\emph{Pipeline} object, and referencing the method by name in a FilesetSpec
+or FieldSpec in the class' data specification table. Pipeline objects are thin
+wrappers around Nipype workflows, which manage the namespaces of the
+workflow nodes, and should be created in constructor methods using the
+\emph{pipeline} method of the Study class (Figure \ref{fig:pipeline_constructor}).
 
@@
 
-At instantiation (via the new\_pipeline method) a Pipeline is passed the
-following arguments:
-
-\begin{itemize}
-\item
-  \begin{quote}
-  A name for the pipeline
-  \end{quote}
-\item
-  \begin{quote}
-  The inputs to the pipeline
-  \end{quote}
-\item
-  \begin{quote}
-  The output specifications the pipeline
-  \end{quote}
-\item
-  \begin{quote}
-  Description of the pipeline
-  \end{quote}
-\item
-  \begin{quote}
-  A list of scientific references the analysis was informed by
-  \end{quote}
-\item
-  \begin{quote}
-  Keyword arguments passed directly from the pipeline constructor method
-  \end{quote}
-\end{itemize}
-
-Inputs and outputs refer to entries in the data specification table and
-specify the file formats (fileset) or data type (field) that the input
-is expected in, or the output will be returned in. If this
-format/data-type differs from that specified in the data specification
-table then an implicit conversion will be performed when the pipeline is
-executed, thereby making data conversion transparent to the researcher.
-Every pipeline constructor should take only wildcard keyword arguments
-(i.e. **kwargs), which should be passed directly through to the
-new\_pipeline method to enable modification of the pipeline namespace by
-overriding methods in subclasses.
+% Need to introduce and explain new syntax
 
@@
 respectively.
+
+At initialisation, a Pipeline is given a name, which must be unique amongst the
+pipelines that can be constructed by the Study. A description of the pipeline and
+the list of scientific references
+
+Study class Inputs and outputs refer to entries in the data specification table and
+specify the file formats (fileset) or data type (field) that the input
+is expected in, or the output will be returned in. If this
+format/data-type differs from that specified in the data specification
+table then an implicit conversion will be performed when the pipeline is
+executed, thereby making data conversion transparent to the researcher.
+Every pipeline constructor should take only wildcard keyword arguments
+(i.e. **kwargs), which should be passed directly through to the
+new\_pipeline method to enable modification of the pipeline namespace by
+overriding methods in subclasses.
+
+% End reworked syntax explanation
 
@@
 \hline\noalign{\smallskip}
-\textbf{Type} & \textbf{Plain-directory} & \textbf{BIDS} & \textbf{XNAT}  \\
+\textbf{Datatype} & \textbf{Plain-directory} & \textbf{BIDS} & \textbf{XNAT}  \\
 \noalign{\smallskip}\hline\noalign{\smallskip}
-\textbf{Derivatives} & /\emph{subj}/\emph{vis}/\emph{study} & /derivatives/\emph{study}/\emph{subj}/\emph{vis} & /\emph{subj}/\emph{vis}\_\emph{study}\\
-\textbf{Fields} & \D/\_\_fields\_\_.json & \D/\_\_fields\_\_.json & MrSession XML \\ 
-\textbf{Provenance} & \D/\_\_prov\_\_/\emph{pl}.json & \D/\_\_prov\_\_/\emph{pl}.json & \D/\_\_prov\_\_/\emph{pl}.json \\
+Derivatives & /\emph{subj}/\emph{vis}/\emph{study} & /derivatives/\emph{study}/\emph{subj}/\emph{vis} & /\emph{subj}/\emph{vis}\_\emph{study}\\
+Fields & \D/\_\_fields\_\_.json & \D/\_\_fields\_\_.json & MrSession XML \\ 
+Provenance & \D/\_\_prov\_\_/\emph{pl}.json & \D/\_\_prov\_\_/\emph{pl}.json & \D/\_\_prov\_\_/\emph{pl}.json \\
 \noalign{\smallskip}\hline
@@
 \noalign{\smallskip}\hline\noalign{\smallskip}
-find\_data() & Queries repository to find all existing filesets and
+\emph{find\_data()} & Queries repository to find all existing filesets and
 fields \\
-get\_fileset(Fileset) & Caches file-set (if necessary) and returns the file path. \\
-get\_field(Field) & Retrieves and returns the value of the field from
+\emph{get\_fileset(Fileset)} & Caches file-set (if necessary) and returns the file path. \\
+\emph{get\_field(Field)} & Retrieves and returns the value of the field from
 the repository \\
-put\_fileset(Fileset) & Inserts file-set into the repository and updates cache. \\
-put\_field(Field) & Inserts the value of the Field into the repository \\
-connect() & Opens a connection to the repository (optional). \\
-disconnect() & Closes connection to repository (optional)\\
+\emph{put\_fileset(Fileset)} & Inserts file-set into the repository and updates cache. \\
+\emph{put\_field(Field)} & Inserts the value of the Field into the repository \\
+\emph{connect()} & Opens a connection to the repository (optional). \\
+\emph{disconnect()} & Closes connection to repository (optional)\\
 \noalign{\smallskip}\hline

### 2018-10-15 manuscript/listings/example_application.py

@@ -17,8 +17,7 @@ study = ExampleStudy(
     repository=XnatRepository(
         project_id='SAMPLE_PROJECT',
         server='https://central.xnat.org',
-        cache_dir=op.expanduser(
-            op.join('~', 'xnat-cache'))),
+        cache_dir=op.expanduser('~/xnat-cache')),
     # Specify the use the SLURM scheduler to submit
     # nodes as jobs using Nipype's SlurmGraphPlugin
     processor=SlurmProcessor(

### 2018-10-15 manuscript/listings/example_study.py

@@ -29,7 +29,7 @@ class ExampleStudy(Study, metaclass=StudyMetaClass):
         # Acquired fields
         AcquiredFieldSpec('acquired_field1', int,
                           frequency='per_subject'),
-        AcquiredFieldSpec('acquired_field2', float),
+        AcquiredFieldSpec('acquired_field2', float, optional=True),
         # "Acquired" file set with default value. Useful for
         # standard templates
         AcquiredFilesetSpec('template1', STD_IMAGE_FORMATS,

### 2018-10-15 manuscript/listings/example_study.py
renamed modifications to name_maps

@@ -57,11 +57,11 @@ class ExampleStudy(Study, metaclass=StudyMetaClass):
         # in the analysis
         SwitchSpec('pipeline_tool', 'toolA', ('toolA', 'toolB'))]
 
-    def pipeline2(self, **mods):
+    def pipeline2(self, **name_maps):
 
         pipeline = self.pipeline(
             name='pipeline2',
-            modifications=mods,
+            name_maps=name_maps,
             desc="Description of the pipeline",
             references=[methods_paper_cite])
 

### 2018-10-16 manuscript/manuscript.tex
renamed modifications to name_maps
finished reworking paper to include Environment and new pipeline syntax

@@
 \lstset{
-    basicstyle=\footnotesize,
     captionpos=b,                    % sets the caption-position to bottom
@@
 \begin{abstract}
+
 Insert your abstract here. Include keywords, PACS and mathematical
 subject classification numbers as needed.
-\keywords{First keyword \and Second keyword \and More}
+
+\keywords{Neuroimaging \and Workflows \and Repository \and Large-scale \and Reproducibility}
+
 % \PACS{PACS code1 \and PACS code2 \and more}
 % \subclass{MSC code1 \and MSC code2 \and more}
+
 \end{abstract}
@@
 
+% Provenanced mentioned here
+
 The utility of the Arcana framework is demonstrated by the
@@
 Object-Oriented (OO) software design. \emph{Study} classes encapsulate
-imaging data with the suite of analysis methods that can be performed on
-them, and, in the basic case, are specialised for a specific imaging
-contrast or modality. Study objects apply the analysis suite defined in
+types of data, such as scans of a specific imaging
+contrast or modality, with the suite of analysis methods that can be performed on
+them. Study objects apply the analysis suite defined in
 the Study class to a specific dataset.
@@
 \emph{table}. Class inheritance can be used to specialise analysis
-suites by overriding pipeline constructor methods or entries in the
-specification tables. Analysis suites for multi-modal data can be
-implemented by combining multiple Study classes in \emph{MultiStudy}
+suites by overriding entries in the specification tables or pipeline
+constructor methods. Analysis suites for multi-modal data can be
+implemented by combining Study classes within \emph{MultiStudy}
 classes\emph{.}
@@
 
-Analysis methods are applied to a specific dataset by instantiating an
-appropriate Study class and requesting a derivative listed in the class'
-data specification table. At instantiation, a Study object is passed
-references to \emph{Repository} and \emph{Processor} objects, which
-define how and where data is stored and processed. When a derivative is
-requested, a Study object queries the repository for intermediate
+Analysis methods defined by a Study class are applied to a
+specific dataset by instantiating an object of the class and
+requesting a derivative listed in the class' data specification table.
+At initialisation, a Study object is passed references to a \emph{Repository},
+a \emph{Processor}, and an \emph{Environment}, which
+define where and how data is stored and processed. When a derivative is
+requested, a Study object queries the Repository for intermediate
 derivatives that can be reused before constructing a workflow to produce
-the requested derivative. Workflows are executed in the computing
-environment specified by the Processor object and their products are
+the requested derivative. The manner in which the workflows are executed
+(i.e. single/multi-process or via SLURM scheduler) is specified by the
+Processor and software modules required by the analysis are
+loaded by the Environment. Selected workflow products are
 stored back in the repository for reuse by subsequent analyses (Figure
-\ref{fig:simple_uml}). Input data to the study are also stored in the repository, and are
-matched against entries in the class' data specification table using
-criteria defined in \emph{Selector} objects passed to the Study object
-at instantiation.
+\ref{fig:simple_uml}). Input data to a study are selected from repositories
+ using criteria defined in \emph{Selector} objects passed to the Study
+ object at initialisation and matched against entries in the class' data
+specification table.
 
@@
 tables}
-\label{data-and-parameter-specification-tables}
+\label{sec:data-and-parameter-specification-tables}
 
@@
 \emph{fileset} or \emph{field} type. Filesets represent single files,
-header and data file pairs, or sets of related files typically contained
-within single directories (e.g. a multi-volume DICOM dataset). Fields
-represent a single integer, floating point value or character string
-type. Each Fileset references a \emph{FileFormat} object, which
+or sets of related files typically contained within a directory
+(e.g. a multi-volume DICOM dataset). Fields
+represent integer, floating point or character string
+values. By default, a Field represents a single value but if the \emph{array}
+flag is set a Field represents a list of values.
+Each Fileset references a \emph{FileFormat} object, which
 specifies the formats of the files in the set. File formats are
@@
 \begin{figure}
-\lstinputlisting[language=Python, firstline=2, lastline=58]{listings/example_study.py}
+\lstinputlisting[basicstyle=\footnotesize,firstline=2, lastline=59]{listings/example_study.py}
 \caption{Example data and parameter specifications. The data
@@
 
-Both acquired and derived data specifications have a \emph{frequency}
-attribute which specifies where the data sits in the hierarchy of the
-dataset and can take the values \emph{per\_session},
-\emph{per\_subject}, \emph{per\_visit} or \emph{per\_study}. In
+All data specifications have a \emph{frequency} attribute which specifies
+where the data sits in the hierarchy of the
+dataset and can take the values 'per\_session',
+'per\_subject, 'per\_visit' or 'per\_study'. In
 addition, derived specifications are passed the name of a method in the
@@
 
-\subsubsection*{Workflow design}
-\label{workflow-design}
-
-Analysis workflows are implemented in Arcana as a series of pipelines
-that each perform a unit of the analysis (e.g. registration, brain
-extraction). Each pipeline is in turn constructed from a (typically
-small) graph of Nipype nodes, with each node wrapping a stand alone tool
+\subsubsection*{Workflow design: pipeline constructor methods}
+\label{sec:pipeline-constructors}
+
+Workflows are implemented in Arcana as a series of pipelines, which
+each perform a unit of the analysis (e.g. registration, brain
+extraction, quantitative susceptibility mapping). Pipelines are represented by \emph{Pipeline} objects,
+which are thin wrappers around Nipype workflows to handle input/output
+connections and namespace management. Each pipeline consists of a
+(typically small) graph of Nipype nodes, with each node wrapping a stand alone tool
 (e.g. FSL's FLIRT) or analysis package function (e.g. SPM's \emph{coreg}
-tool).
-
-Pipelines are included in the analysis suite of a Study class by
-defining a method in the class that constructs and returns a
-\emph{Pipeline} object, and referencing the method by name in a FilesetSpec
-or FieldSpec in the class' data specification table. Pipeline objects are thin
-wrappers around Nipype workflows, which manage the namespaces of the
-workflow nodes, and should be created in constructor methods using the
-\emph{pipeline} method of the Study class (Figure \ref{fig:pipeline_constructor}).
+tool). Pipelines source their inputs from, and sink their outputs to, entries
+in the data specification table, thereby linking the table together.
+
+Pipelines are constructed dynamically by ``pipeline constructor" methods
+of the study. Pipeline constructor methods are referenced by name in the \emph{pipeline\_name}
+argument of the FilesetSpec and FieldSpec objects of data specifications
+they derive. Pipeline constructor methods should only receive wildcard keyword
+arguments (e.g. \lstinline{my_pipeline(self, **name_maps)}), and these arguments
+should be passed as a dictionary directly to the \emph{name\_maps} argument
+of the pipeline initialisation to enable inputs and outputs of the
+pipeline to be rerouted to alternative data specifications in modified constructor
+methods, typically in subclasses and multi-studies.
 
 \begin{figure}
-\lstinputlisting[language=Python, firstline=59]{listings/example_study.py}
+\lstinputlisting[firstline=61, basicstyle=\footnotesize]{listings/example_study.py}
 \caption{Example pipeline constructor method. Pipelines are
-created using the \emph{create\_pipeline} method of the Study class.
-Pipeline objects are thin wrappers around Nipype workflows to allow for
-namespace management}
+created using the \emph{pipeline} method of the Study class.
+Pipeline objects are thin wrappers around Nipype Workflow objects to
+in order manage the namespaces of the workflow's inputs, outputs and nodes. Every
+pipeline constructor method should allow wildcard keyword arguments,
+which are passed to the \emph{name\_maps} argument of the pipeline
+initialisation. This allows pipeline constructors in sub and multi classes to map the
+inputs and outputs of the pipeline onto different data specifications.}
 \label{fig:pipeline_constructor}
@@
 
-% Need to introduce and explain new syntax
-
-The syntax for workflow graph construction in Arcana is inspired by the
-proposed format for Nipype v2.0
-(\href{http://github.com/nipy/nipype/issues/2539}{http://github.com/nipy/nipype/issues/2539}),
-and will be updated as Nipype v2.0 is developed and upstream
-functionality becomes available. Workflow nodes are created from Nipype
-interfaces using the \emph{add(name, interface)} method of the
-Pipeline should be used. Once created, the inputs of the node can be set
-explicitly via the node's \emph{inputs} attribute, connected to other
-nodes with the \emph{connect(out\_node, out\_node\_output,
-in\_node, in\_node\_input)} method, or connected to inputs of the
-pipeline. Pipeline inputs and outputs are connected to nodes using the
-\emph{add\_input(spec\_name, node, node\_input)} and
-\emph{add\_output(spec\_name, node, node\_output)} methods,
-respectively.
-
-At initialisation, a Pipeline is given a name, which must be unique amongst the
-pipelines that can be constructed by the Study. A description of the pipeline and
-the list of scientific references
-
-Study class Inputs and outputs refer to entries in the data specification table and
-specify the file formats (fileset) or data type (field) that the input
-is expected in, or the output will be returned in. If this
-format/data-type differs from that specified in the data specification
-table then an implicit conversion will be performed when the pipeline is
-executed, thereby making data conversion transparent to the researcher.
-Every pipeline constructor should take only wildcard keyword arguments
-(i.e. **kwargs), which should be passed directly through to the
-new\_pipeline method to enable modification of the pipeline namespace by
-overriding methods in subclasses.
-
-% End reworked syntax explanation
+The syntax for pipeline construction is inspired by a proposed form for Nipype v2.0
+(\href{http://github.com/nipy/nipype/issues/2539}{http://github.com/nipy/nipype/issues/2539}).
+Within a pipeline constructor, the Pipeline object is initialised by the \emph{pipeline} method
+of the Study (Figure \ref{fig:pipeline_constructor}). At initialisation, each pipeline is given a name,
+which must be unique amongst the pipelines constructed by the Study. The methods implemented
+by the pipeline can be characterised by providing a the list of scientific references
+and a text description to the \emph{references} and \emph{desc} keyword arguments, respectively.
+
+The \emph{add(name, interface)} method is used to add a node to a pipeline, which takes
+a unique name for the node (within the pipeline) and a Nipype Interface object, and returns
+a reference to the newly added node. For clarity, is recommended to put all static inputs
+(i.e. parameters) of the interface as keyword arguments of the interface constructor
+(Figure \ref{fig:pipeline_constructor}). However, if an input conditionally depends on a parameter of the
+study it can be set via the \emph{inputs} attribute of the node (e.g. \lstinline{my_node.inputs.my_param = 1.0}).
+
+Interface traits are connected to inputs and outputs of the pipeline by
+providing \emph{inputs} and \emph{outputs} keyword arguments to the \emph{add} method. Both
+arguments take a dictionary, where the keys of the dictionary are the names of traits of the interface. The
+values of the dictionary are 2-tuples each consisting of the name of a data specification
+and the format the pipeline expects the data in (i.e. a FileFormat for Fileset specifications or datatype
+for Field specifications). If the expected format does not match that of the corresponding data specification
+table or study input then an conversion nodes are implicitly connected to the pipeline.
+Inputs and outputs that are conditional on parameters of the study can be set outside of
+the \emph{add} method using the \emph{connect\_input} or
+\emph{connect\_output} methods, respectively.
+
+Internal connections between nodes within a pipeline are specified by a dictionary
+passed to the \emph{connect} keyword argument of the receiving node. The
+dictionary keys are the names of the receiving traits and the values are 2-tuples
+consisting of the sending node and the name of the sending trait. Alternatively,
+conditional connections can be specified via the \emph{connect} method of the
+pipeline, which simply calls the method of the same name in the underlying
+Nipype workflow.
 
@@
 requirements can be used by the Processor to configure environment
-modules \citep{furlani_modules:_1991} if present, to ensure the required software
+modules \citep{furlani_modules:_1991}, to ensure the required software
 packages are available. Similarly, the expected memory requirements and
-wall time for the node execution should be provided as keyword args,
-\emph{memory}, and \emph{wall\_time}, so they can be inserted into job
-scripts submitted to schedulers by HPC Processors.
+wall time for the node execution should be provided to the keyword args
+\emph{memory}, and \emph{wall\_time} so they can be inserted into HPC
+scheduler job scripts if required.
 
@@
 depends on the frequency of the pipeline's inputs and outputs. To create
-a summary derivative (i.e. frequency != \emph{per\_session}) from more
-frequent data a join node is used. Join nodes that join over subjects or
-visits are created with \emph{add}\_\emph{join\_subjects(name,
-interface, joinfield)} and \emph{add\_join\_visits(name,
-interface, joinfield)} respectively. As in the underlying Nipype, the
-\emph{joinfield} argument specifies which inputs of the receiving node
-to join into lists. If direct access to the subject or visit IDs is
-required by a node they can be connected to the implicit iterator nodes
-with \emph{connect\_subject\_id(node, name)} and
-\emph{connect\_visit\_id} respectively. Note that expansion
-over iterator sources is handled implicitly by Nipype when nodes with
-different iterators are connected to a downstream node.
+a summary derivative (i.e. frequency != 'per\_session') from more frequent
+data, \emph{Study.SUBJECT\_ID} or \emph{Study.VISIT\_ID} should be
+passed to the \emph{joinsource} keyword to join over subjects or visits, respectively.
+In this case, a JoinNode will be created instead of standard Node,
+which should be passed the additional keyword argument \emph{joinfield} to
+specify the list of input traits to convert into lists to receive the joined input.
+Similarly, if the name of an input trait is provided (or list thereof) to the the \emph{iterfield}
+keyword argument, then a MapNode will be created and the interface will
+be applied to all items of the list connected to that input \citep{gorgolewski_nipype:_2011}.
+The subject and visit IDs are directly accessible as input fields of the pipeline
+named \emph{Study.SUBJECT\_ID} and \emph{Study.VISIT\_ID}, respectively.
 
@@
 parameter. The analysis branch designated by a switch value should be
-tested with \emph{branch(name, ref\_value)} method.
+tested with \emph{branch(name)} in the case of boolean switches and
+\emph{branch(name, ref\_value)} in the case of string switches.
 
@@
 
-Pipeline constructors can be overridden in subclasses like any Python
-method. Typically the overriding method will call the superclass method
-to construct a base Pipeline, apply modifications and return the
-modified Pipeline. In this scenario, references to the data
-specification in the superclass method can be mapped onto different
-entries in the subclass by passing a dictionary containing the maps to
-the \emph{name\_map} keyword argument of pipeline constructor in the
-superclass.
-
-Instead of setting the class attributes directly, the data and parameter
-specifications are set by the metaclas\emph{s}, in order to combine with
-specifications from base classes. The combined data and parameter
-specifications are constructed by visiting the class' bases in reverse
-method resolution order (MRO) and adding specifications from their
-\emph{add\_data\_specs}, \emph{add\_param\_specs} attributes,
+Instead of being set directly, the data and parameter specifications are set
+by the metaclass of the Study (i.e. StudyMetaClass),
+in order to combine them with corresponding specifications in the class' bases. The combined
+data and parameter specifications are constructed by visiting the class'
+bases in reverse method resolution order (MRO) and adding specifications
+from their \emph{add\_data\_specs}, \emph{add\_param\_specs} attributes,
 overriding previously added specifications with matching names. Note
@@
 inherited from base classes.
+
+Pipeline constructor methods can be overridden in subclasses like any Python
+method. Often the overriding method will call the superclass method
+to construct a pipeline, apply modifications and return the
+modified pipeline. In this scenario, references to the data
+specification in the superclass method can be mapped onto different
+entries in the table of the subclass by providing the \emph{input\_map} and
+\emph{output\_map} keyword arguments when calling the superclass method.
+Additionally the name of the pipeline can be altered by providing the \emph{name}
+argument, which is useful when creating multiple  constructor methods from the
+one base method. In these scenarios it is important to
+also pass the the wildcard keyword arguments of the overriding method to the
+\emph{name\_maps} keyword argument of the superclass method, to allow the
+overriding method to be overridden in turn.
 
@@
 dataset, an instance of the Study class is created with details of where
-the data is stored (the \emph{Repository}) and the computing environment
-available to process it (the \emph{Processor}). A Study object controls
-the construction of analysis workflows, the execution of the workflows,
+the data is stored (\emph{Repository} module) the computing
+resources available to process it (\emph{Processor} module) and the software
+installed in the environment it will be processed in (\emph{Environment} module).
+A Study object controls the construction and execution of analysis workflows,
 and the flow of data to and from the repository (Figure \ref{fig:full_uml}).
@@
 
-Each Study object is assigned a name, which is used to differentiate its
-results from alternative analyses on the same dataset (e.g. by different
-members of a lab). Parameters are set on initialisation of the Study
-object along with the range of subject and visit IDs to be included in
-the analysis (if they are not provided then all IDs are included). The
-remaining arguments passed to the Study object initialisation are the
-Repository and Processor modules and a list of \emph{Selector} objects
-to select input datasets from the repository (Figure \ref{fig:study_application}).
+Each Study instance is assigned a name, which is used to differentiate its
+results from alternative analyses on the same dataset (e.g. with different
+parameterisations). Parameters are set on initialisation of the Study object
+along with the range of subject and visit IDs to be included in the analysis
+(if they are not provided then all IDs found in the repository are included).
+The remaining arguments passed to the Study object initialisation are the
+Repository, Processor and Environment modules to use and a list of
+\emph{Selector} objects to select input data from the repository and match
+it with the Study's data specification table.
+(Figure \ref{fig:study_application}).
 
 \begin{figure}
-\lstinputlisting[language=Python]{listings/example_application.py}
+\lstinputlisting[basicstyle=\footnotesize]{listings/example_application.py}
 \caption{Example application of Study class to a dataset stored in an XNAT
@@
 mapped from their values in the auxiliary repositories to the ``ID
-space'' of the study. This mapping is specified using \emph{IdMapper}
-objects passed to \emph{subject\_id\_map} and \emph{visit\_id\_map}
-keyword arguments during initialisation of a repository.
+space'' of the study, which can be done by passing either by a dictionary
+or callable object (e.g. function) to the \emph{subject\_id\_map} or
+\emph{visit\_id\_map} keyword arguments during initialisation of a repository.
 
@@
 implemented by extending the Repository abstract base class and
-implementing a small set of methods (Table \ref{tbl:abstract-repo-methods}).
+implementing five abstract methods, \emph{find\_data}, \emph{get\_fileset},
+\emph{get\_field}, \emph{put\_fileset} and \emph{put\_field}
+(Table \ref{tbl:abstract-repo-methods}).
 
@@
 fields \\
-\emph{get\_fileset(Fileset)} & Caches file-set (if necessary) and returns the file path. \\
+\emph{get\_fileset(Fileset)} & Caches fileset (if necessary) and returns the path to file(s). \\
 \emph{get\_field(Field)} & Retrieves and returns the value of the field from
 the repository \\
-\emph{put\_fileset(Fileset)} & Inserts file-set into the repository and updates cache. \\
+\emph{put\_fileset(Fileset)} & Inserts fileset into the repository and updates cache. \\
 \emph{put\_field(Field)} & Inserts the value of the Field into the repository \\
@@
 distinguish cases where multiple filesets in the session match the
-pattern provided, such as DICOM header values, or when using an XNAT
-repository, the order and ID of the dataset.
+pattern provided, such as DICOM header values, or the order and ID
+of the dataset.
 
@@
 
-If the data to select has been derived from an alternative study, then
-the name of the alternative study can be passed to the
+If the data to select has been derived from an alternative Arcana Study
+instance, then the name of the alternative study can be passed to the
 \emph{from\_study} keyword argument provided to the selector. There are
@@
 templates as inputs to analyses. They can also be set as the ``default
-input'' for a data spec using the \emph{default\_input} keyword
-argument. For the sake of portability, default inputs should be
-restricted to data in publically accessible repositories or included in
+input'' for a data specification via the \emph{default} keyword
+argument. However, for the sake of portability, default inputs should be
+restricted to data in publically accessible repositories or those included in
 standard software packages (e.g. FSL).
@@
 
-Processor modules control how and where pipelines generated by a Study
-are executed. There currently four Processor modules implemented in
+Processor modules control how pipelines generated by a Study
+are executed. There currently three Processor modules implemented in
 Arcana: \emph{LinearProcessor}, \emph{MultiProcProcessor},
-\emph{SlurmProcessor} and \emph{SgeProcessor}, which wrap the
+\emph{SlurmProcessor}, which wrap the
 correspondingly named Nipype execution plugins. The main task performed
@@
 
-A processor is used internally by a Study instance to execute pipelines
+A Processor is used internally by a Study instance to execute pipelines
 to derive derivatives requested from the data specification by the
-\emph{Study.data(name{[}, name,...{]})} method (Figure \ref{fig:simple_uml}). The first
+\emph{data(name{[}, name,...{]})} method (Figure \ref{fig:simple_uml}). The first
 step in this procedure is to query the repository tree for all data and
 provenance associated with the study. Sessions for which the requested
-outputs of the pipeline are already present in the repository are
+outputs of the pipeline are already present in the repository, and the stored
+provenance matches the current parameters of the study,
 excluded from the list to process. For the remaining sessions to
@@
 
-When a pipeline is processed it is connected to \emph{Source} and
-\emph{Sink} nodes, which get and put the pipeline inputs and outputs
+When a pipeline is processed it is connected to source and
+sink nodes, which get and put the pipeline inputs and outputs
 from and to a repository, respectively. Separate source and sink nodes
@@
 nodes or before the sink nodes. Iterator nodes that iterate over the
-required subjects and visits are connected to the sources, and report
+required subjects and visits are connected to the sources, and ``deiterator''
 nodes that join over subjects and visits are connected to the sink
-nodes. Report nodes of upstream pipelines are connected to downstream
-iterator nodes to create a single workflow, which is then executed using
+nodes. Final nodes of upstream pipelines are connected to downstream
+iterator nodes in order to create a single workflow, which is then executed using
 the Nipype execution plugin.
-
-Software versions are managed by the processor if environment modules
-\citep{furlani_modules:_1991} are installed on the system. These are loaded and
-unloaded before the interface of a workflow node is run based on the
-requirements specified for the node during construction of the pipeline
-(see \emph{Pipeline constructors}. Maps from requirement names to
-module names in the processing environment can be passed to the
-Processor at initialisation. For plugins that submit jobs to HPC
-schedulers (e.g. SLURM, SGE), node memory and wall-time requirements are
-inserted into jobscripts where required.
 
@@
 
+\subsubsection*{Environment modules}
+
+The software packages installed on the system are detected and managed
+by the Environment module. There are currently two types of available Environment modules:
+\emph{StaticEnvironment} and \emph{ModulesEnvironment}.
+
+The \emph{StaticEnvironment} module doesn't perform any management, and instead
+only checks the existing environment for appropriate software versions before running
+the analysis.
+
+The \emph{ModulesEnvironment} module can be used if environment
+modules \citep{furlani_modules:_1991} are installed on the system (typical in many
+HPC environments). In this case, modules are loaded before the interface of a pipeline node
+is run based on the requirements specified for the node during construction of the pipeline
+(see \emph{Pipeline constructors} and then unloaded afterwards. Mappings from non-standard
+module names installed on the system to requirements required by the Study can be
+can be passed to the \emph{packages\_map} keyword argument of the ModulesEnvironment
+at initialisation. Likewise non-standard versions for packages can be mapped onto requirements
+using the \emph{versions\_map} keyword argument.
+
 \section*{Results}
@@
 The Arcana framework is distributed as a publicly available software
-package via GitHub
-(\href{http://github.com/MonashBI/arcana}{{http://github.com/MonashBI/arcana}})
-and the Python Package Index (PyPI)
-(\href{https://pypi.org/project/arcana/}{{http://pypi.org/project/arcana/}}).
+package via GitHub (\url{github.com/MonashBI/arcana}) and the
+Python Package Index (PyPI) (\url{pypi.org/project/arcana/}).
 Study classes for T1, T2* and diffusion weighted MRI data have been
-implemented as part of the \emph{Biomedical imAgiNg ANAlysis (Banana)} package \\
-(\href{https://github.com/MonashBI/banana}{{http://github.com/MonashBI/banana}} and
-\href{http://pypi.org./project/banana}{{http://pypi.org./project/banana}}).
-All three classes, \emph{T1wStudy}, \emph{T2starwStudy} and
+implemented as part of the \emph{Biomedical imAgiNg ANAlysis (Banana)} package
+(\url{github.com/MonashBI/banana}; \url{pypi.org./project/banana}).
+All three classes, \emph{T1Study}, \emph{T2starStudy} and
 \emph{DmriStudy}, inherit generic image analysis methods, such as
@@
 The T1Study and T2starStudy classes are aggregated into the
-\emph{T2starwT1wStudy} MultiStudy class to combine analysis of T2* and
+\emph{T2starwT1Study} MultiStudy class to combine analysis of T2* and
 T1-weighted contrasts.
@@
 
-The \emph{T2starwT1wStudy} class implements an algorithm to generate
+The \emph{T2starwT1Study} class implements an algorithm to generate
 \emph{composite vein images} from the combination of QSM and SWI
@@
 An oft-repeated mantra in the open-source software movement dubbed
-Linus' Law is that "given a large enough beta-tester and co-developer
+Linus' Law is that ``given a large enough beta-tester and co-developer
 base, almost every problem will be characterized quickly and the fix
-obvious to someone" or more compactly, "given enough eyeballs, all
+obvious to someone" or more compactly, ``given enough eyeballs, all
 \href{https://en.wikipedia.org/wiki/Software_bug}{bugs} are shallow"
@@
 However, it has been difficult for researchers to collaborate on the
-same code base due to slight differences in acquisition protocols,
+same code-base due to slight differences in acquisition protocols,
 storage conventions, researcher preferences, and study requirements.
@@
 eyeballs to detect and fix errors, has the potential to form a
-reinforcing cycle where in more developers are attracted to the project.
+reinforcing cycle where more developers are attracted to the project.
 To these ends, the Banana code repository on GitHub
 (\url{http://github.com/MonashBI/banana.git}) is proposed as a code base
-for communal development of neuroimaging workflows in Arcana.
+for communal development of biomedical imaging workflows using Arcana.
 
@@
 algorithm updates. In systems with environment modules \citep{furlani_modules:_1991}
-installed, Arcana loads and unloads the required modules before and
+installed, Arcana can load and unload the required modules before and
 after each node is executed. When running Arcana within a container,
@@
 (\href{http://hub.docker.com/r/monashbi/banana}{{http://hub.docker.com/r/monashbi/banana}}),
-which can be used as a base for neuroimaging analysis containers.
+which can be used as a base for biomedical imaging analysis containers.
 
@@
 Infrastructure Strategy (NCRIS) capability, at Monash Biomedical Imaging,
-Monash University. \textbf{Salary support for me ??} Early versions of the software described in the manuscript
-were informed by existing software written Parnesh Raniga while
-employed at Monash Biomedical Imaging.
+Monash University. The ``transparent repository'' feature of Arcana was
+inspired by in-house software written by Parnesh Raniga while he was
+employed at Monash Biomedical Imaging prior to 2016.
 \end{acknowledgements}

### 2018-10-16 manuscript/listings/example_study.py

@@ -27,7 +27,7 @@ class ExampleStudy(Study, metaclass=StudyMetaClass):
         AcquiredFilesetSpec('acquired_file1', text_format),
         AcquiredFilesetSpec('acquired_file2', STD_IMAGE_FORMATS),
         # Acquired fields
-        AcquiredFieldSpec('acquired_field1', int,
+        AcquiredFieldSpec('acquired_field1', int, array=True,
                           frequency='per_subject'),
         AcquiredFieldSpec('acquired_field2', float, optional=True),
         # "Acquired" file set with default value. Useful for
@@ -42,7 +42,7 @@ class ExampleStudy(Study, metaclass=StudyMetaClass):
         FilesetSpec('derived_file4', dicom_format, 'pipeline3'),
         FilesetSpec('derived_file5', nifti_gz_format, 'pipeline3',
                     frequency='per_subject'),
-        FilesetSpec('derived_file6', text_format, 'pipeline4',
+        FilesetSpec('derived_file6', analyze_format, 'pipeline2',
                     frequency='per_visit'),
         # Derived fields
         FieldSpec('derived_field1', float, 'pipeline2'),
@@ -55,7 +55,8 @@ class ExampleStudy(Study, metaclass=StudyMetaClass):
         ParameterSpec('parameter2', 25.8),
         # "Switch" parameters that specify a qualitative change
         # in the analysis
-        SwitchSpec('pipeline_tool', 'toolA', ('toolA', 'toolB'))]
+        SwitchSpec('node1_option', False),  # Boolean switch
+        SwitchSpec('pipeline2_tool', 'toolA', ('toolA', 'toolB'))]
 
     def pipeline2(self, **name_maps):
 
@@ -69,7 +70,7 @@ class ExampleStudy(Study, metaclass=StudyMetaClass):
             'node1',
             Interface1(
                 param1=3.5,
-                param3=self.parameter('parameter1')),
+                param2=self.parameter('parameter1')),
             inputs={
                 'in_file1': ('acquired_file1', text_format),
                 'in_file2': ('acquired_file2', analyze_format),
@@ -77,8 +78,10 @@ class ExampleStudy(Study, metaclass=StudyMetaClass):
             outputs={
                 'out_field': ('derived_field1', int)},
             wall_time=25, requirements=[software_req1])
+        if self.branch('node1_option'):
+            node1.inputs.option = 'set-extra-option'
 
[…]

### 2018-10-16 arcana_paper.py
updated file locations

@@ -1,7 +1,8 @@
 from arcana import (
     MultiStudy, MultiStudyMetaClass, SubStudySpec, ParameterSpec)
 from nianalysis.study.mri.structural.diffusion import DiffusionStudy
-# from nianalysis.study.mri.structural.t2star import T2starwT1wStudy
+from nianalysis.study.mri.structural.t1 import T1Study
+from nianalysis.study.mri.structural.t2star import T2StarStudy
 from nianalysis.plot import ImageDisplayMixin
 import os.path as op
 
@@ -16,7 +17,13 @@ class ArcanaPaper(MultiStudy, ImageDisplayMixin,
 
     add_sub_study_specs = [
         # Include two Study classes in the overall study
-#         SubStudySpec('t2star', T2starwT1wStudy),
+        SubStudySpec(
+            't1', T1Study),
+        SubStudySpec(
+            't2star', T2StarStudy,
+            name_map={'t1_brain': 'coreg_ref_brain',
+                      't1_coreg_to_atlas_mat': 'coreg_to_atlas_mat',
+                      't1_coreg_to_atlas_warp': 'coreg_to_atlas_warp'}),
         SubStudySpec('dmri', DiffusionStudy)]
 
     add_param_specs = [
@@ -41,11 +48,10 @@ class ArcanaPaper(MultiStudy, ImageDisplayMixin,
         # and vein mask data in the repository.
         swis = self.data('t2star_swi')
         qsms = self.data('t2star_qsm')
-        vein_atlases = self.data('t2star_vein_atlas')
+        cv_image = self.data('t2star_composite_vein_image')
         vein_masks = self.data('t2star_vein_mask')
         # Loop through all sessions
-        for swi, qsm, vein_atlas, vein_mask in zip(swis, qsms,
-                                                   vein_atlases,
+        for swi, qsm, vein_atlas, vein_mask in zip(swis, qsms, cv_image,
                                                    vein_masks):
             # Display slices from the filesets in a panel using
             # method from the ImageDisplayMixin base class.
@@ -115,12 +121,12 @@ class ArcanaPaper(MultiStudy, ImageDisplayMixin,
 if __name__ == '__main__':
     from arcana import (
         DirectoryRepository, LinearProcessor, FilesetSelector)
-    from nianalysis.file_format import dicom_format
+    from nianalysis.file_format import dicom_format, zip_format
     import os
 
     # Path to data, work and output directories
     this_dir = op.dirname(__file__)
[…]

### 2018-10-17 manuscript/manuscript.tex
added in references and fixed vein images so that they show up in correct aspect

@@
 % your LaTeX will extract the file if required
-\begin{filecontents*}{example.eps}
-%!PS-Adobe-3.0 EPSF-3.0
-%%BoundingBox: 19 19 221 221
-%%CreationDate: Mon Sep 29 1997
-%%Creator: programmed by hand (JK)
-%%EndComments
-gsave
-newpath
-  20 20 moveto
-  20 220 lineto
-  220 220 lineto
-  220 20 lineto
-closepath
-2 setlinewidth
-gsave
-  .4 setgray fill
-grestore
-stroke
-grestore
-\end{filecontents*}
-%
+
 \RequirePackage{fix-cm}
-%
+
 %\documentclass{svjour3}                     % onecolumn (standard format)
@@
 %\documentclass[twocolumn]{svjour3}          % twocolumn
-%
+
 \smartqed  % flush right qed marks, e.g. at end of proof
-%
+
+% \usepackage{mathptmx}      % use Times fonts if available on your TeX system
+
 \usepackage{natbib}
@@
 
-% \usepackage{mathptmx}      % use Times fonts if available on your TeX system
-%
-% insert here the call for the packages your document requires
-%\usepackage{latexsym}
-% etc.
-%
-% please place your own definitions here and don't use \def but
-% \newcommand{}{}
-
 \newcommand{\D}{...}
@@
 
-%
 % Insert the name of "your journal" with
 % \journalname{myjournal}
-%
+
 \begin{document}
@@
 \title{A comprehensive framework to capture the arcana of neuroimaging
-analysis%\thanks{Grants or other notes
-%about the article that should go on the front page should be
-%placed here. General acknowledgments should be placed at the end of the article.}
+analysis
 }
@@
 	Zhaolin Chen  \and
-	Gary F. Egan  \and} % if too long for running head
+	Gary F. Egan}
 
@@
 
-Insert your abstract here. Include keywords, PACS and mathematical
-subject classification numbers as needed.
-
-\keywords{Neuroimaging \and Workflows \and Repository \and Large-scale \and Reproducibility}
-
-% \PACS{PACS code1 \and PACS code2 \and more}
-% \subclass{MSC code1 \and MSC code2 \and more}
+These are the notes I have for my abstract
+
+\begin{itemize}
+\item The heterogeneous collection of neuroimaging analysis tools, parameters, styles makes it difficult to design comprehensive workflows
+\item Complex workflows in a flexible extensible manner, reusable
+\item portable between different data storage solutions/scale of studies, separation between design and application yet programmatic
+\item Easily updatable, switchable between tools/versions
+\end{itemize}
+
+\keywords{Neuroimaging \and Workflows \and Repository \and Reproducibility \and Reusability \and Large-scale \and Python}
 
@@
 Despite the availability of well-established neuroimaging analysis
-packages \citep{cox_afni:_1996,smith_advances_2004,friston_statistical_2007,tournier_mrtrix:_2012}, the arcana of neuroimaging analysis is substantial due to
+packages \citep{cox_afni:_1996,smith_advances_2004,friston_statistical_2007,tournier_mrtrix:_2012},
+the arcana of neuroimaging analysis is substantial due to
 the range of available tools, tuneable parameters, and imaging sequences
@@
 conventions, which facilitate the design of portable \emph{BIDS Apps}
-(https://bids-apps.neuroimaging.io). However, for research groups with
-sufficient informatics support, software-managed repositories \citep{marcus_extensible_2007,das_loris:_2012} can provide additional features, such as
+(\url{bids-apps.neuroimaging.io}). However, for research groups with
+sufficient informatics support, software-managed repositories \citep{marcus_extensible_2007,das_loris:_2012}
+can provide additional features, such as
 flexible access-control and automated pipelines. Therefore, for
@@
 Programmatic construction allows for rich control-flow logic that is not
-readily available in alternative workflow frameworks \citep{cusack_automatic_2015,achterberg_fastr:_2016,amstutz_common_2016}, and has been used
+readily available in alternative workflow frameworks \citep{cusack_automatic_2015,achterberg_fastr:_2016,amstutz_common_2016},
+and has been used
 to implement workflows that are robust to differences in fMRI protocols
@@
 neuroimaging analyses. \emph{Abstraction of Repository-Centric ANAlysis
-(Arcana)} \\(\href{http://arcana.readthedocs.io}{http://arcana.readthedocs.io} is a Python framework for
+(Arcana)} (\url{arcana.readthedocs.io}) is a Python framework for
 designing complex workflows in which modular Nipype pipelines operate on
@@
 modules \citep{furlani_modules:_1991} are installed on the system (typical in many
-HPC environments). In this case, modules are loaded before the interface of a pipeline node
-is run based on the requirements specified for the node during construction of the pipeline
-(see \emph{Pipeline constructors} and then unloaded afterwards. Mappings from non-standard
+HPC environments). In this case, modules are loaded before a workflow node is run,
+based on the requirements specified for the node during construction of the pipeline
+(see \emph{Pipeline constructors}), and then unloaded afterwards. Mappings from non-standard
 module names installed on the system to requirements required by the Study can be
@@
 \emph{DmriStudy}, inherit generic image analysis methods, such as
-registration and brain extraction, from the base class \emph{MRIStudy}.
+registration and brain extraction, from the base class \emph{MriStudy}.
 The T1Study and T2starStudy classes are aggregated into the
-\emph{T2starwT1Study} MultiStudy class to combine analysis of T2* and
+\emph{T2starT1Study} MultiStudy class to combine analysis of T2* and
 T1-weighted contrasts.
@@
 
-The \emph{T2starwT1Study} class implements an algorithm to generate
+The \emph{T2starT1Study} class implements an algorithm to generate
 \emph{composite vein images} from the combination of QSM and SWI
 contrasts derived from the T2*-weighted acquisition with an vein atlas
-registered to the T1-weighted acquisition \citep{ward_combining_2018} (Figure \ref{fig:t2star_t1_study}).
+registered to the T1-weighted acquisition \citep{ward_combining_2018}.
+(Figure \ref{fig:t2star_t1_study}).
 
@@
 110x100x60, FOV 256x240x192, TE = 95ms, TR, = 8200ms, 33 diffusion
-directions with b=1500 mm2/s and 3 b=0, bandwidth=781Hz/pixel)
-(\textbf{cite Lifespan paper ??}). Methods for Figure \ref{fig:veins}, \ref{fig:fa_acs},
-and \ref{fig:tractography} in
+directions with b=1500 mm2/s and 3 b=0, bandwidth=781Hz/pixel).
+Methods for Figure \ref{fig:veins}, \ref{fig:fa_adc}, and \ref{fig:tractography} in
 the ArcanaPaper class were applied to the acquired dataset to using the
@@
 
-Figure \ref{fig:veins} displays composite vein images and vein masks for the healthy
+Figure \ref{fig:veins} displays composite vein images for the healthy
 volunteer along with the SWI and QSM intermediate derivatives and the
 input vein atlas. The derived vein images are comparable to those
-generated by the original implementation \citep{ward_combining_2018}. The complete
-workflow took ?? min to complete over ?? compute cores.
+generated by the original implementation \citep{ward_combining_2018}.
 
@@
     \includegraphics[width=\textwidth]{figures/veins}
-  \caption{Vein image (\emph{right column}) constructed by
-combining susceptibility weighted imaging (SWI) (\emph{left column}),
-quantitative susceptibility mapping (QSM) (\emph{left-middle column})
-and a vein atlas from manual tracings (\emph{right-middle column}).
-\emph{Top row}: sagittal slices. \emph{Middle row}: axial slices.
-\emph{Bottom row}: coronal slices.}
+  \caption{Composite vein image (\emph{third row}) constructed by
+  combining susceptibility weighted imaging (SWI) (\emph{top row}),
+  quantitative susceptibility mapping (QSM) (\emph{second row})
+  and a vein atlas from manual tracings. A vein mask was then
+  generated (\emph{bottom row}) by thresholding the composite
+  vein image.
+  \emph{left column}: axial slices. \emph{centre column}: coronal slices.
+  \emph{right column}: sagittal slices.}
 \label{fig:veins}
@@
 To these ends, the Banana code repository on GitHub
-(\url{http://github.com/MonashBI/banana.git}) is proposed as a code base
+(\url{github.com/MonashBI/banana.git}) is proposed as a code base
 for communal development of biomedical imaging workflows using Arcana.
@@
 bridge between the two communities of users and developers. Alternative
-data storage systems \citep{scott_coins:_2011,das_loris:_2012,book_neuroinformatics_2013}, can be integrated into Arcana by overriding a small number of
+data storage systems \citep{scott_coins:_2011,das_loris:_2012,book_neuroinformatics_2013},
+can be integrated into Arcana by overriding a small number of
 methods from the Repository abstract base class. Repository modules
-could also be created for data portals such as \emph{DataLad} \citep{yaroslav_halchenko_datalad/datalad_2018} in order to take advantage of the range of platforms they support.
+could also be created for data portals such as \emph{DataLad}
+\citep{yaroslav_halchenko_datalad/datalad_2018}
+in order to take advantage of the range of platforms they support.
 Implementing analyses in Arcana therefore enables researchers and
@@
 Docker container is available on Docker Hub,
-(\href{http://hub.docker.com/r/monashbi/banana}{{http://hub.docker.com/r/monashbi/banana}}),
-which can be used as a base for biomedical imaging analysis containers.
+(\url{hub.docker.com/r/monashbi/banana}), which can be used as a
+base for biomedical imaging analysis containers. In future versions of Arcana,
+additional Environment modules could be implemented to run each pipeline
+node within its own container if required to take advantage of
+containers maintained by tool developers (e.g. 
+\url{hub.docker.com/r/vistalab/freesurfer/}).
 
@@
 with different combinations of available tools and only present results
-that are robust to the ``analytic noise'' (cite here?) they introduce.
+that are robust to the ``analytic noise'' \citep{maumet:inserm-01886089} they introduce.
 Switch parameters make it straightforward to rerun analyses in Arcana
@@
 inspired by in-house software written by Parnesh Raniga while he was
-employed at Monash Biomedical Imaging prior to 2016.
+employed at Monash University prior to 2016.
 \end{acknowledgements}

### 2018-10-17 arcana_paper.py

@@ -1,8 +1,7 @@
+#!/usr/bin/env python3
 from arcana import (
     MultiStudy, MultiStudyMetaClass, SubStudySpec, ParameterSpec)
-from nianalysis.study.mri.structural.diffusion import DiffusionStudy
-from nianalysis.study.mri.structural.t1 import T1Study
-from nianalysis.study.mri.structural.t2star import T2StarStudy
+from nianalysis.study.mri import (DiffusionStudy, T1Study, T2StarStudy)
 from nianalysis.plot import ImageDisplayMixin
 import os.path as op
 
@@ -18,13 +17,17 @@ class ArcanaPaper(MultiStudy, ImageDisplayMixin,
     add_sub_study_specs = [
         # Include two Study classes in the overall study
         SubStudySpec(
-            't1', T1Study),
+            't1',
+            T1Study),
         SubStudySpec(
-            't2star', T2StarStudy,
+            't2star',
+            T2StarStudy,
             name_map={'t1_brain': 'coreg_ref_brain',
                       't1_coreg_to_atlas_mat': 'coreg_to_atlas_mat',
                       't1_coreg_to_atlas_warp': 'coreg_to_atlas_warp'}),
-        SubStudySpec('dmri', DiffusionStudy)]
+        SubStudySpec(
+            'dmri',
+            DiffusionStudy)]
 
     add_param_specs = [
         ParameterSpec(
@@ -53,12 +56,17 @@ class ArcanaPaper(MultiStudy, ImageDisplayMixin,
         # Loop through all sessions
         for swi, qsm, vein_atlas, vein_mask in zip(swis, qsms, cv_image,
                                                    vein_masks):
+            # Set the saturation limits for the QSM image
+            row_kwargs = [{} for _ in range(4)]
+            row_kwargs[1]['vmax_percentile'] = 95
+            row_kwargs[1]['vmin_percentile'] = 5
             # Display slices from the filesets in a panel using
             # method from the ImageDisplayMixin base class.
             self.display_slice_panel(
-                (swi, qsm, vein_atlas, vein_mask), **kwargs)
+                (swi, qsm, vein_atlas, vein_mask),
+                row_kwargs=row_kwargs, **kwargs)
             # Display or save to file the generated image.
-            self.save_or_show(save_path, swi.subject_id, swi.visit_id)
+            self.show(save_path, swi.subject_id, swi.visit_id)
 
[…]

### 2018-10-17 manuscript/listings/example_study.py

@@ -79,7 +79,7 @@ class ExampleStudy(Study, metaclass=StudyMetaClass):
                 'out_field': ('derived_field1', int)},
             wall_time=25, requirements=[software_req1])
         if self.branch('node1_option'):
-            node1.inputs.option = 'set-extra-option'
+            node1.inputs.an_option = 'set-extra-option'
 
         if self.branch('pipeline2_tool', 'toolA'):
             pipeline.add(

### 2018-10-17 manuscript/manuscript.tex
finished touching up results and methods sections, only the abstract to write

@@
 extraction, quantitative susceptibility mapping). Pipelines are represented by \emph{Pipeline} objects,
-which are thin wrappers around Nipype workflows to handle input/output
-connections and namespace management. Each pipeline consists of a
+which are thin wrappers around Nipype workflows to handle input and output
+connections, and namespace management. Each pipeline consists of a
 (typically small) graph of Nipype nodes, with each node wrapping a stand alone tool
@@
 pipeline to be rerouted to alternative data specifications in modified constructor
-methods, typically in subclasses and multi-studies.
+methods, typically in subclasses and multi-studies (see
+\emph{Extension and specialisation by class inheritance} and \emph{Implementing multi-modal studies}).
 
@@
 The syntax for pipeline construction is inspired by a proposed form for Nipype v2.0
-(\href{http://github.com/nipy/nipype/issues/2539}{http://github.com/nipy/nipype/issues/2539}).
-Within a pipeline constructor, the Pipeline object is initialised by the \emph{pipeline} method
-of the Study (Figure \ref{fig:pipeline_constructor}). At initialisation, each pipeline is given a name,
+(\url{github.com/nipy/nipype/issues/2539}).
+Within a pipeline constructor method, a Pipeline object is constructed by the \emph{Study.pipeline} method
+(Figure \ref{fig:pipeline_constructor}). At initialisation, each pipeline is given a name,
 which must be unique amongst the pipelines constructed by the Study. The methods implemented
@@
 
-The \emph{add(name, interface)} method is used to add a node to a pipeline, which takes
+The \emph{add(name, interface)} method is used to add a node to a pipeline and takes
 a unique name for the node (within the pipeline) and a Nipype Interface object, and returns
@@
 for Field specifications). If the expected format does not match that of the corresponding data specification
-table or study input then an conversion nodes are implicitly connected to the pipeline.
-Inputs and outputs that are conditional on parameters of the study can be set outside of
-the \emph{add} method using the \emph{connect\_input} or
+or study input then a conversion node is implicitly connected to the pipeline.
+Inputs and outputs that are conditional on parameters or inputs provided to the
+study can be set outside of the \emph{add} method using the \emph{connect\_input} or
 \emph{connect\_output} methods, respectively.
 
-Internal connections between nodes within a pipeline are specified by a dictionary
-passed to the \emph{connect} keyword argument of the receiving node. The
-dictionary keys are the names of the receiving traits and the values are 2-tuples
+Connections between nodes are specified by a dictionary
+passed to the \emph{connect} keyword argument of the \emph{add} method
+that creates the receiving node. The dictionary keys are the names of the
+receiving traits and the values are 2-tuples
 consisting of the sending node and the name of the sending trait. Alternatively,
@@
 in the \emph{requirements} keyword argument as a list of
-\emph{Requirement} objects when the node added to the pipeline. These
-requirements can be used by the Processor to configure environment
-modules \citep{furlani_modules:_1991}, to ensure the required software
-packages are available. Similarly, the expected memory requirements and
-wall time for the node execution should be provided to the keyword args
-\emph{memory}, and \emph{wall\_time} so they can be inserted into HPC
-scheduler job scripts if required.
+\emph{Requirement} objects when the node added to the pipeline.
+Similarly, the expected memory requirements and
+wall time for the node execution should be provided to the keyword arguments
+\emph{memory}, and \emph{wall\_time}.
 
@@
 data, \emph{Study.SUBJECT\_ID} or \emph{Study.VISIT\_ID} should be
-passed to the \emph{joinsource} keyword to join over subjects or visits, respectively.
+passed to the \emph{joinsource} keyword of the \emph{add} method to join over subjects or visits, respectively.
 In this case, a JoinNode will be created instead of standard Node,
@@
 be applied to all items of the list connected to that input \citep{gorgolewski_nipype:_2011}.
-The subject and visit IDs are directly accessible as input fields of the pipeline
+Additionally, the values of the subject and visit IDs are directly accessible as input fields of the pipeline
 named \emph{Study.SUBJECT\_ID} and \emph{Study.VISIT\_ID}, respectively.
@@
 Study parameters can be accessed during pipeline construction with the
-\emph{parameter(name)} method. If conditional logic is included in
+\emph{Study.parameter(name)} method. If conditional logic is included in
 the workflow construction that alters the pipeline inputs, outputs or
@@
 parameter. The analysis branch designated by a switch value should be
-tested with \emph{branch(name)} in the case of boolean switches and
-\emph{branch(name, ref\_value)} in the case of string switches.
+tested with \emph{Study.branch(name)} in the case of boolean switches and
+\emph{Study.branch(name, ref\_value)} in the case of string switches.
 
@@
 
-\subsubsection*{Implementing multi-modal
-studies}
+\subsubsection*{Implementing multi-modal studies}
 \label{implementing-multi-modal-studies}
@@
 
-The software packages installed on the system are detected and managed
-by the Environment module. There are currently two types of available Environment modules:
+The software packages installed on the system that are required by a study's
+workflows (e.g. FSL, SPM) are detected and managed by
+the Environment object passed to the study at initialisation.
+There are currently two types of Environment class implemented in Arcana:
 \emph{StaticEnvironment} and \emph{ModulesEnvironment}.
 
-The \emph{StaticEnvironment} module doesn't perform any management, and instead
-only checks the existing environment for appropriate software versions before running
-the analysis.
-
-The \emph{ModulesEnvironment} module can be used if environment
+\emph{ModulesEnvironment} objects can be used if environment
 modules \citep{furlani_modules:_1991} are installed on the system (typical in many
-HPC environments). In this case, modules are loaded before a workflow node is run,
+HPC systems). In this case, environment modules are loaded before a workflow node is run,
 based on the requirements specified for the node during construction of the pipeline
 (see \emph{Pipeline constructors}), and then unloaded afterwards. Mappings from non-standard
-module names installed on the system to requirements required by the Study can be
-can be passed to the \emph{packages\_map} keyword argument of the ModulesEnvironment
-at initialisation. Likewise non-standard versions for packages can be mapped onto requirements
-using the \emph{versions\_map} keyword argument.
+module names installed on the system to those expected by the Study can be
+can be passed as a dictionary to the \emph{packages\_map} keyword argument
+at initialisation. Likewise non-standard versions for packages can be mapped onto
+requirements using the \emph{versions\_map} keyword argument.
+
+\emph{StaticEnvironment} objects don't actively manage the environment,
+and instead only check the current environment for appropriate software
+versions before running requested workflows.
+
+\subsection*{Acquisition of test dataset}
+
+A healthy volunteer was scanned using a 3T Siemens Skyra with a 32-channel head
+and neck coil to demonstrate the application of analyses implemented in
+Arcana. The protocol was a T1-weighted MPRAGE (1mm contiguous,
+matrix size 256x240x192, FOV 256x240x192, TE = 2.13ms, TR, = 2300ms, TI
+= 900ms, bandwidth=230Hz/pixel), GRE (1.8 mm contiguous, matrix size
+256x232x72, FOV 230x208x130, TE = 20ms, TR, = 30ms,
+bandwidth=120Hz/pixel), and diffusion MRI (1.2 mm contiguous, matrix size
+110x100x60, FOV 256x240x192, TE = 95ms, TR, = 8200ms, 33 diffusion
+directions with b=1500 mm2/s and 3 b=0, bandwidth=781Hz/pixel).
 
@@
 registration and brain extraction, from the base class \emph{MriStudy}.
-The T1Study and T2starStudy classes are aggregated into the
-\emph{T2starT1Study} MultiStudy class to combine analysis of T2* and
-T1-weighted contrasts.
 
@@
 
-The \emph{T2starT1Study} class implements an algorithm to generate
-\emph{composite vein images} from the combination of QSM and SWI
-contrasts derived from the T2*-weighted acquisition with an vein atlas
-registered to the T1-weighted acquisition \citep{ward_combining_2018}.
-(Figure \ref{fig:t2star_t1_study}).
+The \emph{T2starStudy} class implements an algorithm to generate
+\emph{composite vein images} \citep{ward_combining_2018} and
+vein masks \citep{ward_vein_2017} from the combination of QSM and SWI
+contrasts derived from the T2*-weighted acquisition with vein atlases
+derived from manual tracings (Figure \ref{fig:t2star_t1_study}).
 
@@
 
-The DiffusionStudy and T2starT1Study classes are further aggregated in
-turn into a single MultiStudy class for the results section of this
-manuscript\emph{, ArcanaPaper}, (Supplementary material). Methods are
-implemented in ArcanaPaper to generate and display the derivative
-images in Figure \ref{fig:veins}, \ref{fig:fa_adc} and \ref{fig:tractography}.
-
-To test the analysis workflows implemented in ArcanaPaper, a healthy
-volunteer was scanned using a 3T Siemens Skyra with a 32-channel head
-and neck coil. The protocol was a T1-weighted MPRAGE (1mm contiguous,
-matrix size 256x240x192, FOV 256x240x192, TE = 2.13ms, TR, = 2300ms, TI
-= 900ms, bandwidth=230Hz/pixel), GRE (1.8 mm contiguous, matrix size
-256x232x72, FOV 230x208x130, TE = 20ms, TR, = 30ms,
-bandwidth=120Hz/pixel), diffusion MRI (1.2 mm contiguous, matrix size
-110x100x60, FOV 256x240x192, TE = 95ms, TR, = 8200ms, 33 diffusion
-directions with b=1500 mm2/s and 3 b=0, bandwidth=781Hz/pixel).
-Methods for Figure \ref{fig:veins}, \ref{fig:fa_adc}, and \ref{fig:tractography} in
-the ArcanaPaper class were applied to the acquired dataset to using the
-\emph{SlurmProcessor} to submit jobs to the the MASSIVE HPC cluster
-\citep{goscinski_multi-modal_2014} in order to generate the figures.
-
-Figure \ref{fig:veins} displays composite vein images for the healthy
-volunteer along with the SWI and QSM intermediate derivatives and the
-input vein atlas. The derived vein images are comparable to those
+The T1Study, T2starStudy and DmriStudy classes are
+aggregated into a single MultiStudy class,
+\emph{ArcanaPaper} (Supplementary material), which is specialised to produce
+the figures in the Results section of this manuscript. In order to warp the
+prior vein atlases to the subject space in the generation of the composite vein images,
+nonlinear registration to Montreal Neurological Institute templates
+\citep{mni-cite} is performed in the T1Study. The transform and warp
+field from this registration are then mapped onto the `coreg\_to\_atlas\_mat` and
+`coreg\_to\_atlas\_warp' specifications in the T2starStudy, instead
+of registering the T2*-weighted images directly, in order to improve the registration.
+These transforms were used to produce the composite vein
+image in conjuction with the linear transform from the brain-extracted T2*-weighted
+magnitude image to the brain extracted T1-weighted image, which required the
+`brain' specification in the T1Study to be mapped to the `coreg\_ref\_brain`
+specification in the T2starStudy.
+
+The \emph{vein\_fig}, \emph{fa\_adc\_fig} and \emph{tractography\_fig} methods
+implemented in the ArcanaPaper class were applied to the test dataset to produce
+Figure \ref{fig:veins}, \ref{fig:fa_adc}, and \ref{fig:tractography}, respectively.
+Figure \ref{fig:veins} displays composite vein images and vein masks for the healthy
+volunteer along with the SWI and QSM intermediate derivatives.
+The derived vein images are comparable to those
 generated by the original implementation \citep{ward_combining_2018}.
@@
   and a vein atlas from manual tracings. A vein mask was then
-  generated (\emph{bottom row}) by thresholding the composite
+  generated (\emph{bottom row}) from the composite
   vein image.
@@
 the rest of the brain.
+Figure \ref{fig:tractography} displays the global tractography derived from the dMRI
+acquisition. The streamlines follow well known white matter tracts such
+as the cortico-spinal, fasciculus and corpus callosum. Intermediate
+derivatives derived for the FA and ADC analysis, including the
+preprocessed and bias-corrected dMRI image and a whole brain mask, were
+reused in the generation of the streamlines.
 
@@
 \end{figure*}
-
-Figure \ref{fig:tractography} displays the global tractography derived from the dMRI
-acquisition. The streamlines follow well known white matter tracts such
-as the cortico-spinal, fasciculus and corpus callosum. Intermediate
-derivatives derived for the FA and ADC analysis, including the
-preprocessed and bias-corrected dMRI image and a whole brain mask, were
-reused in the generation of the streamlines reducing the time taken to
-produce the tractography results from ?? to ??.
 
@@
 additional Environment modules could be implemented to run each pipeline
-node within its own container if required to take advantage of
+node within its own container to take advantage of
 containers maintained by tool developers (e.g. 

### 2018-10-17 arcana_paper.py

@@ -31,7 +31,7 @@ class ArcanaPaper(MultiStudy, ImageDisplayMixin,
 
     add_param_specs = [
         ParameterSpec(
-            'dmri_fig_slice_offset', (4, 0, 0),
+            'dmri_fig_slice_offset', (6, 0, 0),
             desc=("Offset the sagittal slices of dMRI figures so they "
                   "intersect a cerebral hemisphere instead of the "
                   "midline between the hemispheres"))]
@@ -187,5 +187,5 @@ if __name__ == '__main__':
     # Derive required data and display them in a single step for each
     # figure.
     paper.vein_fig(op.join(args.fig_dir, 'veins.png'))
-#     paper.fa_adc_fig(op.join(args.fig_dir, 'fa_adc.png'))
-#     paper.tractography_fig(op.join(args.fig_dir, 'tractography.png'))
+    paper.fa_adc_fig(op.join(args.fig_dir, 'fa_adc.png'))
+    paper.tractography_fig(op.join(args.fig_dir, 'tractography.png'))

### 2018-10-17 arcana_paper.py
Tidied up arcana paper script

@@ -1,7 +1,8 @@
 #!/usr/bin/env python3
 from arcana import (
     MultiStudy, MultiStudyMetaClass, SubStudySpec, ParameterSpec)
-from nianalysis.study.mri import (DiffusionStudy, T1Study, T2StarStudy)
+from nianalysis.study.mri import (
+    DiffusionStudy, T1Study, T2StarStudy, MriStudy)
 from nianalysis.plot import ImageDisplayMixin
 import os.path as op
 
@@ -23,11 +24,19 @@ class ArcanaPaper(MultiStudy, ImageDisplayMixin,
             't2star',
             T2StarStudy,
             name_map={'t1_brain': 'coreg_ref_brain',
+                      'swi_brain': 'swi',
                       't1_coreg_to_atlas_mat': 'coreg_to_atlas_mat',
                       't1_coreg_to_atlas_warp': 'coreg_to_atlas_warp'}),
         SubStudySpec(
             'dmri',
-            DiffusionStudy)]
+            DiffusionStudy),
+        # Since we are using the SWI image produced from the scanner console
+        # we need to brain extract it in order to display it properly, so
+        # we create a basic MriStudy to use its brain extraction before
+        # mapping the extracted image to the T2* study.
+        SubStudySpec(
+            'swi',
+            MriStudy)]
 
     add_param_specs = [
         ParameterSpec(
@@ -49,7 +58,7 @@ class ArcanaPaper(MultiStudy, ImageDisplayMixin,
         """
         # Derive (when necessary) and access data SWI, QSM, vein atlas,
         # and vein mask data in the repository.
-        swis = self.data('t2star_swi')
+        swis = self.data('swi_brain')
         qsms = self.data('t2star_qsm')
         cv_image = self.data('t2star_composite_vein_image')
         vein_masks = self.data('t2star_vein_mask')
@@ -142,10 +151,20 @@ if __name__ == '__main__':
     parser.add_argument('--work_dir', help="The work directory",
                         default=op.join(op.expanduser('~'),
                                         'arcana-paper-work'))
-    parser.add_argument(
-        '--fig_dir', help="The directory to store the figures",
-        default=op.join(op.expanduser('~'),
-                        'arcana-paper-fig'))
+    parser.add_argument('--fig_dir',
+                        help="The directory to store the figures",
+                        default=op.join(op.expanduser('~'),
+                                        'arcana-paper-fig'))
+    parser.add_argument('--t1', default='.*mprage.*',
+                        help="Pattern to match T1-weighted scan")
[…]

### 2018-10-17 manuscript/manuscript.tex
Tidied up arcana paper script
renamed nianalysis to banana

@@
 \item Complex workflows in a flexible extensible manner, reusable
-\item portable between different data storage solutions/scale of studies, separation between design and application yet programmatic
+\item portable between different data storage solutions/scale of studies, separation between design and application yet programmatic, prototype locally and deploy on cluster
 \item Easily updatable, switchable between tools/versions
+\item Data specification, like make, dependencies are resolved by framework
+\item Modular Repository, Processor, Environment and input matching
+\item supports BIDS
+\item provenance, checks for updates to find stale data and reprocesses
+\item we have created a framework that handles all the tedious aspects and allows researchers to focus on the analysis design
+\item it is flexible to allow researchers to collaborate
 \end{itemize}
@@
 nonlinear registration to Montreal Neurological Institute templates
-\citep{mni-cite} is performed in the T1Study. The transform and warp
+\citep{grabner_symmetric_2006} is performed in the T1Study. The transform and warp
 field from this registration are then mapped onto the `coreg\_to\_atlas\_mat` and
@@
 
-MR contrast-specific analyses are implemented in NiAnalysis via a chain
+MR contrast-specific analyses are implemented in banana via a chain
 of successively specialised Study sub-classes (e.g.

### 2018-10-17 arcana_paper.py

@@ -1,9 +1,9 @@
 #!/usr/bin/env python3
 from arcana import (
     MultiStudy, MultiStudyMetaClass, SubStudySpec, ParameterSpec)
-from nianalysis.study.mri import (
+from banana.study.mri import (
     DiffusionStudy, T1Study, T2StarStudy, MriStudy)
-from nianalysis.plot import ImageDisplayMixin
+from banana.plot import ImageDisplayMixin
 import os.path as op
 
 
@@ -141,7 +141,7 @@ if __name__ == '__main__':
     from arcana import (
         DirectoryRepository, LinearProcessor, StaticEnvironment,
         FilesetSelector)
-    from nianalysis.file_format import (
+    from banana.file_format import (
         dicom_format, zip_format, nifti_gz_format)
 
     parser = ArgumentParser(
@@ -157,7 +157,7 @@ if __name__ == '__main__':
                                         'arcana-paper-fig'))
     parser.add_argument('--t1', default='.*mprage.*',
                         help="Pattern to match T1-weighted scan")
-    parser.add_argument('--t2star_chann', default='.*coils.*',
+    parser.add_argument('--t2star_chann', default='.*channels.*',
                         help="Pattern to match T1-weighted scan")
     parser.add_argument('--swi', default='.*(swi|SWI).*',
                         help="Pattern to match T1-weighted scan")
@@ -178,8 +178,7 @@ if __name__ == '__main__':
         # Repository is a simple directory on the local file system
         repository=DirectoryRepository(args.data_dir),
         # Use a single process on the local system to derive
-        processor=LinearProcessor(args.work_dir,
-                                  clean_work_dir_between_runs=False),
+        processor=LinearProcessor(args.work_dir),
         # Use the static environment (i.e. no Modules)
         environment=StaticEnvironment(),
         # Match names in the data specification to filenames used
@@ -191,7 +190,7 @@ if __name__ == '__main__':
                             is_regex=True),
             FilesetSelector('t2star_header_image', dicom_format, args.swi,
                             is_regex=True),
-            FilesetSelector('swi_magnitude', nifti_gz_format, args.swi,
+            FilesetSelector('swi_magnitude', dicom_format, args.swi,
                             is_regex=True),
             FilesetSelector('dmri_magnitude', dicom_format, args.dmri,
                             is_regex=True),

### 2018-10-17 examples/manuscript.py

@@ -2,7 +2,7 @@ from arcana import (Study, StudyMetaClass, AcquiredFilesetSpec, FilesetSpec,
                     AcquiredFieldSpec, FieldSpec, ParameterSpec, SwitchSpec,
                     FilesetCollection, XnatRepository, Fileset)
 from arcana.data.file_format.standard import text_format
-from nianalysis.file_format import (
+from banana.file_format import (
     nifti_gz_format, dicom_format, nifti_format, analyze_format)
 
 STD_IMAGE_FORMATS = (dicom_format, nifti_format, nifti_gz_format,

### 2018-10-17 manuscript/listings/example_application.py

@@ -4,7 +4,7 @@ from arcana import (
     FilesetSelector, FieldSelector, XnatRepository,
     SlurmProcessor, ModulesEnvironment)
 from .example_study import ExampleStudy
-from nianalysis.file_format import dicom_format
+from banana.file_format import dicom_format
 
 # Create study object that accesses an XNAT repository
 # and submits jobs to a SLURM scheduler

### 2018-10-17 manuscript/listings/example_study.py

@@ -3,7 +3,7 @@ from arcana import (
     Study, StudyMetaClass, AcquiredFilesetSpec, FilesetSpec,
     AcquiredFieldSpec, FieldSpec, ParameterSpec, SwitchSpec,
     FilesetSelector, XnatRepository)
-from nianalysis.file_format import (
+from banana.file_format import (
     nifti_gz_format, dicom_format, nifti_format, analyze_format,
     text_format, text_mat_format)
 

### 2018-10-18 manuscript/manuscript.tex
renamed nianalysis to banana

--- 2018-10-17 manuscript/manuscript.tex
@@
 \lstset{
-    captionpos=b,                    % sets the caption-position to bottom
+%    captionpos=b,                    % sets the caption-position to bottom
     language=Python,                 % the language of the code
@@
 
-These are the notes I have for my abstract
-
-\begin{itemize}
-\item The heterogeneous collection of neuroimaging analysis tools, parameters, styles makes it difficult to design comprehensive workflows
-\item Complex workflows in a flexible extensible manner, reusable
-\item portable between different data storage solutions/scale of studies, separation between design and application yet programmatic
-\item Easily updatable, switchable between tools/versions
-\end{itemize}
+Mastering the ``arcana of neuroimaging analysis'', the obscure knowledge required to apply an
+appropriate combination of software tools and parameters to analyse a given neuroimaging dataset,
+is a time consuming process. Therefore, it is typically not feasible to invest the additional effort
+required to implement analysis workflows in a form that generalises across the various acquisition
+parameters, data storage conventions and computing environments in use at different research sites,
+which limits the reusability of published workflows.
+
+We present a novel software framework, \emph{Abstraction of Repository-Centric ANAlysis (Arcana)}, which enables
+the development of complex, ``end-to-end'' workflows that are adaptable to new analyses and
+portable to a wide range of computing infrastructures. Analysis templates for specific image types (e.g. MRI contrast)
+are implemented as Python classes that specify potential derivatives and modular pipelines to derive them.
+Arcana retrieves data from imaging repositories, which can be BIDS datasets, XNAT instances or plain directories, and
+stores selected derivatives back into a repository with provenance data for reuse by subsequent analyses.
+Pipelines are constructed using Nipype and can be processed on local or on high performance computing environments,
+enabling a smooth transition from locally developed prototypes to large-scale deployment.
+we have created a framework that handles all the tedious aspects and allows researchers to focus on the analysis design
+it is flexible to allow researchers to collaborate
 
@@
     \centering
-    \includegraphics[width=0.55\textwidth]{figures/example_study}
+    \includegraphics[width=0.55\textwidth]{../figures/example_study}
   \caption{Example study. Blue boxes represent acquired (input)
@@
     \centering
-    \includegraphics[width=0.9\textwidth]{figures/simplified_arcana_uml}
+    \includegraphics[width=0.9\textwidth]{../figures/simplified_arcana_uml}
   \caption{Unified Modelling Language (UML) diagram
@@
 \begin{figure}
-\lstinputlisting[basicstyle=\footnotesize,firstline=2, lastline=59]{listings/example_study.py}
+\lstinputlisting[basicstyle=\footnotesize,firstline=2, lastline=59]{../code/example_study.py}
 \caption{Example data and parameter specifications. The data
@@
 \begin{figure}
-\lstinputlisting[firstline=61, basicstyle=\footnotesize]{listings/example_study.py}
+\lstinputlisting[firstline=61, basicstyle=\footnotesize]{../code/example_study.py}
 \caption{Example pipeline constructor method. Pipelines are
@@
   \centering
-    \includegraphics[width=0.775\textwidth]{figures/example_multi_study}
+    \includegraphics[width=0.775\textwidth]{../figures/example_multi_study}
   \caption{Example MultiStudy. Blue boxes represent acquired
@@
 	\centering
-    \includegraphics[width=\textwidth]{figures/full_arcana_uml}
+    \includegraphics[width=\textwidth]{../figures/full_arcana_uml}
   \caption{Detailed Unified Modelling Language (UML) diagram of
@@
 \begin{figure}
-\lstinputlisting[basicstyle=\footnotesize]{listings/example_application.py}
+\lstinputlisting[basicstyle=\footnotesize]{../code/example_application.py}
 \caption{Example application of Study class to a dataset stored in an XNAT
@@
 
-The DmriStudy class implements diffusion tensor metrics, FA and ADC, as
-well as global tractography using streamlines tracking from the MRtrix
+The DmriStudy class implements the extraction of diffusion tensor metrics,
+FA and ADC, as well as whole-brain tractography using streamlines tracking from the MRtrix
 toolbox \citep{tournier_improved_2010,tournier_mrtrix:_2012} (Figure \ref{fig:dmri_study}).
@@
 	\centering
-    \includegraphics[width=0.55\textwidth]{figures/dmri_study}
+    \includegraphics[width=0.55\textwidth]{../figures/dmri_study}
   \caption{Example diffusion MRI (dMRI) study, which can derive
@@
 \emph{composite vein images} \citep{ward_combining_2018} and
-vein masks \citep{ward_vein_2017} from the combination of QSM and SWI
-contrasts derived from the T2*-weighted acquisition with vein atlases
-derived from manual tracings (Figure \ref{fig:t2star_t1_study}).
+vein masks \citep{ward_vein_2017} from the combination of
+vein atlases derived from manual tracings with QSM and SWI
+contrasts derived from the T2*-weighted acquisition (Figure \ref{fig:t2star_t1_study}).
 
@@
 	\centering
-    \includegraphics[width=0.775\textwidth]{figures/t2star_t1_study}
+    \includegraphics[width=0.775\textwidth]{../figures/t2star_t1_study}
   \caption{Combined T2*-weighted/T1-weighted multi-study,
@@
 the figures in the Results section of this manuscript. In order to warp the
-prior vein atlases to the subject space in the generation of the composite vein images,
+vein atlases to the subject space for comparison with the SWI and QSM images,
 nonlinear registration to Montreal Neurological Institute templates
-\citep{mni-cite} is performed in the T1Study. The transform and warp
+\citep{grabner_symmetric_2006} is performed in the T1Study. The transform and warp
 field from this registration are then mapped onto the `coreg\_to\_atlas\_mat` and
-`coreg\_to\_atlas\_warp' specifications in the T2starStudy, instead
-of registering the T2*-weighted images directly, in order to improve the registration.
+`coreg\_to\_atlas\_warp' specifications in the T2starStudy, in order to improve the registration.
 These transforms were used to produce the composite vein
@@
     \centering
-    \includegraphics[width=\textwidth]{figures/veins}
+    \includegraphics[width=\textwidth]{../figures/veins}
   \caption{Composite vein image (\emph{third row}) constructed by
@@
     \centering
-    \includegraphics[width=\textwidth]{figures/fa_adc}
+    \includegraphics[width=\textwidth]{../figures/fa_adc}
   \caption{Fractional Anisotropy (FA) \emph{(top row)} and
@@
     \centering
-    \includegraphics[width=\textwidth]{figures/tractography}
+    \includegraphics[width=\textwidth]{../figures/tractography}
   \caption{Global tractography performed using the MRtrix
@@
 
-MR contrast-specific analyses are implemented in NiAnalysis via a chain
+MR contrast-specific analyses are implemented in Banana via a chain
 of successively specialised Study sub-classes (e.g.
@@
 
+\section*{Supplementary material}
+\lstinputlisting[basicstyle=\footnotesize,caption=ArcanaPaper class definition,lastline=135]{../code/arcana_paper.py}
+\lstinputlisting[basicstyle=\footnotesize,caption=Application of ArcanaPaper class to a dataset,firstline=139]{../code/arcana_paper.py}
+
 \end{document}

### 2018-10-18 code/arcana_paper.py

@@ -2,7 +2,7 @@
 from arcana import (
     MultiStudy, MultiStudyMetaClass, SubStudySpec, ParameterSpec)
 from banana.study.mri import (
-    DiffusionStudy, T1Study, T2StarStudy, MriStudy)
+    DmriStudy, T1Study, T2starStudy, MriStudy)
 from banana.plot import ImageDisplayMixin
 import os.path as op
 
@@ -22,14 +22,14 @@ class ArcanaPaper(MultiStudy, ImageDisplayMixin,
             T1Study),
         SubStudySpec(
             't2star',
-            T2StarStudy,
+            T2starStudy,
             name_map={'t1_brain': 'coreg_ref_brain',
                       'swi_brain': 'swi',
                       't1_coreg_to_atlas_mat': 'coreg_to_atlas_mat',
                       't1_coreg_to_atlas_warp': 'coreg_to_atlas_warp'}),
         SubStudySpec(
             'dmri',
-            DiffusionStudy),
+            DmriStudy),
         # Since we are using the SWI image produced from the scanner console
         # we need to brain extract it in order to display it properly, so
         # we create a basic MriStudy to use its brain extraction before

### 2018-10-18 manuscript/manuscript.tex
finished abstract

@@
 appropriate combination of software tools and parameters to analyse a given neuroimaging dataset,
-is a time consuming process. Therefore, it is typically not feasible to invest the additional effort
-required to implement analysis workflows in a form that generalises across the various acquisition
-parameters, data storage conventions and computing environments in use at different research sites,
-which limits the reusability of published workflows.
-
-We present a novel software framework, \emph{Abstraction of Repository-Centric ANAlysis (Arcana)}, which enables
-the development of complex, ``end-to-end'' workflows that are adaptable to new analyses and
+is a time consuming process. Therefore, it is not typically feasible to invest the additional effort
+required generalise workflow implementations to accommodate for the various acquisition parameters,
+data storage conventions and computing environments in use at different research sites,
+limiting the reusability of published workflows.
+
+We present a novel software framework, \emph{Abstraction of Repository-Centric ANAlysis (Arcana)},
+which enables the development of complex, ``end-to-end'' workflows that are adaptable to new analyses and
 portable to a wide range of computing infrastructures. Analysis templates for specific image types (e.g. MRI contrast)
-are implemented as Python classes that specify potential derivatives and modular pipelines to derive them.
+are implemented as Python classes, which specify a range of potential derivatives and analysis methods.
 Arcana retrieves data from imaging repositories, which can be BIDS datasets, XNAT instances or plain directories, and
 stores selected derivatives back into a repository with provenance data for reuse by subsequent analyses.
-Pipelines are constructed using Nipype and can be processed on local or on high performance computing environments,
-enabling a smooth transition from locally developed prototypes to large-scale deployment.
-we have created a framework that handles all the tedious aspects and allows researchers to focus on the analysis design
-it is flexible to allow researchers to collaborate
+Workflows are constructed using Nipype and can be executed on local workstations or in high performance
+computing environments without alteration. Generic analysis methods can be consolidated within a common
+base classes to facilitate code-reuse and collaborative development, which can be specialised for study-specific
+requirements via class inheritance. Therefore, Arcana provides a platform to develop unified neuroimaging
+workflows that can be reused across many research sites and studies.
 

### 2018-10-18 manuscript/manuscript.tex
finalised proof of Arcana for bioRxiv

@@
 values of the dictionary are 2-tuples each consisting of the name of a data specification
-and the format the pipeline expects the data in (i.e. a FileFormat for Fileset specifications or datatype
-for Field specifications). If the expected format does not match that of the corresponding data specification
-or study input then a conversion node is implicitly connected to the pipeline.
-Inputs and outputs that are conditional on parameters or inputs provided to the
+and the format the pipeline either expects or produces the data in (i.e. a FileFormat for Fileset specifications
+or Python datatype for Field specifications). If the expected format does not match that of the
+corresponding data specification or study input then a conversion node is implicitly connected
+to the pipeline. Inputs and outputs that are conditional on parameters or inputs provided to the
 study can be set outside of the \emph{add} method using the \emph{connect\_input} or
@@
 \emph{Requirement} objects when the node added to the pipeline.
-Similarly, the expected memory requirements and
+Similarly, the expected memory requirements in MB and
 wall time for the node execution should be provided to the keyword arguments
@@
 matrix size 256x240x192, FOV 256x240x192, TE = 2.13ms, TR, = 2300ms, TI
-= 900ms, bandwidth=230Hz/pixel), GRE (1.8 mm contiguous, matrix size
+= 900ms, bandwidth = 230Hz/pixel), GRE (1.8 mm contiguous, matrix size
 256x232x72, FOV 230x208x130, TE = 20ms, TR, = 30ms,
-bandwidth=120Hz/pixel), and diffusion MRI (1.2 mm contiguous, matrix size
+bandwidth = 120Hz/pixel), and diffusion MRI (1.2 mm contiguous, matrix size
 110x100x60, FOV 256x240x192, TE = 95ms, TR, = 8200ms, 33 diffusion
-directions with b=1500 mm2/s and 3 b=0, bandwidth=781Hz/pixel).
+directions with b = 1500 mm2/s and 3 b=0, bandwidth = 781Hz/pixel).
 

### 2018-10-19 manuscript/manuscript.tex
touching up wording of abstract

@@
 portable to a wide range of computing infrastructures. Analysis templates for specific image types (e.g. MRI contrast)
-are implemented as Python classes, which specify a range of potential derivatives and analysis methods.
+are implemented as Python classes, which define a range of potential derivatives and analysis methods.
 Arcana retrieves data from imaging repositories, which can be BIDS datasets, XNAT instances or plain directories, and
-stores selected derivatives back into a repository with provenance data for reuse by subsequent analyses.
+stores selected derivatives and associated provenance back into a repository for reuse by subsequent analyses.
 Workflows are constructed using Nipype and can be executed on local workstations or in high performance
-computing environments without alteration. Generic analysis methods can be consolidated within a common
+computing environments. Generic analysis methods can be consolidated within common
 base classes to facilitate code-reuse and collaborative development, which can be specialised for study-specific
-requirements via class inheritance. Therefore, Arcana provides a platform to develop unified neuroimaging
+requirements via class inheritance. Arcana therefore provides a platform to develop unified neuroimaging
 workflows that can be reused across many research sites and studies.

### 2018-10-19 code/arcana_paper.py

@@ -58,10 +58,10 @@ class ArcanaPaper(MultiStudy, ImageDisplayMixin,
         """
         # Derive (when necessary) and access data SWI, QSM, vein atlas,
         # and vein mask data in the repository.
-        swis = self.data('swi_brain')
-        qsms = self.data('t2star_qsm')
-        cv_image = self.data('t2star_composite_vein_image')
         vein_masks = self.data('t2star_vein_mask')
+        qsms = self.data('t2star_qsm')
+        swis = self.data('swi_brain')
+        cv_image = self.data('t2star_composite_vein_image')
         # Loop through all sessions
         for swi, qsm, vein_atlas, vein_mask in zip(swis, qsms, cv_image,
                                                    vein_masks):
@@ -137,12 +137,12 @@ class ArcanaPaper(MultiStudy, ImageDisplayMixin,
 
 if __name__ == '__main__':
     import os
+    import os.path as op
     from argparse import ArgumentParser
     from arcana import (
         DirectoryRepository, LinearProcessor, StaticEnvironment,
         FilesetSelector)
-    from banana.file_format import (
-        dicom_format, zip_format, nifti_gz_format)
+    from banana.file_format import dicom_format, zip_format
 
     parser = ArgumentParser(
         "A script to produce figures for the Arcana manuscript")
@@ -158,13 +158,13 @@ if __name__ == '__main__':
     parser.add_argument('--t1', default='.*mprage.*',
                         help="Pattern to match T1-weighted scan")
     parser.add_argument('--t2star_chann', default='.*channels.*',
-                        help="Pattern to match T1-weighted scan")
+                        help="Pattern to match T2*-weighted scan")
     parser.add_argument('--swi', default='.*(swi|SWI).*',
-                        help="Pattern to match T1-weighted scan")
+                        help="Pattern to match SWI scan")
     parser.add_argument('--dmri', default='.*diff.*',
-                        help="Pattern to match T1-weighted scan")
+                        help="Pattern to match dMRI scan")
     parser.add_argument('--distort', default='.*distortion_correction.*',
-                        help="Pattern to match T1-weighted scan")
+                        help="Pattern to match dMRI reverse PE ref. scan")
     args = parser.parse_args()
 
     # Make figure directory
@@ -199,6 +199,7 @@ if __name__ == '__main__':
         parameters={
             'dmri_num_global_tracks': int(1e5),
             'dmri_global_tracks_cutoff': 0.175,
[…]

### 2018-10-20 manuscript/manuscript.tex
touched up manuscript and arcana_paper class

@@
 base classes to facilitate code-reuse and collaborative development, which can be specialised for study-specific
-requirements via class inheritance. Arcana therefore provides a platform to develop unified neuroimaging
+requirements via class inheritance. Arcana therefore provides a platform to develop unified and neuroimaging
 workflows that can be reused across many research sites and studies.
@@
 (dMRI) data and the application of dMRI tractogram \citep{tournier_mrtrix:_2012} and
-composite vein image \citep{ward_combining_2018} workflows to data collected from a
+vein masks \citep{ward_vein_2017} workflows to data collected from a
 healthy subject.

### 2018-10-20 code/arcana_paper.py

@@ -199,7 +199,7 @@ if __name__ == '__main__':
         parameters={
             'dmri_num_global_tracks': int(1e5),
             'dmri_global_tracks_cutoff': 0.175,
-            't2star_qsm_erosion_size': 5,
+            't2star_qsm_erosion_size': 7,
             # This is needed as the channels aren't reconstructed with the
             # correct headers
             't2star_force_channel_flip': ['-x', '-y', 'z']})
@@ -207,5 +207,5 @@ if __name__ == '__main__':
     # Derive required data and display them in a single step for each
     # figure.
     paper.vein_fig(op.join(args.fig_dir, 'veins.png'))
-    paper.fa_adc_fig(op.join(args.fig_dir, 'fa_adc.png'))
-    paper.tractography_fig(op.join(args.fig_dir, 'tractography.png'))
+    #paper.fa_adc_fig(op.join(args.fig_dir, 'fa_adc.png'))
+    #paper.tractography_fig(op.join(args.fig_dir, 'tractography.png'))

### 2018-10-22 manuscript/manuscript.tex
finalised manuscript for submission

@@
 base classes to facilitate code-reuse and collaborative development, which can be specialised for study-specific
-requirements via class inheritance. Arcana therefore provides a platform to develop unified and neuroimaging
-workflows that can be reused across many research sites and studies.
+requirements via class inheritance. Arcana provides a framework in which to develop unified neuroimaging
+workflows that can be reused across a wide range of research studies and sites.
 
@@
 necessary for routine reproduction because of the effort required to
-accurately exactly reimplement such analyses \citep{kennedy_neuroimaging_2018}. It is also
+accurately reimplement such analyses \citep{kennedy_neuroimaging_2018}. It is also
 difficult to adapt existing workflows to new studies without detailed
@@
 can provide additional features, such as
-flexible access-control and automated pipelines. Therefore, for
+flexible access-control and automated pipelines. For
 published workflows, the choice of repository should be transparent in
@@
 idiosyncrasies of the acquisition protocols in use at different sites
-\citep{esteban_fmriprep:_2018}. Therefore, workflows may require conditional
+\citep{esteban_fmriprep:_2018}. Workflows may require conditional
 logic in construction or execution to be portable. Nipype is a flexible
@@
 rerunning common segments can lead to significant increases in
-computation time and therefore project cost. In addition, duplication of
+computation time and project cost. In addition, duplication of
 processing segments increases time for manual quality control (QC),
@@
 designing complex workflows in which modular Nipype pipelines operate on
-data stored in various repositories. Intermediate derivatives are
+data stored in repositories. Intermediate derivatives are
 derived on demand, checking against stored provenance for required
@@
 
-Workflows are implemented in Arcana as a series of pipelines, which
+Workflows are implemented in Arcana as a series of modular pipelines, which
 each perform a unit of the analysis (e.g. registration, brain
@@
 vein masks \citep{ward_vein_2017} from the combination of
-vein atlases derived from manual tracings with QSM and SWI
-contrasts derived from the T2*-weighted acquisition (Figure \ref{fig:t2star_t1_study}).
+vein atlases derived from manual tracings with Quantitative
+Susceptibility Mapping (QSM) and Susceptible Weighted Imaging (SWI)
+images derived from the T2*-weighted acquisition (Figure \ref{fig:t2star_t1_study}).
 
@@
     \includegraphics[width=0.775\textwidth]{../figures/t2star_t1_study}
-  \caption{Combined T2*-weighted/T1-weighted multi-study,
-which can derive vein masks by combining Quantitative Susceptibility
+  \caption{Combined T2*/T1-weighted studies within \emph{ArcanaPaper}
+  MultiStudy class, which can derive vein masks by combining Quantitative Susceptibility
 Mapping (QSM) and Susceptible Weighted Imaging (SWI) contrasts with a
@@
 the linear registration between T1-weighted and T2*-weighted images, QSM
-and SWI images mapped from the T2*-weighted sub-study to produce the
-composite-vein image. The brain mask from the T1-weighted sub-study is
-combined with the composite vein image to produce the vein mask.}
+and SWI images are combined to produce the composite-vein image. In this
+instance, the SWI acquired from the scanner console is passed
+as an input to the derived \emph{SWI} specification, overriding the
+\emph{SWI} pipeline that would otherwise generate it (dashed oval).}
 \label{fig:t2star_t1_study}
@@
 field from this registration are then mapped onto the `coreg\_to\_atlas\_mat` and
-`coreg\_to\_atlas\_warp' specifications in the T2starStudy, in order to improve the registration.
-These transforms were used to produce the composite vein
-image in conjuction with the linear transform from the brain-extracted T2*-weighted
-magnitude image to the brain extracted T1-weighted image, which required the
-`brain' specification in the T1Study to be mapped to the `coreg\_ref\_brain`
-specification in the T2starStudy.
+`coreg\_to\_atlas\_warp' specifications in the T2starStudy, as the registration of
+T2*-weighted images to the MNI template is typically poor.
+These transforms are combined with the linear transform from the
+brain-extracted T2*-weighted magnitude image to the brain extracted T1-weighted image,
+which requires the `brain' specification in the T1Study to be mapped
+to the `coreg\_ref\_brain` specification in the T2starStudy.
+
+The SWI image reconstructed on the scanner console is substituted for the \emph{SWI} derivative
+produced by the \emph{SWI} pipeline of the T2starStudy. For ease of comparison
+with the QSM and vein images produced by T2starStudy, this SWI image is brain extracted
+in a separate MriStudy sub-study of ArcanaPaper.
 
@@
 
-\section*{Supplementary material}
-\lstinputlisting[basicstyle=\footnotesize,caption=ArcanaPaper class definition,lastline=135]{../code/arcana_paper.py}
-\lstinputlisting[basicstyle=\footnotesize,caption=Application of ArcanaPaper class to a dataset,firstline=139]{../code/arcana_paper.py}
-
 \end{document}

### 2018-10-22 code/arcana_paper.py

@@ -4,7 +4,6 @@ from arcana import (
 from banana.study.mri import (
     DmriStudy, T1Study, T2starStudy, MriStudy)
 from banana.plot import ImageDisplayMixin
-import os.path as op
 
 
 class ArcanaPaper(MultiStudy, ImageDisplayMixin,
@@ -24,7 +23,6 @@ class ArcanaPaper(MultiStudy, ImageDisplayMixin,
             't2star',
             T2starStudy,
             name_map={'t1_brain': 'coreg_ref_brain',
-                      'swi_brain': 'swi',
                       't1_coreg_to_atlas_mat': 'coreg_to_atlas_mat',
                       't1_coreg_to_atlas_warp': 'coreg_to_atlas_warp'}),
         SubStudySpec(
@@ -43,7 +41,11 @@ class ArcanaPaper(MultiStudy, ImageDisplayMixin,
             'dmri_fig_slice_offset', (6, 0, 0),
             desc=("Offset the sagittal slices of dMRI figures so they "
                   "intersect a cerebral hemisphere instead of the "
-                  "midline between the hemispheres"))]
+                  "midline between the hemispheres")),
+        # Override default values to reduce the number of tracks in order to
+        # make it easier to see the tracts
+        ParameterSpec('dmri_num_global_tracks', int(1e5)),
+        ParameterSpec('dmri_global_tracks_cutoff', 0.175)]
 
     def vein_fig(self, save_path=None, **kwargs):
         """
@@ -142,6 +144,7 @@ if __name__ == '__main__':
     from arcana import (
         DirectoryRepository, LinearProcessor, StaticEnvironment,
         FilesetSelector)
+    from arcana.utils import parse_value
     from banana.file_format import dicom_format, zip_format
 
     parser = ArgumentParser(
@@ -158,13 +161,19 @@ if __name__ == '__main__':
     parser.add_argument('--t1', default='.*mprage.*',
                         help="Pattern to match T1-weighted scan")
     parser.add_argument('--t2star_chann', default='.*channels.*',
-                        help="Pattern to match T2*-weighted scan")
+                        help=("Pattern to match separate channels from the "
+                              "head coil for the T2*-weighted scan in "
+                              "separate NiFTI files within a single "
+                              "directory"))
     parser.add_argument('--swi', default='.*(swi|SWI).*',
-                        help="Pattern to match SWI scan")
+                        help="Pattern to match SWI scan in DICOM format")
     parser.add_argument('--dmri', default='.*diff.*',
[…]

### 2018-10-23 manuscript/manuscript.tex
final round of edits before submission to NI and bioRxiv

@@
 
-\subsubsection*{Implementing multi-modal studies}
+\subsubsection*{Implementing multi-modal studies: MultiStudy classes}
 \label{implementing-multi-modal-studies}
@@
 table} of a MultiStudy class via a list of \emph{SubStudySpec} objects
-in the \emph{add\_sub\_study\_specs} class attribute, in the manner of
+in the \emph{add\_sub\_study\_specs} class attribute in the manner of
 data and parameter specifications. A SubStudySpec consists of a name, a
@@
 dictionary maps data and parameter specification names from the
-namespace of the MultiStudy class to the namespace of the Study class.
+sub-study namespace to the namespace of the MultiStudy class.
 
@@
 referenced in the sub study's name map are implicitly mapped to the
-MultiStudy namespace in the construction of the MultiStudy class by the
-metaclass using the name of the sub-study as a prefix. If the spec is a
-derivative then the pipeline constructor used to derive it is also
-mapped into the MultiStudy namespace. For example, \emph{derived1} in
+MultiStudy namespace by the MultiStudyMetaClass during construction of the MultiStudy class,
+using the name of the sub-study as a prefix.
+If the specification is derived, then its associated pipeline constructor method
+is also mapped into the MultiStudy namespace. For example, \emph{derived1} in
 \emph{sub\_study2} would be mapped to \emph{sub\_study2\_derived1} along

### 2018-10-23 code/arcana_paper.py

@@ -1,7 +1,7 @@
 #!/usr/bin/env python3
 from arcana import (
     MultiStudy, MultiStudyMetaClass, SubStudySpec, ParameterSpec)
-from banana.study.mri import (
+from banana import (
     DmriStudy, T1Study, T2starStudy, MriStudy)
 from banana.plot import ImageDisplayMixin
 
@@ -15,23 +15,24 @@ class ArcanaPaper(MultiStudy, ImageDisplayMixin,
     """
 
     add_sub_study_specs = [
-        # Include two Study classes in the overall study
+        # Sub-study to process the T1-weighted data
         SubStudySpec(
             't1',
             T1Study),
+        # Sub-study to process the T2*-weighted data
         SubStudySpec(
             't2star',
             T2starStudy,
-            name_map={'t1_brain': 'coreg_ref_brain',
-                      't1_coreg_to_atlas_mat': 'coreg_to_atlas_mat',
-                      't1_coreg_to_atlas_warp': 'coreg_to_atlas_warp'}),
+            name_map={'coreg_ref_brain': 't1_brain',
+                      'coreg_to_atlas_mat': 't1_coreg_to_atlas_mat',
+                      'coreg_to_atlas_warp': 't1_coreg_to_atlas_warp'}),
+        # Sub-study to process the dMRI data
         SubStudySpec(
             'dmri',
             DmriStudy),
         # Since we are using the SWI image produced from the scanner console
-        # we need to brain extract it in order to display it properly, so
-        # we create a basic MriStudy to use its brain extraction before
-        # mapping the extracted image to the T2* study.
+        # we need to brain extract it in order to compare with QSM/vein image/
+        # mask, which we do with a basic MriStudy.
         SubStudySpec(
             'swi',
             MriStudy)]
@@ -43,7 +44,7 @@ class ArcanaPaper(MultiStudy, ImageDisplayMixin,
                   "intersect a cerebral hemisphere instead of the "
                   "midline between the hemispheres")),
         # Override default values to reduce the number of tracks in order to
-        # make it easier to see the tracts
+        # make it easier to see the tracts in tractography figure.
         ParameterSpec('dmri_num_global_tracks', int(1e5)),
         ParameterSpec('dmri_global_tracks_cutoff', 0.175)]
 
@@ -91,7 +92,9 @@ class ArcanaPaper(MultiStudy, ImageDisplayMixin,
             displayed instead of saved
         """
         # Derive FA and ADC if necessary and return a handle to the
-        # data collections in the repository
[…]

### 2018-10-23 code/example_application.py

@@ -47,7 +47,7 @@ study = ExampleStudy(
 # Generate whole brain tracks and return path to
 # a cached dataset
 derived5 = study.data('whole_brain_tracks')
-print("The \"derived5\" fileset for the second visit "
-      "of subject 'PILOT1' were produced at:\n{}"
+print("The \"derived5\" fileset for the 'SECOND' visit "
+      "of subject 'PILOT1' was produced at:\n{}"
       .format(derived5.path(subject_id='PILOT1',
-                            visit_id=1)))
+                            visit_id='SECOND')))

### 2018-10-30 manuscript/manuscript.tex
added code for floating listings (but then disabled them again)

@@
 
+\usepackage{float}
 \usepackage{natbib}
@@
 \lstset{
-%    captionpos=b,                    % sets the caption-position to bottom
+    captionpos=b,                    % sets the caption-position to bottom
     language=Python,                 % the language of the code
@@
     keywordstyle=\color{keywordcolour}\bfseries,       % keyword style
+    float
 }
+
+\newfloat{lstfloat}{htbp}{lop}
+\floatname{lstfloat}{Listing}
+\def\lstfloatautorefname{Listing}
 

### 2018-12-19 manuscript/manuscript.tex
added t2 study and freesurfer

@@
 256x232x72, FOV 230x208x130, TE = 20ms, TR, = 30ms,
-bandwidth = 120Hz/pixel), and diffusion MRI (1.2 mm contiguous, matrix size
+bandwidth = 120Hz/pixel), and diffusion MRI (2 mm contiguous, matrix size
 110x100x60, FOV 256x240x192, TE = 95ms, TR, = 8200ms, 33 diffusion

### 2018-12-19 code/arcana_paper.py

@@ -2,7 +2,7 @@
 from arcana import (
     MultiStudy, MultiStudyMetaClass, SubStudySpec, ParameterSpec)
 from banana.study import (
-    DmriStudy, T1Study, T2starStudy, MriStudy)
+    DmriStudy, T1Study, T2Study, T2starStudy, MriStudy)
 from banana.plot import ImageDisplayMixin
 
 
@@ -18,7 +18,14 @@ class ArcanaPaper(MultiStudy, ImageDisplayMixin,
         # Sub-study to process the T1-weighted data
         SubStudySpec(
             't1',
-            T1Study),
+            T1Study,
+            name_map={
+                't2_coreg': 't2_coreg'}),
+        SubStudySpec(
+            't2',
+            T2Study,
+            name_map={
+                'coreg_ref': 't1_magnitude'}),
         # Sub-study to process the T2*-weighted data
         SubStudySpec(
             't2star',
@@ -172,6 +179,8 @@ if __name__ == '__main__':
                                         'arcana-paper-fig'))
     parser.add_argument('--t1', default='.*mprage.*',
                         help="Pattern to match T1-weighted scan")
+    parser.add_argument('--t2', default='.*t2_spc_da_fl.*',
+                        help="Pattern to match T1-weighted scan")
     parser.add_argument('--t2star_chann', default='.*channels.*',
                         help=("Pattern to match separate channels from the "
                               "head coil for the T2*-weighted scan in "
@@ -204,13 +213,16 @@ if __name__ == '__main__':
         # Use a single process on the local system to derive
         processor=LinearProcessor(args.work_dir, reprocess=args.reprocess,
                                   prov_ignore=DEFAULT_PROV_IGNORE + [
-                                      '/workflow/nodes/.*/requirements']),
+                                      '/workflow/.*'],
+                                  clean_work_dir_between_runs=False),
         # Use the static environment (i.e. no Modules)
         environment=StaticEnvironment(),
         # Match names in the data specification to filenames used
         # in the repository
         inputs=[
             FilesetSelector('t1_magnitude', args.t1, dicom_format,
+                            is_regex=True),
+            FilesetSelector('t2_magnitude', args.t2, dicom_format,
                             is_regex=True),
             FilesetSelector('t2star_channels', args.t2star_chann, zip_format,
[…]

### 2018-12-19 code/freesurfer.py

@@ -1,0 +1,88 @@
+#!/usr/bin/env python3
+from arcana import (
+    MultiStudy, MultiStudyMetaClass, SubStudySpec)
+from banana.study import (
+    T1Study, T2Study)
+import os
+import os.path as op
+import logging
+from argparse import ArgumentParser
+from arcana import (
+    DirectoryRepository, LinearProcessor, StaticEnvironment,
+    FilesetSelector, DEFAULT_PROV_IGNORE)
+from arcana.utils import parse_value
+from banana.file_format import nifti_gz_format
+
+logger = logging.getLogger('arcana')
+logger.setLevel(logging.INFO)
+handler = logging.StreamHandler()
+formatter = logging.Formatter("%(levelname)s - %(message)s")
+handler.setFormatter(formatter)
+logger.addHandler(handler)
+
+
+class FreesurferStudy(MultiStudy, metaclass=MultiStudyMetaClass):
+    """
+    An Study class to perform the analyses performed in the paper
+    introducing Arcana. Requires a repository containing
+    T1-weighted, T2*-weighted and diffusion MRI data.
+    """
+
+    add_sub_study_specs = [
+        # Sub-study to process the T1-weighted data
+        SubStudySpec(
+            't1',
+            T1Study,
+            name_map={
+                't2_coreg': 't2_coreg'}),
+        SubStudySpec(
+            't2',
+            T2Study,
+            name_map={
+                'coreg_ref': 't1_magnitude'})]
+
+
+# Set up parser to parse arguments passed to the script
+parser = ArgumentParser(
+    "A script to produce figures for the Arcana manuscript")
+parser.add_argument('data_dir',
+                    help="The directory containing repository")
+parser.add_argument('--work_dir', help="The work directory",
+                    default=op.join(op.expanduser('~'),
+                                    'arcana-paper-work'))
+args = parser.parse_args()
+
+# Make figure directory
+os.makedirs(args.fig_dir, exist_ok=True)
+
+# Instantiate the ArcanaPaper class in order to apply it to a
+# specific dataset
+paper = FreesurferStudy(
+    # Name for this analysis instance
+    'fs',
+    # Repository is a simple directory on the local file system
+    repository=DirectoryRepository(args.data_dir),
+    # Use a single process on the local system to derive
+    processor=LinearProcessor(args.work_dir, reprocess=args.reprocess,
+                              prov_ignore=DEFAULT_PROV_IGNORE + [
[…]

### 2018-12-19 code/freesurfer.py
fixed up freesurfer script, although it isn't running

@@ -52,8 +52,6 @@ parser.add_argument('--work_dir', help="The work directory",
                                     'arcana-paper-work'))
 args = parser.parse_args()
 
-# Make figure directory
-os.makedirs(args.fig_dir, exist_ok=True)
 
 # Instantiate the ArcanaPaper class in order to apply it to a
 # specific dataset
@@ -63,7 +61,7 @@ paper = FreesurferStudy(
     # Repository is a simple directory on the local file system
     repository=DirectoryRepository(args.data_dir),
     # Use a single process on the local system to derive
-    processor=LinearProcessor(args.work_dir, reprocess=args.reprocess,
+    processor=LinearProcessor(args.work_dir,
                               prov_ignore=DEFAULT_PROV_IGNORE + [
                                   '/workflow/.*'],
                               clean_work_dir_between_runs=False),
@@ -76,10 +74,11 @@ paper = FreesurferStudy(
                         is_regex=True),
         FilesetSelector('t2_preproc', 't2_preproc', nifti_gz_format,
                         is_regex=True)],
-    # Set parameters of the study
-    parameters={n: parse_value(v.strip()) for n, v in args.parameter})
+        enforce_inputs=False)
 
+print('Running freesurfer')
 paper.data('t1_fs_recon_all')
+print('Ran freesurfer')
 
     # Derive required data and display them in a single step for each
     # figure.

### 2018-12-19 code/freesurfer.py
fixed up freesurfer script to treat preproc as mags

@@ -70,11 +70,11 @@ paper = FreesurferStudy(
     # Match names in the data specification to filenames used
     # in the repository
     inputs=[
-        FilesetSelector('t1_preproc', 't1_preproc', nifti_gz_format,
+        FilesetSelector('t1_magnitude', 't1_preproc', nifti_gz_format,
                         is_regex=True),
-        FilesetSelector('t2_preproc', 't2_preproc', nifti_gz_format,
+        FilesetSelector('t2_magnitude', 't2_preproc', nifti_gz_format,
                         is_regex=True)],
-        enforce_inputs=False)
+    enforce_inputs=False)
 
 print('Running freesurfer')
 paper.data('t1_fs_recon_all')

### 2019-03-12 manuscript/manuscript-export.tex
renamed DmriStudy to DwiStudy to match BIDS

@@
 All three classes, \emph{T1wStudy}, \emph{T2starwStudy} and
-\emph{DmriStudy}, inherit generic image analysis methods, such as
+\emph{DwiStudy}, inherit generic image analysis methods, such as
 registration and brain extraction, from the base class \emph{MRIStudy}.
@@
 
-The DmriStudy class implements diffusion tensor metrics, FA and ADC, as
+The DwiStudy class implements diffusion tensor metrics, FA and ADC, as
 well as global tractography using streamlines tracking from the MRtrix

### 2019-03-12 manuscript/manuscript.tex
renamed DmriStudy to DwiStudy to match BIDS

@@
 All three classes, \emph{T1Study}, \emph{T2starStudy} and
-\emph{DmriStudy}, inherit generic image analysis methods, such as
+\emph{DwiStudy}, inherit generic image analysis methods, such as
 registration and brain extraction, from the base class \emph{MriStudy}.
 
-The DmriStudy class implements the extraction of diffusion tensor metrics,
+The DwiStudy class implements the extraction of diffusion tensor metrics,
 FA and ADC, as well as whole-brain tractography using streamlines tracking from the MRtrix
@@
 
-The T1Study, T2starStudy and DmriStudy classes are
+The T1Study, T2starStudy and DwiStudy classes are
 aggregated into a single MultiStudy class,

### 2019-03-12 code/arcana_paper.py

@@ -2,7 +2,7 @@
 from arcana import (
     MultiStudy, MultiStudyMetaClass, SubStudySpec, ParameterSpec)
 from banana.study import (
-    DmriStudy, T1Study, T2Study, T2starStudy, MriStudy)
+    DwiStudy, T1Study, T2Study, T2starStudy, MriStudy)
 from banana.plot import ImageDisplayMixin
 
 
@@ -36,7 +36,7 @@ class ArcanaPaper(MultiStudy, ImageDisplayMixin,
         # Sub-study to process the dMRI data
         SubStudySpec(
             'dmri',
-            DmriStudy),
+            DwiStudy),
         # Since we are using the SWI image produced from the scanner console
         # we need to brain extract it in order to compare with QSM/vein image/
         # mask, which we do with a basic MriStudy.

### 2019-03-13 manuscript/manuscript.tex
reworked Pipeline.add paragraph to describe new structure

@@
 
-Interface traits are connected to inputs and outputs of the pipeline by
+Node interfaces are connected to each other, and to inputs and outputs of the pipeline, by
 providing \emph{inputs} and \emph{outputs} keyword arguments to the \emph{add} method. Both
-arguments take a dictionary, where the keys of the dictionary are the names of traits of the interface. The
-values of the dictionary are 2-tuples each consisting of the name of a data specification
-and the format the pipeline either expects or produces the data in (i.e. a FileFormat for Fileset specifications
-or Python datatype for Field specifications). If the expected format does not match that of the
-corresponding data specification or study input then a conversion node is implicitly connected
-to the pipeline. Inputs and outputs that are conditional on parameters or inputs provided to the
-study can be set outside of the \emph{add} method using the \emph{connect\_input} or
-\emph{connect\_output} methods, respectively.
-
-Connections between nodes are specified by a dictionary
-passed to the \emph{connect} keyword argument of the \emph{add} method
-that creates the receiving node. The dictionary keys are the names of the
-receiving traits and the values are 2-tuples
-consisting of the sending node and the name of the sending trait. Alternatively,
-conditional connections can be specified via the \emph{connect} method of the
-pipeline, which simply calls the method of the same name in the underlying
-Nipype workflow.
+arguments take a dictionary. The keys of the \emph{inputs} dictionary correspond to
+trait names in the node's input interface, whereas the keys of the \emph{outputs} dictionary correspond to
+names of entries in the data specification table. The values of both dictionaries are 2-tuples. For pipeline
+inputs, values of the \emph{inputs} dictionary consist of a name of an entry in the data specification table
+and the format the input is expected in (i.e. a FileFormat for Fileset specifications or Python datatype for Field specifications).
+For pipeline outputs, values of the \emph{outputs} dictionary consist of a trait name in the node's output interface and the format the
+output data is generated in. For input connections from other nodes, values of the \emph{inputs} dictionary
+consist of a reference to the upstream node and the name of a trait in the
+upstream node's output interface (output connections are implied by input connections to other nodes).
+
+If the expected format of a pipeline input or generated format of a pipeline output does not match that
+of the corresponding study input or data specification, then a conversion node is implicitly connected
+to the pipeline by the framework to perform the required conversion. Pipeline inputs and outputs of
+that are conditional on parameters or inputs provided to the study can be specified outside of the
+\emph{add} method using the \emph{connect\_input} or
+\emph{connect\_output} methods, respectively. Conditional connections between
+nodes can be specified via the \emph{connect} method of the pipeline (which simply calls the
+method of the same name in the underlying Nipype workflow).
 

### 2019-03-14 manuscript/manuscript.tex
ensured that mappings have the right key/value pairings

@@
 which must be unique amongst the pipelines constructed by the Study. The methods implemented
-by the pipeline can be characterised by providing a the list of scientific references
-and a text description to the \emph{references} and \emph{desc} keyword arguments, respectively.
+by the pipeline can be characterised by providing a the list of citations
+and a text description to the \emph{citations} and \emph{desc} keyword arguments, respectively.
 
@@
 Additionally the name of the pipeline can be altered by providing the \emph{name}
-argument, which is useful when creating multiple  constructor methods from the
-one base method. In these scenarios it is important to
+argument, which is useful when creating multiple pipeline constructor methods
+from a single base method. In these scenarios it is important to
 also pass the the wildcard keyword arguments of the overriding method to the
-\emph{name\_maps} keyword argument of the superclass method, to allow the
+\emph{name\_maps} keyword argument of the superclass method to allow the
 overriding method to be overridden in turn.
@@
 dictionary maps data and parameter specification names from the
-sub-study namespace to the namespace of the MultiStudy class.
+sub-study namespace to the namespace of the MultiStudy class, i.e.
+the dictionary keys are in the sub-study namespace and the dictionary
+values are in the global namespace.
 
@@
 referenced in the sub study's name map are implicitly mapped to the
-MultiStudy namespace by the MultiStudyMetaClass during construction of the MultiStudy class,
-using the name of the sub-study as a prefix.
-If the specification is derived, then its associated pipeline constructor method
-is also mapped into the MultiStudy namespace. For example, \emph{derived1} in
-\emph{sub\_study2} would be mapped to \emph{sub\_study2\_derived1} along
-with the method \emph{sub\_study2\_pipeline1}.
+MultiStudy namespace by the MultiStudyMetaClass during construction of the
+MultiStudy class using the name of the sub-study as a prefix.
+If the implicitly mapped specification is derived, then its associated pipeline
+constructor method is also mapped into the MultiStudy namespace with a prefix.
+For example, \emph{derived1} in \emph{sub\_study2} would be mapped to
+\emph{sub\_study2\_derived1} along with the method
+\emph{sub\_study2\_pipeline1}.
 
@@
 can be passed as a dictionary to the \emph{packages\_map} keyword argument
-at initialisation. Likewise non-standard versions for packages can be mapped onto
-requirements using the \emph{versions\_map} keyword argument.
+at initialisation. Likewise non-standard versions for packages can be mapped
+onto the versioning system of a requirement using the \emph{versions\_map}
+keyword argument.
 

### 2019-03-14 code/example_application.py

@@ -28,7 +28,7 @@ study = ExampleStudy(
     # package names explicitly mapped to approp. reqs.
     environment=ModulesEnvironment(
         packages_map={
-            'Package1_Parallel': package1_req}),
+            package1_req: 'Package1_Parallel'}),
     # Link files and fields in the repository
     # to entries in the data specification
     inputs={

### 2019-03-14 code/arcana_paper.py
renamed *Repository to *Repo

@@ -153,7 +153,7 @@ if __name__ == '__main__':
     import logging
     from argparse import ArgumentParser
     from arcana import (
-        DirectoryRepository, LinearProcessor, StaticEnvironment,
+        DirectoryRepo, LinearProcessor, StaticEnvironment,
         FilesetSelector, DEFAULT_PROV_IGNORE)
     from arcana.utils import parse_value
     from banana.file_format import dicom_format, zip_format
@@ -209,7 +209,7 @@ if __name__ == '__main__':
         # Name for this analysis instance
         'arcana_paper1',
         # Repository is a simple directory on the local file system
-        repository=DirectoryRepository(args.data_dir),
+        repository=DirectoryRepo(args.data_dir),
         # Use a single process on the local system to derive
         processor=LinearProcessor(args.work_dir, reprocess=args.reprocess,
                                   prov_ignore=DEFAULT_PROV_IGNORE + [

### 2019-03-14 examples/manuscript.py

@@ -1,6 +1,6 @@
 from arcana import (Study, StudyMetaClass, AcquiredFilesetSpec, FilesetSpec,
                     AcquiredFieldSpec, FieldSpec, ParameterSpec, SwitchSpec,
-                    FilesetCollection, XnatRepository, Fileset)
+                    FilesetCollection, XnatRepo, Fileset)
 from arcana.data.file_format.standard import text_format
 from banana.file_format import (
     nifti_gz_format, dicom_format, nifti_format, analyze_format)
@@ -8,7 +8,7 @@ from banana.file_format import (
 STD_IMAGE_FORMATS = (dicom_format, nifti_format, nifti_gz_format,
                      analyze_format)
 
-template_repo = XnatRepository('http://central.xnat.org', 'SAMPLE_TEMPLATES')
+template_repo = XnatRepo('http://central.xnat.org', 'SAMPLE_TEMPLATES')
 template1_default = FilesetCollection(Fileset('sample_atlas', ))
 
 

### 2019-03-14 manuscript/manuscript.tex
renamed *Repository to *Repo
renamed ParameterSpec to ParamSpec

@@
 Similar to data specifications, parameter specifications are included in
-the Study class by providing a list of \emph{ParameterSpec} objects to
-the \emph{add\_param\_specs} class attribute. ParameterSpec objects
+the Study class by providing a list of \emph{ParamSpec} objects to
+the \emph{add\_param\_specs} class attribute. ParamSpec objects
 are initialised with a name and default value. Special parameters that
@@
 \citep{marcus_extensible_2007}, BIDS \citep{gorgolewski_brain_2016} and a simple
-``directory'' format, which are encapsulated by \emph{XnatRepository},
-\emph{BidsRepository}, and \emph{DirectoryRepository} classes
+``directory'' format, which are encapsulated by \emph{XnatRepo},
+\emph{BidsRepo}, and \emph{DirectoryRepo} classes
 respectively.

### 2019-03-14 code/arcana_paper.py

@@ -1,6 +1,6 @@
 #!/usr/bin/env python3
 from arcana import (
-    MultiStudy, MultiStudyMetaClass, SubStudySpec, ParameterSpec)
+    MultiStudy, MultiStudyMetaClass, SubStudySpec, ParamSpec)
 from banana.study import (
     DwiStudy, T1Study, T2Study, T2starStudy, MriStudy)
 from banana.plot import ImageDisplayMixin
@@ -45,15 +45,15 @@ class ArcanaPaper(MultiStudy, ImageDisplayMixin,
             MriStudy)]
 
     add_param_specs = [
-        ParameterSpec(
+        ParamSpec(
             'dmri_fig_slice_offset', (6, 0, 0),
             desc=("Offset the sagittal slices of dMRI figures so they "
                   "intersect a cerebral hemisphere instead of the "
                   "midline between the hemispheres")),
         # Override default values to reduce the number of tracks in order to
         # make it easier to see the tracts in tractography figure.
-        ParameterSpec('dmri_num_global_tracks', int(1e5)),
-        ParameterSpec('dmri_global_tracks_cutoff', 0.175)]
+        ParamSpec('dmri_num_global_tracks', int(1e5)),
+        ParamSpec('dmri_global_tracks_cutoff', 0.175)]
 
     def vein_fig(self, save_path=None, **kwargs):
         """

### 2019-03-14 examples/manuscript.py

@@ -1,5 +1,5 @@
 from arcana import (Study, StudyMetaClass, AcquiredFilesetSpec, FilesetSpec,
-                    AcquiredFieldSpec, FieldSpec, ParameterSpec, SwitchSpec,
+                    AcquiredFieldSpec, FieldSpec, ParamSpec, SwitchSpec,
                     FilesetCollection, XnatRepo, Fileset)
 from arcana.data.file_format.standard import text_format
 from banana.file_format import (
@@ -40,7 +40,7 @@ class ExampleStudy(Study, metaclass=StudyMetaClass):
 
     add_param_specs = [
         # Standard parameters
-        ParameterSpec('parameter1', 10),
-        ParameterSpec('parameter2', 25.8),
+        ParamSpec('parameter1', 10),
+        ParamSpec('parameter2', 25.8),
         # Parameters that specify a qualitative change in the analysis
         SwitchSpec('pipeline_tool', 'toolA', ('toolA', 'toolB'))]

### 2019-03-14 manuscript/manuscript.tex
Renamed Acquired*Spec with *InputSpec

@@
 
-The set of acquired data, the derivatives that can be derived from it,
+The set of input data, the derivatives that can be derived from it,
 and methods that construct pipelines to derive the derivatives, are
@@
     \includegraphics[width=0.55\textwidth]{../figures/example_study}
-  \caption{Example study. Blue boxes represent acquired (input)
+  \caption{Example study. Blue boxes represent input
 data (filesets or fields) stored in a repository and green derivatives
@@
 Specifications for acquired data (i.e. input data to the study) are
-distinguished from derived data by using the \emph{AcquiredFilesetSpec}
-and \emph{AcquiredFieldSpec} subtypes. However, the distinction is
+distinguished from derived data by using the \emph{FilesetInputSpec}
+and \emph{FieldInputSpec} subtypes. However, the distinction is
 fluid, with derived specifications able to be overridden by acquired
@@
 \caption{Example data and parameter specifications. The data
-specification specifies two ``acquired'' file sets, `one' and `ten' and
+specification specifies two input file sets, `one' and `ten' and
 ten derived file sets that can be derived from them, at least
@@
 namespaces (e.g. \emph{Derived} \emph{1}, \emph{2} and \emph{3}).
-There are no restrictions
-between mapping acquired and derivative specifications: both acquired
-and derivative specifications can be mapped onto acquired data or
-derivative specifications in sub-studies. If a spec in the global spaced
-is mapped onto a derivative spec in the sub-study space, then the
-pipeline that generates that derivative in the sub-study will not run
-unless it generates other required derivatives (e.g. \emph{Pipeline 3} in
-\emph{Sub-Study 2})}
+There are no restrictions between mapping input and derivative data
+specifications: both input and derivative specifications can be mapped
+onto input data or derivative specifications in sub-studies.
+If a spec in the global spaced is mapped onto a derivative spec in the
+sub-study space, then the pipeline that generates that derivative in the
+sub-study will not run unless it generates other required derivatives
+(e.g. \emph{Pipeline 3} in \emph{Sub-Study 2})}
 \label{fig:example_multi_study}
@@
 no restrictions on selecting any data, derived or otherwise, to match
-acquired or derived specifications. For example, it is possible to
+input or derived specifications. For example, it is possible to
 deliberately skip analysis steps by selecting an output of an early step
@@
 Mapping (QSM) and Susceptible Weighted Imaging (SWI) contrasts with a
-manual atlas. Blue boxes: acquired (input) data (filesets or fields).
+manual atlas. Blue boxes: input data (filesets or fields).
 Green boxes: derivatives. Orange ovals: pipelines. Blue and green
-arrows: acquired and derived inputs to pipelines, respectively. Orange
+arrows: inputs to pipelines from input and derived data, respectively. Orange
 arrows: outputs of pipelines. Dashed boxes represent data specifications

### 2019-03-14 examples/manuscript.py

@@ -1,5 +1,5 @@
-from arcana import (Study, StudyMetaClass, AcquiredFilesetSpec, FilesetSpec,
-                    AcquiredFieldSpec, FieldSpec, ParamSpec, SwitchSpec,
+from arcana import (Study, StudyMetaClass, FilesetInputSpec, FilesetSpec,
+                    FieldInputSpec, FieldSpec, ParamSpec, SwitchSpec,
                     FilesetCollection, XnatRepo, Fileset)
 from arcana.data.file_format.standard import text_format
 from banana.file_format import (
@@ -16,13 +16,13 @@ class ExampleStudy(Study, metaclass=StudyMetaClass):
 
     add_data_specs = [
         # Acquired file sets
-        AcquiredFilesetSpec('acquired_file1', text_format),
-        AcquiredFilesetSpec('acquired_file2', IMAGE_FORMATS),
+        FilesetInputSpec('acquired_file1', text_format),
+        FilesetInputSpec('acquired_file2', IMAGE_FORMATS),
         # Acquired fields
-        AcquiredFieldSpec('acquired_field1', int, frequency='per_subject'),
-        AcquiredFieldSpec('acquired_field2', str,),
+        FieldInputSpec('acquired_field1', int, frequency='per_subject'),
+        FieldInputSpec('acquired_field2', str,),
         # "Acquired" file set with default value. Useful for standard templates
-        AcquiredFilesetSpec('template1', IMAGE_FORMATS, frequency='per_study',
+        FilesetInputSpec('template1', IMAGE_FORMATS, frequency='per_study',
                             default=template1_default),
         # Derived file sets
         FilesetSpec('derived_file1', text_format, 'pipeline1'),

### 2019-03-14 manuscript/manuscript.tex
Renamed *Selector to *Input

@@
 
-Selection criteria are specified by list of \emph{FilesetSelector} and
-\emph{FieldSelector} objects provided to the \emph{inputs} argument of
+Selection criteria are specified by list of \emph{FilesetInput} and
+\emph{FieldInput} objects provided to the \emph{inputs} argument of
 the Study initialisation method. Matching is typically performed on file

### 2019-03-14 code/arcana_paper.py

@@ -154,7 +154,7 @@ if __name__ == '__main__':
     from argparse import ArgumentParser
     from arcana import (
         DirectoryRepo, LinearProcessor, StaticEnvironment,
-        FilesetSelector, DEFAULT_PROV_IGNORE)
+        FilesetInput, DEFAULT_PROV_IGNORE)
     from arcana.utils import parse_value
     from banana.file_format import dicom_format, zip_format
 
@@ -220,21 +220,21 @@ if __name__ == '__main__':
         # Match names in the data specification to filenames used
         # in the repository
         inputs=[
-            FilesetSelector('t1_magnitude', args.t1, dicom_format,
+            FilesetInput('t1_magnitude', args.t1, dicom_format,
                             is_regex=True),
-            FilesetSelector('t2_magnitude', args.t2, dicom_format,
+            FilesetInput('t2_magnitude', args.t2, dicom_format,
                             is_regex=True),
-            FilesetSelector('t2star_channels', args.t2star_chann, zip_format,
+            FilesetInput('t2star_channels', args.t2star_chann, zip_format,
                             is_regex=True),
-            FilesetSelector('t2star_header_image', args.swi, dicom_format,
+            FilesetInput('t2star_header_image', args.swi, dicom_format,
                             is_regex=True),
-            FilesetSelector('t2star_swi', args.swi, dicom_format,
+            FilesetInput('t2star_swi', args.swi, dicom_format,
                             is_regex=True),
-            FilesetSelector('swi_magnitude', args.swi, dicom_format,
+            FilesetInput('swi_magnitude', args.swi, dicom_format,
                             is_regex=True),
-            FilesetSelector('dmri_magnitude', args.dmri, dicom_format,
+            FilesetInput('dmri_magnitude', args.dmri, dicom_format,
                             is_regex=True),
-            FilesetSelector('dmri_reverse_phase', args.distort, dicom_format,
+            FilesetInput('dmri_reverse_phase', args.distort, dicom_format,
                             is_regex=True)],
         # Set parameters of the study
         parameters={n: parse_value(v.strip()) for n, v in args.parameter})

### 2019-03-14 manuscript/manuscript.tex
renamed BidsSelector BidsInput

@@
 For fileset specifications that correspond to a known type in the BIDS
-standard, a \emph{BidsSelector} or \emph{BidsAssociatedSelector} can be
-provided to the \emph{bids} keyword arg of the spec. BidsSelector
+standard, a \emph{BidsInput} or \emph{BidsAssocInput} can be
+provided to the \emph{bids} keyword arg of the spec. BidsInput
 specifies a primary scan in the BIDS standard using its type, modality
-and optional run number. BidsAssociatedSelector is used to select
+and optional run number. BidsAssocInput is used to select
 associated files, such as field maps and diffusion encoding matrices.
-When passing a BidsSelector to a FilesetSpec the \emph{run} keyword
+When passing a BidsInput to a FilesetSpec the \emph{run} keyword
 argument of the selector is typically not set, so it can be read from
@@
 specifications)} so inputs do not need to be provided to the
-initialisation of the Study. However, BidsSelector and
-BidsAssociatedSelector objects can be provided to override the default
+initialisation of the Study. However, BidsInput and
+BidsAssocInput objects can be provided to override the default
 selections is required.

### 2019-03-14 manuscript/manuscript.tex
renamed *Processor -> *Proc and LinearProc to SingleProc

@@
 are executed. There currently three Processor modules implemented in
-Arcana: \emph{LinearProcessor}, \emph{MultiProcProcessor},
-\emph{SlurmProcessor}, which wrap the
+Arcana: \emph{SingleProc}, \emph{MultiProcProc},
+\emph{SlurmProc}, which wrap the
 correspondingly named Nipype execution plugins. The main task performed

### 2019-03-14 code/arcana_paper.py

@@ -153,7 +153,7 @@ if __name__ == '__main__':
     import logging
     from argparse import ArgumentParser
     from arcana import (
-        DirectoryRepo, LinearProcessor, StaticEnvironment,
+        DirectoryRepo, SingleProc, StaticEnvironment,
         FilesetInput, DEFAULT_PROV_IGNORE)
     from arcana.utils import parse_value
     from banana.file_format import dicom_format, zip_format
@@ -211,7 +211,7 @@ if __name__ == '__main__':
         # Repository is a simple directory on the local file system
         repository=DirectoryRepo(args.data_dir),
         # Use a single process on the local system to derive
-        processor=LinearProcessor(args.work_dir, reprocess=args.reprocess,
+        processor=SingleProc(args.work_dir, reprocess=args.reprocess,
                                   prov_ignore=DEFAULT_PROV_IGNORE + [
                                       '/workflow/.*'],
                                   clean_work_dir_between_runs=False),

### 2019-03-14 manuscript/manuscript.tex
Fixed up references to processor names

@@
 are executed. There currently three Processor modules implemented in
-Arcana: \emph{SingleProc}, \emph{MultiProcProc},
-\emph{SlurmProc}, which wrap the
-correspondingly named Nipype execution plugins. The main task performed
+Arcana: \emph{SingleProc}, \emph{MultiProc},
+\emph{SlurmProc}, which wrap the LinearPlugin, MultiProcPlugin and SlurmPlugin
+Nipype execution plugins. The main task performed
 by the processor, as separate from the Nipype execution plugin it wraps,

### 2019-03-14 manuscript/manuscript.tex
renamed *Environment -> *Env

@@
 There are currently two types of Environment class implemented in Arcana:
-\emph{StaticEnvironment} and \emph{ModulesEnvironment}.
-
-\emph{ModulesEnvironment} objects can be used if environment
+\emph{StaticEnv} and \emph{ModulesEnv}.
+
+\emph{ModulesEnv} objects can be used if environment
 modules \citep{furlani_modules:_1991} are installed on the system (typical in many
@@
 
-\emph{StaticEnvironment} objects don't actively manage the environment,
+\emph{StaticEnv} objects don't actively manage the environment,
 and instead only check the current environment for appropriate software

### 2019-03-14 code/arcana_paper.py

@@ -153,7 +153,7 @@ if __name__ == '__main__':
     import logging
     from argparse import ArgumentParser
     from arcana import (
-        DirectoryRepo, SingleProc, StaticEnvironment,
+        DirectoryRepo, SingleProc, StaticEnv,
         FilesetInput, DEFAULT_PROV_IGNORE)
     from arcana.utils import parse_value
     from banana.file_format import dicom_format, zip_format
@@ -216,7 +216,7 @@ if __name__ == '__main__':
                                       '/workflow/.*'],
                                   clean_work_dir_between_runs=False),
         # Use the static environment (i.e. no Modules)
-        environment=StaticEnvironment(),
+        environment=StaticEnv(),
         # Match names in the data specification to filenames used
         # in the repository
         inputs=[

### 2019-03-14 code/arcana_paper.py
Renamed DirectoryRepo to BasicRepo

@@ -153,7 +153,7 @@ if __name__ == '__main__':
     import logging
     from argparse import ArgumentParser
     from arcana import (
-        DirectoryRepo, SingleProc, StaticEnv,
+        BasicRepo, SingleProc, StaticEnv,
         FilesetInput, DEFAULT_PROV_IGNORE)
     from arcana.utils import parse_value
     from banana.file_format import dicom_format, zip_format
@@ -209,7 +209,7 @@ if __name__ == '__main__':
         # Name for this analysis instance
         'arcana_paper1',
         # Repository is a simple directory on the local file system
-        repository=DirectoryRepo(args.data_dir),
+        repository=BasicRepo(args.data_dir),
         # Use a single process on the local system to derive
         processor=SingleProc(args.work_dir, reprocess=args.reprocess,
                                   prov_ignore=DEFAULT_PROV_IGNORE + [

### 2019-03-14 code/arcana_paper.py
tidied up arcana paper example

@@ -153,8 +153,7 @@ if __name__ == '__main__':
     import logging
     from argparse import ArgumentParser
     from arcana import (
-        BasicRepo, SingleProc, StaticEnv,
-        FilesetInput, DEFAULT_PROV_IGNORE)
+        BasicRepo, SingleProc, StaticEnv, FilesetInput)
     from arcana.utils import parse_value
     from banana.file_format import dicom_format, zip_format
 
@@ -179,7 +178,7 @@ if __name__ == '__main__':
                                         'arcana-paper-fig'))
     parser.add_argument('--t1', default='.*mprage.*',
                         help="Pattern to match T1-weighted scan")
-    parser.add_argument('--t2', default='.*t2_spc_da_fl.*',
+    parser.add_argument('--t2', default='.*t2.*',
                         help="Pattern to match T1-weighted scan")
     parser.add_argument('--t2star_chann', default='.*channels.*',
                         help=("Pattern to match separate channels from the "
@@ -188,7 +187,7 @@ if __name__ == '__main__':
                               "directory"))
     parser.add_argument('--swi', default='.*(swi|SWI).*',
                         help="Pattern to match SWI scan in DICOM format")
-    parser.add_argument('--dmri', default='.*diff.*',
+    parser.add_argument('--dwi', default='.*diff.*',
                         help="Pattern to match dMRI scan")
     parser.add_argument('--distort', default='.*distortion_correction.*',
                         help="Pattern to match dMRI reverse PE ref. scan")
@@ -210,39 +209,29 @@ if __name__ == '__main__':
         'arcana_paper1',
         # Repository is a simple directory on the local file system
         repository=BasicRepo(args.data_dir),
-        # Use a single process on the local system to derive
-        processor=SingleProc(args.work_dir, reprocess=args.reprocess,
-                                  prov_ignore=DEFAULT_PROV_IGNORE + [
-                                      '/workflow/.*'],
-                                  clean_work_dir_between_runs=False),
-        # Use the static environment (i.e. no Modules)
+        # Use a single process on the local system to run pipelines
+        processor=SingleProc(args.work_dir, reprocess=args.reprocess),
+        # Use the software installed and on the curren PATH (i.e. no Modules)
         environment=StaticEnv(),
         # Match names in the data specification to filenames used
         # in the repository
-        inputs=[
-            FilesetInput('t1_magnitude', args.t1, dicom_format,
[…]

### 2019-03-14 manuscript/manuscript.tex
Renamed DirectoryRepo to BasicRepo
syntax updates

@@
 \ref{fig:simple_uml}). Input data to a study are selected from repositories
- using criteria defined in \emph{Selector} objects passed to the Study
+ using criteria defined in \emph{Input} objects passed to the Study
  object at initialisation and matched against entries in the class' data
@@
 construct analysis pipelines, which are sent to the \emph{Processor} to
-be processed. Input data is selected by \emph{Selector} objects and
+be processed. Input data is selected by \emph{Input} objects and
 pulled to the compute environment to be processed along with existing
@@
     \includegraphics[width=0.775\textwidth]{../figures/example_multi_study}
-  \caption{Example MultiStudy. Blue boxes represent acquired
-(input) data (filesets or fields) and green derivatives. Orange ovals
-are pipelines. Blue and green arrows: acquired and derived inputs to
-pipelines, respectively. Orange arrows: outputs of pipelines. Dashed
+  \caption{Example MultiStudy. Blue boxes represent input data
+(filesets or fields) and green derivatives. Orange ovals
+are pipelines. Blue and green arrows: pipeline inputs from study inputs
+and derived data, respectively. Orange arrows: outputs of pipelines. Dashed
 boxes represent data specifications in a sub-study that are present in
@@
 namespaces (e.g. \emph{Derived} \emph{1}, \emph{2} and \emph{3}).
-There are no restrictions between mapping input and derivative data
+There are no restrictions between mapping study input and derivative data
 specifications: both input and derivative specifications can be mapped
@@
 to the \emph{Processor} to be processed. Data is selected by
-\emph{Selector} objects, pulled to the compute environment to be
+\emph{Input} objects, pulled to the compute environment to be
 processed, and then the derivatives are pushed back to the repository.
@@
 Repository, Processor and Environment modules to use and a list of
-\emph{Selector} objects to select input data from the repository and match
+\emph{Input} objects to select input data from the repository and match
 it with the Study's data specification table.
@@
 ``directory'' format, which are encapsulated by \emph{XnatRepo},
-\emph{BidsRepo}, and \emph{DirectoryRepo} classes
+\emph{BidsRepo}, and \emph{BasicRepo} classes
 respectively.
@@
 with the data specification of the Study class, arbitrary naming
-conventions can be used for input datasets and fields to allow for
-heterogeneity in acquisition procedures. A selection stage is therefore
-necessary to match input data to appropriate entries in the data
-specification table of the Study class. The criteria for this selection
-is passed to the Study object at instantiation and is required to match
-exactly one fileset or field in every session included in the study.
-
-Selection criteria are specified by list of \emph{FilesetInput} and
-\emph{FieldInput} objects provided to the \emph{inputs} argument of
-the Study initialisation method. Matching is typically performed on file
-names (dataset labels for XNAT repositories), and field names. If the
+conventions can be used for input datasets and fields. A selection
+stage matches input data to entries in the data specification table of
+the Study class. The criteria for these selections are passed to the
+the \emph{inputs} argument of the Study object at instantiation in a
+dictionary mapping data specification names to \emph{FilesetInput} and
+\emph{FieldInput} objects, and are required
+to match exactly one fileset or field in every session included in the study.
+
+Matching is typically performed on file
+names (dataset labels for XNAT repositories) and field names. If the
 names are inconsistent across the study then regular expressions can be
-used instead of exact matches by passing \emph{is\_regex=True} when
-initialising the Selector. Additional criteria can be used to
-distinguish cases where multiple filesets in the session match the
-pattern provided, such as DICOM header values, or the order and ID
-of the dataset.
+used instead of exact matches with the \emph{pattern} keyword argument.
+Additional criteria can be used to distinguish cases where multiple
+filesets in the session match the pattern provided, such as DICOM
+header values, or the order and ID of the dataset.
 
 Inputs can be drawn from auxiliary repositories by providing alternative
-Repository instances to the \emph{repository} keyword of the Selector.
+Repository instances to the \emph{repository} keyword of the Input.
 Care should be taken to ensure that the subject and visit ID schemes
@@
     \includegraphics[width=0.55\textwidth]{../figures/dmri_study}
-  \caption{Example diffusion MRI (dMRI) study, which can derive
+  \caption{Example diffusion-weighted MRI (DWI) study, which can derive
 tensor metrics, fractional anisotropy (FA) and apparent diffusion

### 2019-03-14 code/example_application.py

@@ -1,8 +1,7 @@
 #!/usr/bin/env python3
 import os.path as op
 from arcana import (
-    FilesetSelector, FieldSelector, XnatRepository,
-    SlurmProcessor, ModulesEnvironment)
+    FilesetInput, FieldInput, XnatRepo, SlurmProc, ModulesEnv)
 from .example_study import ExampleStudy
 from banana.file_format import dicom_format
 from myproj.requirements import package1_req
@@ -15,31 +14,30 @@ study = ExampleStudy(
     # performed on the same data
     name='example',
     # Set up connection to XNAT repository
-    repository=XnatRepository(
+    repository=XnatRepo(
         project_id='SAMPLE_PROJECT',
         server='https://central.xnat.org',
         cache_dir=op.expanduser('~/xnat-cache')),
     # Specify the use the SLURM scheduler to submit
     # nodes as jobs using Nipype's SlurmGraphPlugin
-    processor=SlurmProcessor(
+    processor=SlurmProc(
         work_dir=op.expanduser('~/work')),
     # Specify the use of environment modules to
     # satisfy software requirements. Non-standard
     # package names explicitly mapped to approp. reqs.
-    environment=ModulesEnvironment(
+    environment=ModulesEnv(
         packages_map={
             package1_req: 'Package1_Parallel'}),
     # Link files and fields in the repository
     # to entries in the data specification
     inputs={
-        'acquired1_file': FilesetSelector(
-            '.*mprage.*', dicom_format, is_regex=True),
-        'acquired_file2': FilesetSelector(
-            'SWI_Images', dicom_format),
-        'acquired_field1': FieldSelector(
-            'YOB', int, frequency='per_subject'),
-        'acquired_field2': FieldSelector(
-            'weight', float)},
+        'acquired1_file': FilesetInput(pattern='.*mprage.*',
+                                       dicom_format),
+        'acquired_file2': FilesetInput('SWI_Images',
+                                       dicom_format),
+        'acquired_field1': FieldInput('YOB', int,
+                                      frequency='per_subject'),
+        'acquired_field2': FieldInput('weight', float)},
     # Specify parameters specific to this
     # analysis
     parameters={'parameter1': 55.0,

### 2019-03-14 code/example_study.py

@@ -1,8 +1,8 @@
 import os
 from arcana import (
-    Study, StudyMetaClass, AcquiredFilesetSpec, FilesetSpec,
-    AcquiredFieldSpec, FieldSpec, ParameterSpec, SwitchSpec,
-    FilesetSelector, XnatRepository)
+    Study, StudyMetaClass, FilesetInputSpec, FilesetSpec,
+    FieldInputSpec, FieldSpec, ParamSpec, SwitchSpec,
+    FilesetInput, XnatRepo)
 from banana.file_format import (
     nifti_gz_format, dicom_format, nifti_format, analyze_format,
     text_format, text_matrix_format)
@@ -11,12 +11,11 @@ STD_IMAGE_FORMATS = (dicom_format, nifti_format, nifti_gz_format,
                      analyze_format)
 
 # Select a Fileset collection to use as a default for template1
-template_repo = XnatRepository(
+template_repo = XnatRepo(
     server='http://central.xnat.org', project_id='TEMPLATES',
     cache=os.path.expanduser(os.path.join('~', 'xnat-cache')))
-template_selector = FilesetSelector(
-    name='template1_default', format=nifti_gz_format,
-    pattern='MNI152_T1', frequency='per_study')
+template_selector = FilesetInput('MNI152_T1', nifti_gz_format,
+                                 frequency='per_study')
 template_collectn = template_selector.match(template_repo.tree())
 
 
@@ -24,21 +23,22 @@ class ExampleStudy(Study, metaclass=StudyMetaClass):
 
     add_data_specs = [
         # Acquired file sets
-        AcquiredFilesetSpec('acquired_file1', text_format),
-        AcquiredFilesetSpec('acquired_file2', STD_IMAGE_FORMATS),
+        FilesetInputSpec('acquired_file1', text_format),
+        FilesetInputSpec('acquired_file2', STD_IMAGE_FORMATS),
         # Acquired fields
-        AcquiredFieldSpec('acquired_field1', int, array=True,
-                          frequency='per_subject'),
-        AcquiredFieldSpec('acquired_field2', float, optional=True),
+        FieldInputSpec('acquired_field1', int, array=True,
+                       frequency='per_subject'),
+        FieldInputSpec('acquired_field2', float, optional=True),
         # "Acquired" file set with default value. Useful for
         # standard templates
-        AcquiredFilesetSpec('template1', STD_IMAGE_FORMATS,
-                            frequency='per_study',
-                            default=template_collectn),
[…]

### 2019-03-14 code/freesurfer.py

@@ -1,87 +1,0 @@
-#!/usr/bin/env python3
-from arcana import (
-    MultiStudy, MultiStudyMetaClass, SubStudySpec)
-from banana.study import (
-    T1Study, T2Study)
-import os
-import os.path as op
-import logging
-from argparse import ArgumentParser
-from arcana import (
-    DirectoryRepository, LinearProcessor, StaticEnvironment,
-    FilesetSelector, DEFAULT_PROV_IGNORE)
-from arcana.utils import parse_value
-from banana.file_format import nifti_gz_format
-
-logger = logging.getLogger('arcana')
-logger.setLevel(logging.INFO)
-handler = logging.StreamHandler()
-formatter = logging.Formatter("%(levelname)s - %(message)s")
-handler.setFormatter(formatter)
-logger.addHandler(handler)
-
-
-class FreesurferStudy(MultiStudy, metaclass=MultiStudyMetaClass):
-    """
-    An Study class to perform the analyses performed in the paper
-    introducing Arcana. Requires a repository containing
-    T1-weighted, T2*-weighted and diffusion MRI data.
-    """
-
-    add_sub_study_specs = [
-        # Sub-study to process the T1-weighted data
-        SubStudySpec(
-            't1',
-            T1Study,
-            name_map={
-                't2_coreg': 't2_coreg'}),
-        SubStudySpec(
-            't2',
-            T2Study,
-            name_map={
-                'coreg_ref': 't1_magnitude'})]
-
-
-# Set up parser to parse arguments passed to the script
-parser = ArgumentParser(
-    "A script to produce figures for the Arcana manuscript")
-parser.add_argument('data_dir',
-                    help="The directory containing repository")
-parser.add_argument('--work_dir', help="The work directory",
-                    default=op.join(op.expanduser('~'),
-                                    'arcana-paper-work'))
-args = parser.parse_args()
-
-
-# Instantiate the ArcanaPaper class in order to apply it to a
-# specific dataset
-paper = FreesurferStudy(
-    # Name for this analysis instance
-    'fs',
-    # Repository is a simple directory on the local file system
-    repository=DirectoryRepository(args.data_dir),
-    # Use a single process on the local system to derive
-    processor=LinearProcessor(args.work_dir,
-                              prov_ignore=DEFAULT_PROV_IGNORE + [
-                                  '/workflow/.*'],
-                              clean_work_dir_between_runs=False),
[…]

### 2019-03-14 manuscript/manuscript.tex
Changed references to dMRI to DWI

@@
 implementation of analysis suites for T1, T2* and diffusion weighted MRI
-(dMRI) data and the application of dMRI tractogram \citep{tournier_mrtrix:_2012} and
+(DWI) data and the application of DWI tractogram \citep{tournier_mrtrix:_2012} and
 vein masks \citep{ward_vein_2017} workflows to data collected from a
@@
 sub-study (e.g. brain extracted T1-weighted anatomical) to be referenced
-by workflows of other sub-studies (e.g. anatomically constrained dMRI
+by workflows of other sub-studies (e.g. anatomically constrained DWI
 tractography).
@@
 FA and ADC, as well as whole-brain tractography using streamlines tracking from the MRtrix
-toolbox \citep{tournier_improved_2010,tournier_mrtrix:_2012} (Figure \ref{fig:dmri_study}).
+toolbox \citep{tournier_improved_2010,tournier_mrtrix:_2012} (Figure \ref{fig:dwi_study}).
 
@@
 	\centering
-    \includegraphics[width=0.55\textwidth]{../figures/dmri_study}
+    \includegraphics[width=0.55\textwidth]{../figures/dwi_study}
   \caption{Example diffusion-weighted MRI (DWI) study, which can derive
@@
 inputs to pipelines, respectively. Orange arrows: outputs of pipelines.
-The dMRI magnitude image is preprocessed for motion correction and EPI
+The DWI magnitude image is preprocessed for motion correction and EPI
 distortions masked and bias corrected. From the bias corrected image two
@@
 derivatives: FA and ADC and/or streamlines fibre tracking.}
-\label{fig:dmri_study}
+\label{fig:dwi_study}
 \end{figure*}
@@
 the rest of the brain.
-Figure \ref{fig:tractography} displays the global tractography derived from the dMRI
+Figure \ref{fig:tractography} displays the global tractography derived from the DWI
 acquisition. The streamlines follow well known white matter tracts such
@@
 derivatives derived for the FA and ADC analysis, including the
-preprocessed and bias-corrected dMRI image and a whole brain mask, were
+preprocessed and bias-corrected DWI image and a whole brain mask, were
 reused in the generation of the streamlines.
@@
 of successively specialised Study sub-classes (e.g.
-MRI\textgreater{}EPI\textgreater{}dMRI) to enable generic processing
+MRI\textgreater{}EPI\textgreater{}DWI) to enable generic processing
 steps (e.g. registration) to be shared between classes. While not
@@
 shared intermediate derivatives between analyses, such as the
-preprocessed dMRI shared between tensor and fibre tracking workflows
+preprocessed DWI shared between tensor and fibre tracking workflows
 (Figure \ref{fig:fa_adc} and \ref{fig:tractography}), processing time as

### 2019-03-14 manuscript/manuscript.tex
finished updating paper for latest syntax changes

@@
 and methods that construct pipelines to derive the derivatives, are
-linked together by the \emph{data specification} \emph{table} of the
-Study class (Figure \ref{fig:example_study}). Likewise, free parameters used in pipeline
-construction are defined in the class' \emph{parameter specification}
-\emph{table}. Class inheritance can be used to specialise analysis
-suites by overriding entries in the specification tables or pipeline
-constructor methods. Analysis suites for multi-modal data can be
-implemented by combining Study classes within \emph{MultiStudy}
-classes\emph{.}
+linked together by the \emph{data specification} \emph{table} class
+attribute of the Study (Figure \ref{fig:example_study}). Likewise,
+free parameters used in pipeline construction are defined in the class'
+\emph{parameter specification} \emph{table}. Class inheritance can
+be used to specialise analysis suites by overriding entries in the
+specification tables or pipeline constructor methods. Analysis suites
+for multi-modal data can be implemented by combining Study classes
+within \emph{MultiStudy} classes\emph{.}
 
@@
 At initialisation, a Study object is passed references to a \emph{Repository},
-a \emph{Processor}, and an \emph{Environment}, which
+a \emph{Processor}, and an \emph{Environment} objects, which
 define where and how data is stored and processed. When a derivative is
@@
 
-At the heart of each Study class is the data specification table, which
+At the heart of each Study class is the data-specification-table attribute, which
 specifies both the input and output data of the analysis, and all the
@@
 (e.g. a multi-volume DICOM dataset). Fields
-represent integer, floating point or character string
+represent integer, floating point, datetime, or character string
 values. By default, a Field represents a single value but if the \emph{array}
-flag is set a Field represents a list of values.
+flag is set, a Field represents a list of values.
 Each Fileset references a \emph{FileFormat} object, which
@@
 
-For fileset specifications that correspond to a known type in the BIDS
-standard, a \emph{BidsInput} or \emph{BidsAssocInput} can be
-provided to the \emph{bids} keyword arg of the spec. BidsInput
-specifies a primary scan in the BIDS standard using its type, modality
-and optional run number. BidsAssocInput is used to select
-associated files, such as field maps and diffusion encoding matrices.
-When passing a BidsInput to a FilesetSpec the \emph{run} keyword
-argument of the selector is typically not set, so it can be read from
-the \emph{bids\_run} attribute of the Study. This allows the Study class
-to be applicable to any BIDS run.
+For Study classes that correspond to a known type in the BIDS
+standard, a dictionary mapping their data specifications to default
+\emph{BidsInput} or \emph{BidsAssocInput} selectors can be specified in the
+\emph{default\_bids\_inputs} class attribute. BidsInput
+specifies a primary scan in the BIDS standard using its \emph{type}, \emph{modality},
+\emph{format} and optionally the \emph{task} it belongs to. BidsAssocInput is used to select
+associated files, such as field maps and diffusion encoding matrices in reference
+to a primary scan. Default Bids selectors are typically not provided with
+a value for the \emph{task} keyword, which can be set at instantiation of
+the Study class with the \emph{bids\_task} keyword argument to enable the design of Study
+classes that are applicable to any BIDS task.
 
@@
 sub-study namespace to the namespace of the MultiStudy class, i.e.
-the dictionary keys are in the sub-study namespace and the dictionary
-values are in the global namespace.
+the dictionary keys refer to entries in the sub-study specification table and
+the dictionary values refer to entries in the multi-study specification table.
 
@@
 (Figure \ref{fig:simple_uml}). There are currently three supported repository types, XNAT
-\citep{marcus_extensible_2007}, BIDS \citep{gorgolewski_brain_2016} and a simple
-``directory'' format, which are encapsulated by \emph{XnatRepo},
+\citep{marcus_extensible_2007}, BIDS \citep{gorgolewski_brain_2016} and a
+``basic'' format, which are encapsulated by \emph{XnatRepo},
 \emph{BidsRepo}, and \emph{BasicRepo} classes
@@
 
-In its most basic form, a directory repository is just a file system
-directory with separate subdirectories for each subject in the study,
-with subject IDs taken from the subdirectory names. If the study has
-more than one visit then nested subdirectories for each visit are
-required in the subject subdirectories. Note that the directory
+In its most basic form, a ``basic'' repository, is just a file system
+directory containing the data to be processed for a single subject.
+For multi-subject studies, the root directory should contain separate
+subdirectories for each subject in the study, with subject IDs taken
+from the subdirectory names. If data was acquired for each subject
+over multiple visits, than an additional layer of nested subdirectories
+is included in the subject subdirectories, with the visit IDs taken from
+the subdirectory names. Note that the directory
 repository is similar to the BIDS format, however, there are no naming
@@
 \emph{per\_study} frequencies\emph{)} are stored in specially named
-subjects and visits (e.g. `all'), the names for which are specified when
+subjects and visits (e.g. `group'), the names for which are specified when
 the repository is initialised. For example, given in plain-directory
@@
 per\_subject data for `subj1' would be stored at
-\emph{\textless{}root\textgreater{}/subj1/}all, per\_visit data for
-`visit1' in \emph{\textless{}root\textgreater{}/}all\emph{/visit1},
-and per\_study data in \emph{\textless{}root\textgreater{}/}all/all
+\emph{\textless{}root\textgreater{}/subj1/}group, per\_visit data for
+`visit1' in \emph{\textless{}root\textgreater{}/}group\emph{/visit1},
+and per\_study data in \\ \emph{\textless{}root\textgreater{}/}group/group
 (Table \ref{tbl:repo-structure}).
@@
 subject/visit/study depending on the frequency of the corresponding data
-spec). Collection objects can be used to pass reference atlases and
-templates as inputs to analyses. They can also be set as the ``default
-input'' for a data specification via the \emph{default} keyword
+specifcation). Collection objects can be used to pass reference atlases and
+templates as inputs to analyses. They can also be set as the default
+for a data specification via the \emph{default} keyword
 argument. However, for the sake of portability, default inputs should be
@@
 
-For subsequent analyses, changes w.r.t. Any of the stored values, with
+For subsequent analyses, changes with respect to any of the stored values, with
 the exception of subject and visit IDs, will be flagged as a mismatch.
@@
 \emph{ModulesEnv} objects can be used if environment
-modules \citep{furlani_modules:_1991} are installed on the system (typical in many
+modules \citep{furlani_modules:_1991} are installed on the system (typical on many
 HPC systems). In this case, environment modules are loaded before a workflow node is run,
@@
 Study classes for T1, T2* and diffusion weighted MRI data have been
-implemented as part of the \emph{Biomedical imAgiNg ANAlysis (Banana)} package
+implemented as part of the \emph{Biomedical imging ANAlysis iN Arcana (Banana)} package
 (\url{github.com/MonashBI/banana}; \url{pypi.org./project/banana}).

### 2019-03-15 manuscript/manuscript.tex
touched up a sentence

@@
 
-At the heart of each Study class is the data-specification-table attribute, which
+At the heart of each Study class is the data specification table, which
 specifies both the input and output data of the analysis, and all the

### 2019-03-15 manuscript/manuscript.tex
tidied up methods reworkings

@@
 At the heart of each Study class is the data specification table, which
-specifies both the input and output data of the analysis, and all the
+is stored in the \emph{\_data\_specs} class attribute and specifies the
+input and output data of the analysis, and all
 stages in between. There is a one-to-one relationship between entries in
-the data specification table and data that is stored in the repository
-or will be stored if and when it is derived. Which intermediate
+the data specification table and data that are stored in the repository,
+or will be stored if and when they are derived. Which intermediate
 derivatives to include in the data specification table, and therefore
@@
 \emph{format} and optionally the \emph{task} it belongs to. BidsAssocInput is used to select
-associated files, such as field maps and diffusion encoding matrices in reference
-to a primary scan. Default Bids selectors are typically not provided with
+associated files, such as field maps and diffusion encoding matrices relative
+to a primary scan. Default BIDS selectors are typically not provided with
 a value for the \emph{task} keyword, which can be set at instantiation of
@@
 
-The syntax for pipeline construction is inspired by a proposed form for Nipype v2.0
+The syntax for pipeline construction is inspired by changes proposed for Nipype v2.0
 (\url{github.com/nipy/nipype/issues/2539}).
@@
 consist of a reference to the upstream node and the name of a trait in the
-upstream node's output interface (output connections are implied by input connections to other nodes).
+upstream node's output interface (output connections to other nodes are implied by input connections of other nodes).
 
@@
 of the corresponding study input or data specification, then a conversion node is implicitly connected
-to the pipeline by the framework to perform the required conversion. Pipeline inputs and outputs of
+to the pipeline by the framework to perform the required conversion. Pipeline inputs and outputs
 that are conditional on parameters or inputs provided to the study can be specified outside of the
@@
 Instead of being set directly, the data and parameter specifications are set
-by the metaclass of the Study (i.e. StudyMetaClass),
+by the metaclass of the Study (i.e. StudyMetaClass)
 in order to combine them with corresponding specifications in the class' bases. The combined
@@
 is included in the subject subdirectories, with the visit IDs taken from
-the subdirectory names. Note that the directory
+the subdirectory names. Note that the basic
 repository is similar to the BIDS format, however, there are no naming
-conventions in the directory repository, which enables prototyping and
+conventions in the basic repository, which enables prototyping and
 testing of analyses on loosely structured data.
@@
 Derivatives are stored by their specification name in a study-specific
-namespaces to avoid clashes with separate analyses. In directory
+namespaces to avoid clashes with separate analyses. In basic
 repositories this namespace is a subdirectory named after the study
-nested within each visit subdirectory if present or subject subdirectory
-otherwise. In BIDS repositories, the namespace is a subdirectory of the
+nested within the lowest layer of the data tree. In BIDS repositories, the namespace is a subdirectory of the
 \emph{derivatives} directory, again named after the study. In XNAT
@@
 BidsAssocInput objects can be provided to override the default
-selections is required.
+selections if required.
 
@@
 \emph{SlurmProc}, which wrap the LinearPlugin, MultiProcPlugin and SlurmPlugin
-Nipype execution plugins. The main task performed
+Nipype execution plugins, respectively. The main task performed
 by the processor, as separate from the Nipype execution plugin it wraps,
@@
 Provenance is stored for each pipeline run alongside the generated
-derivatives and consists of: parameter values used by the pipeline,
+derivatives and consists of parameter values used by the pipeline,
 software versions used by the pipeline, a graph representation of the
@@
 For subsequent analyses, changes with respect to any of the stored values, with
-the exception of subject and visit IDs, will be flagged as a mismatch.
+the exception of subject and visit IDs, will be flagged as a mismatch by default.
+However, changes can be ignored by providing the path to the attribute to ignore
+to the \emph{prov\_ignore} keyword argument at initialisation of the Processor.
 Subject or visit IDs only flag a mismatch if any of the inputs, or
-inputs of upstream pipelines, are per-visit or per-subject,
-respectively, or per-study. How provenance mismatches are handled by the
+inputs of upstream pipelines, are of per-visit or per-subject frequency,
+respectively, or per-study frequency. How provenance mismatches are handled by the
 study is determined by the \emph{reprocess} flag, which is passed to the
@@
 \end{table}
-
-Additionally, a time limit can be passed to the
-\emph{reprocess\_time\_limit}, and if the estimated time to reprocess
-all the required sessions is less than the time limit they will be
-reprocessed and otherwise an exception will be raised.
 

### 2019-03-15 manuscript/manuscript.tex
updated reprocessing handling to match API

@@
 derivatives and consists of parameter values used by the pipeline,
-software versions used by the pipeline, a graph representation of the
-underlying Nipype workflow, checksums of inputs, version of Arcana used,
-version of Nipype used, subject and visit IDs used by study.
-
-For subsequent analyses, changes with respect to any of the stored values, with
-the exception of subject and visit IDs, will be flagged as a mismatch by default.
-However, changes can be ignored by providing the path to the attribute to ignore
-to the \emph{prov\_ignore} keyword argument at initialisation of the Processor.
-Subject or visit IDs only flag a mismatch if any of the inputs, or
-inputs of upstream pipelines, are of per-visit or per-subject frequency,
-respectively, or per-study frequency. How provenance mismatches are handled by the
-study is determined by the \emph{reprocess} flag, which is passed to the
-Study on initialisation (Table \ref{tbl:reprocess-flag}).
-
-\begin{table}
-\caption{Effect of the \emph{reprocess} flag value on the
-behaviour of the study when existing derivatives are found that were
-derived with mismatching inputs and parameters.}
-\label{tbl:reprocess-flag} 
-\begin{tabular}{ll}
-\hline\noalign{\smallskip}
-\textbf{Reprocess value} & \textbf{Behaviour on provenance mismatch} \\
-\noalign{\smallskip}\hline\noalign{\smallskip}
-False (default) & Raises an exception \\
-True & Mismatching derivatives will be reprocessed \\
-`ignore' & Mismatches are ignored \\
-`ignore\_versions' & Ignore versions, otherwise raise exception \\
-`ignore\_versions\_true' & Ignore versions, otherwise the derivative will be reprocessed \\
-\noalign{\smallskip}\hline
-\end{tabular}
-\end{table}
+software versions used by the pipeline, interface parameters,
+a graph representation of the underlying Nipype workflow, checksums of inputs,
+version of Arcana used, version of Nipype used, and any subject and visit IDs
+that were joined over in the workflow.
+
+For subsequent analyses, changes with respect to any of the stored provenance values will
+be flagged as a mismatch, with the exception of interface package versions
+(e.g. Nipype or Banana versions). How mismatches are handled depends on the \emph{reprocess} flag passed to the
+Processor. If \emph{reprocess} is true then the sessions with mismatching provenance
+will be reprocessed, otherwise if \emph{reprocess} is false (the default) an exception will be raised.
+Changes with respect to any element in the provenance JSON document can be ignored by providing
+a list of JSONPath queries to the \emph{prov\_ignore} keyword argument.
 

### 2019-03-15 manuscript/manuscript.tex
rewording paragraphs on reviewers advice

@@
 
-Fileset and field specifications are passed to the data specification of
-a Study class via the \emph{add\_data\_specs} class attribute as a list
-of named \emph{FilesetSpec} and \emph{FieldSpec} objects (Figure \ref{fig:data_spec}).
-Specifications for acquired data (i.e. input data to the study) are
-distinguished from derived data by using the \emph{FilesetInputSpec}
-and \emph{FieldInputSpec} subtypes. However, the distinction is
-fluid, with derived specifications able to be overridden by acquired
-specifications in subclasses or MultiStudy classes, and vice-versa, or
-passed inputs when the class is instantiated.
+Fileset and field specifications of a Study class are defined by the
+list of \emph{FilesetSpec} and \emph{FieldSpec} objects in the
+\emph{add\_data\_specs} class attribute (Figure \ref{fig:data_spec}),
+The specifications are collated with any data specifications in base
+classes into the \emph{\_data\_specs} class attribute during the creation
+of the class by the StudyMetaClass metaclass.
+Specifications for input data to the study are
+distinguished from derivative specifications by the \emph{FilesetInputSpec}
+and \emph{FieldInputSpec} subtypes. However, the distinction between
+input and derived data is somewhat blurred, as derivative specifications can be
+passed input data when the class is instantiated. In addition,
+when subclassing a Study class, or combining it in a MultiStudy class,
+derivative specifications can be overridden by input
+specifications, and vice-versa.
 
@@
 Pipelines are constructed dynamically by ``pipeline constructor" methods
-of the study. Pipeline constructor methods are referenced by name in the \emph{pipeline\_name}
-argument of the FilesetSpec and FieldSpec objects of data specifications
-they derive. Pipeline constructor methods should only receive wildcard keyword
-arguments (e.g. \lstinline{my_pipeline(self, **name_maps)}), and these arguments
-should be passed as a dictionary directly to the \emph{name\_maps} argument
+of the study. Pipeline constructor methods are referenced by name in the
+data specifications they derive. Pipeline constructor methods should only
+receive wildcard keyword arguments (e.g. \lstinline{my_pipeline(self, **name_maps)}),
+and these arguments should be passed as a dictionary directly to the \emph{name\_maps} argument
 of the pipeline initialisation to enable inputs and outputs of the
@@
 inputs, values of the \emph{inputs} dictionary consist of a name of an entry in the data specification table
-and the format the input is expected in (i.e. a FileFormat for Fileset specifications or Python datatype for Field specifications).
+and the format the input data is expected in (i.e. a FileFormat for Fileset specifications or Python datatype for Field specifications).
 For pipeline outputs, values of the \emph{outputs} dictionary consist of a trait name in the node's output interface and the format the
@@
 consist of a reference to the upstream node and the name of a trait in the
-upstream node's output interface (output connections to other nodes are implied by input connections of other nodes).
+upstream node's output interface (output connections to other nodes are implied by input connections of the receiving nodes).
 

### 2019-03-15 manuscript/manuscript.tex
made minor clarification changes suggested by reviewer

@@
 classes (sub-studies) in a \emph{MultiStudy} class. Analysis suites are
-integrated by joining the data specification tables of the sub-studies
-of a MultiStudy class. Entries in specification tables of sub-studies
-are joined by mapping them to a common entry in the specification table
+integrated in a MultiStudy class by linking the data specification tables
+of sub-studies. Sub-study specification table entries are linked by mapping
+them to a common entry in the specification table class attribute
 of the MultiStudy (Figure \ref{fig:example_multi_study}). This enables derivatives from one

### 2019-03-15 manuscript/manuscript.tex
minor rewording

@@
 thereby enables researchers to quickly prototype analysis suites on
-local workstations that can be deployed on enterprise-scale
+local workstations that can be deployed on large-scale
 infrastructure without modification.
@@
 
-A level of proficiency in Python OO design is required to design new
+A level of proficiency in Python OO design is required to implement new
 analyses in Arcana, which may preclude inexperienced programmers.

### 2019-03-18 manuscript/manuscript.tex
changed reference to specification tables to just specifications

@@
 and methods that construct pipelines to derive the derivatives, are
-linked together by the \emph{data specification} \emph{table} class
-attribute of the Study (Figure \ref{fig:example_study}). Likewise,
+linked together by the \emph{data specification} class attribute of the
+Study (Figure \ref{fig:example_study}). Likewise,
 free parameters used in pipeline construction are defined in the class'
-\emph{parameter specification} \emph{table}. Class inheritance can
+\emph{parameter specification} class attribute. Class inheritance can
 be used to specialise analysis suites by overriding entries in the
-specification tables or pipeline constructor methods. Analysis suites
+specifications or pipeline constructor methods. Analysis suites
 for multi-modal data can be implemented by combining Study classes
@@
 specific dataset by instantiating an object of the class and
-requesting a derivative listed in the class' data specification table.
+requesting a derivative listed in the class' data specification.
 At initialisation, a Study object is passed references to a \emph{Repository},
@@
 the requested derivative. The manner in which the workflows are executed
-(i.e. single/multi-process or via SLURM scheduler) is specified by the
-Processor and software modules required by the analysis are
+(i.e. single/multi-process or via a SLURM scheduler \citep{yoo_slurm:_2003})
+is specified by the Processor and software modules required by the analysis are
 loaded by the Environment. Selected workflow products are
@@
  object at initialisation and matched against entries in the class' data
-specification table.
+specification.
 
@@
 
-\subsubsection*{Data and parameter specification
-tables}
-\label{sec:data-and-parameter-specification-tables}
-
-At the heart of each Study class is the data specification table, which
-is stored in the \emph{\_data\_specs} class attribute and specifies the
-input and output data of the analysis, and all
+\subsubsection*{Data and parameter specifications}
+\label{sec:data-and-parameter-specifications}
+
+At the heart of each Study class is the data specification attribute, which
+specifies the input and output data of the analysis, and all
 stages in between. There is a one-to-one relationship between entries in
-the data specification table and data that are stored in the repository,
+the data specification and derivatives that are stored in the repository,
 or will be stored if and when they are derived. Which intermediate
-derivatives to include in the data specification table, and therefore
+derivatives to include in the data specification, and therefore
 store in the repository, is left to the discretion of the researcher
@@
 require manual QC or are likely to be reused between different branches
-of analysis should be included in the table.
-
-Data specified in the data specification table can be of either a
-\emph{fileset} or \emph{field} type. Filesets represent single files,
+of analysis should be included in the data specification.
+
+Entries in the data specification can be of either a
+\emph{file set} or \emph{field} type. File sets represent single files,
 or sets of related files typically contained within a directory
 (e.g. a multi-volume DICOM dataset). Fields
-represent integer, floating point, datetime, or character string
-values. By default, a Field represents a single value but if the \emph{array}
-flag is set, a Field represents a list of values.
-Each Fileset references a \emph{FileFormat} object, which
+represent integer, floating point, date-time, or character string
+values. By default, a field represents a single value but if the \emph{array}
+flag is set, a field represents a list of values.
+Each file set references a \emph{FileFormat} object, which
 specifies the formats of the files in the set. File formats are
@@
 
-Fileset and field specifications of a Study class are defined by the
+The data specification of a Study class are defined by providing a
 list of \emph{FilesetSpec} and \emph{FieldSpec} objects in the
-\emph{add\_data\_specs} class attribute (Figure \ref{fig:data_spec}),
-The specifications are collated with any data specifications in base
-classes into the \emph{\_data\_specs} class attribute during the creation
-of the class by the StudyMetaClass metaclass.
-Specifications for input data to the study are
-distinguished from derivative specifications by the \emph{FilesetInputSpec}
+\emph{add\_data\_specs} class attribute (Figure \ref{fig:data_spec}).
+The lists are collated with data specifications in any base Study
+classes during the creation of the class. Input data to the study are
+distinguished from derivatives by using the \emph{FilesetInputSpec}
 and \emph{FieldInputSpec} subtypes. However, the distinction between
@@
 to a primary scan. Default BIDS selectors are typically not provided with
-a value for the \emph{task} keyword, which can be set at instantiation of
-the Study class with the \emph{bids\_task} keyword argument to enable the design of Study
-classes that are applicable to any BIDS task.
+a value for the \emph{task} keyword since the task can be set at instantiation of
+the Study class with the \emph{bids\_task} keyword argument, which enables the design of Study
+classes that are not restricted to a single task by default.
 
@@
 tool). Pipelines source their inputs from, and sink their outputs to, entries
-in the data specification table, thereby linking the table together.
+in the data specification, thereby linking the specification together.
 
@@
 Within a pipeline constructor method, a Pipeline object is constructed by the \emph{Study.pipeline} method
-(Figure \ref{fig:pipeline_constructor}). At initialisation, each pipeline is given a name,
-which must be unique amongst the pipelines constructed by the Study. The methods implemented
-by the pipeline can be characterised by providing a the list of citations
+(Figure \ref{fig:pipeline_constructor}). At initialisation, each pipeline is assigned a name,
+which must be unique amongst the pipelines constructed by the Study given the any combination of
+switches. The methods implemented by the pipeline can be characterised by providing a the list of citations
 and a text description to the \emph{citations} and \emph{desc} keyword arguments, respectively.
@@
 trait names in the node's input interface, whereas the keys of the \emph{outputs} dictionary correspond to
-names of entries in the data specification table. The values of both dictionaries are 2-tuples. For pipeline
-inputs, values of the \emph{inputs} dictionary consist of a name of an entry in the data specification table
-and the format the input data is expected in (i.e. a FileFormat for Fileset specifications or Python datatype for Field specifications).
+names of entries in the data specification. The values of both dictionaries are 2-tuples. For pipeline
+inputs, values of the \emph{inputs} dictionary consist of a name of an entry in the data specification
+and the format the input data is expected in (i.e. a FileFormat for Fileset specifications or core Python type for Field specifications).
 For pipeline outputs, values of the \emph{outputs} dictionary consist of a trait name in the node's output interface and the format the
@@
 consist of a reference to the upstream node and the name of a trait in the
-upstream node's output interface (output connections to other nodes are implied by input connections of the receiving nodes).
+upstream node's output interface (output connections to other nodes are implied by input connections to the receiving nodes).
 
@@
 by the metaclass of the Study (i.e. StudyMetaClass)
-in order to combine them with corresponding specifications in the class' bases. The combined
-data and parameter specifications are constructed by visiting the class'
+in order to combine them with corresponding specifications in base classes.
+The combined data and parameter specifications are constructed by visiting the class'
 bases in reverse method resolution order (MRO) and adding specifications
@@
 specification in the superclass method can be mapped onto different
-entries in the table of the subclass by providing the \emph{input\_map} and
+entries in the specification of the subclass by providing the \emph{input\_map} and
 \emph{output\_map} keyword arguments when calling the superclass method.
@@
 classes (sub-studies) in a \emph{MultiStudy} class. Analysis suites are
-integrated in a MultiStudy class by linking the data specification tables
-of sub-studies. Sub-study specification table entries are linked by mapping
-them to a common entry in the specification table class attribute
-of the MultiStudy (Figure \ref{fig:example_multi_study}). This enables derivatives from one
+integrated in a MultiStudy class by linking the data specifications
+of sub-studies. Sub-study specification entries are linked by mapping
+them to a common entry in the specification of the MultiStudy class
+(Figure \ref{fig:example_multi_study}). This enables derivatives from one
 sub-study (e.g. brain extracted T1-weighted anatomical) to be referenced
@@
 
-Sub-studies are aggregated in the \emph{sub-study} \emph{specification
-table} of a MultiStudy class via a list of \emph{SubStudySpec} objects
+Sub-studies are aggregated in the \emph{sub-study} \emph{specification}
+of a MultiStudy class via a list of \emph{SubStudySpec} objects
 in the \emph{add\_sub\_study\_specs} class attribute in the manner of
@@
 sub-study namespace to the namespace of the MultiStudy class, i.e.
-the dictionary keys refer to entries in the sub-study specification table and
-the dictionary values refer to entries in the multi-study specification table.
-
-Entries in the specification tables of sub-study classes that are not
+the dictionary keys refer to entries in the sub-study specification and
+the dictionary values refer to entries in the multi-study specification.
+
+Entries in the specifications of sub-study classes that are not
 referenced in the sub study's name map are implicitly mapped to the
@@
 \emph{Input} objects to select input data from the repository and match
-it with the Study's data specification table.
+it with the Study's data specification.
 (Figure \ref{fig:study_application}).
@@
 conventions can be used for input datasets and fields. A selection
-stage matches input data to entries in the data specification table of
+stage matches input data to entries in the data specification of
 the Study class. The criteria for these selections are passed to the
@@
 objects. Collection objects reference an entry in the data specification
-table and contain a single Fileset or Field for every session (or
+and contain a single Fileset or Field for every session (or
 subject/visit/study depending on the frequency of the corresponding data

### 2019-03-18 code/arcana_paper.py

@@ -14,7 +14,7 @@ class ArcanaPaper(MultiStudy, ImageDisplayMixin,
     T1-weighted, T2*-weighted and diffusion MRI data.
     """
 
-    add_sub_study_specs = [
+    add_substudy_specs = [
         # Sub-study to process the T1-weighted data
         SubStudySpec(
             't1',

### 2019-03-18 manuscript/manuscript.tex
touched up methods and started writing FAIR paragraph in discussion

@@
 All MultiStudy classes must inherit from the Multi\emph{Study} base
-class and be created by the Multi\emph{StudyMetaClass} metaclass or
+class and be created by the \emph{MultiStudyMetaClass} metaclass or
 subclasses thereof. As in the case of subclassing the standard Study
@@
 of a MultiStudy class via a list of \emph{SubStudySpec} objects
-in the \emph{add\_sub\_study\_specs} class attribute in the manner of
+in the \emph{add\_substudy\_specs} class attribute in the manner of
 data and parameter specifications. A SubStudySpec consists of a name, a
@@
 constructor method is also mapped into the MultiStudy namespace with a prefix.
-For example, \emph{derived1} in \emph{sub\_study2} would be mapped to
-\emph{sub\_study2\_derived1} along with the method
-\emph{sub\_study2\_pipeline1}.
+For example, \emph{derived1} in \emph{substudy2} would be mapped to
+\emph{substudy2\_derived1} along with the method
+\emph{substudy2\_pipeline1}.
 
@@
 dataset, an instance of the Study class is created with details of where
-the data is stored (\emph{Repository} module) the computing
+the data is stored (\emph{Repository} module and \emph{Input} selectors) the computing
 resources available to process it (\emph{Processor} module) and the software
@@
 along with the range of subject and visit IDs to be included in the analysis
-(if they are not provided then all IDs found in the repository are included).
-The remaining arguments passed to the Study object initialisation are the
-Repository, Processor and Environment modules to use and a list of
-\emph{Input} objects to select input data from the repository and match
-it with the Study's data specification.
-(Figure \ref{fig:study_application}).
+If subject and visit IDs are not explicitly provided then all IDs found in the repository are included.
+The remaining arguments passed to the Study object at initialisation are the
+Repository, Processor and Environment modules and a list of
+\emph{Input} objects to match data in the repository with inputs in the
+data specification (Figure \ref{fig:study_application}).
 
@@
 is included in the subject subdirectories, with the visit IDs taken from
-the subdirectory names. Note that the basic
-repository is similar to the BIDS format, however, there are no naming
+the subdirectory names. The basic
+repository is similar to the BIDS format in this form, however, there are no naming
 conventions in the basic repository, which enables prototyping and
@@
 Derivatives are stored by their specification name in a study-specific
-namespaces to avoid clashes with separate analyses. In basic
+namespaces to avoid clashes between separate analyses. In basic
 repositories this namespace is a subdirectory named after the study
@@
 Derived filesets are stored with the format specified in the study's
-data specification. In plain-directory and BIDS repositories, fields are
+data specification. In basic and BIDS repositories, fields are
 stored in a single JSON file named `\_\_fields\_\_.json' in each derived
-session, and on XNAT they are stored in custom fields of the derived
+session, and on XNAT they are stored in custom variables in the derived
 session. Provenance is stored in a `\_\_prov\_\_' sub-directory (dataset
 on XNAT) of the derivatives directory (MrSession on XNAT) in separate
-JSON files for each pipeline named after the pipeline (Table 1).
-
-Summary data (i.e. with \emph{per\_subject}, \emph{per\_visit}, and
+JSON files for each pipeline (Table 1).
+
+Data from group analyses (i.e. with \emph{per\_subject}, \emph{per\_visit}, and
 \emph{per\_study} frequencies\emph{)} are stored in specially named
 subjects and visits (e.g. `group'), the names for which are specified when
-the repository is initialised. For example, given in plain-directory
-repository using all as the summary name for both subjects and visits,
+the repository is initialised. For example, given a basic
+repository using `group' as the summary name for both subjects and visits,
 per\_subject data for `subj1' would be stored at
@@
 While derivatives generated by a Study object are named in accordance
-with the data specification of the Study class, arbitrary naming
-conventions can be used for input datasets and fields. A selection
-stage matches input data to entries in the data specification of
-the Study class. The criteria for these selections are passed to the
+with the data specification of the Study class, input file sets and fields
+do not need to be conventionally named when using basic or XNAT
+repositories. In these cases, a selection stage matches input data to
+entries in the data specification of the Study class. The criteria for
+these selections are passed to the
 the \emph{inputs} argument of the Study object at instantiation in a
 dictionary mapping data specification names to \emph{FilesetInput} and
-\emph{FieldInput} objects, and are required
+\emph{FieldInput} objects.
+
+FilesetInput and FieldInput objects are required
 to match exactly one fileset or field in every session included in the study.
-
 Matching is typically performed on file
@@
 
-If the data to select has been derived from an alternative Arcana Study
+If the data to select has been derived from an alternative Study
 instance, then the name of the alternative study can be passed to the
-\emph{from\_study} keyword argument provided to the selector. There are
+\emph{from\_study} keyword argument provided to the Input object. There are
 no restrictions on selecting any data, derived or otherwise, to match
 input or derived specifications. For example, it is possible to
-deliberately skip analysis steps by selecting an output of an early step
-in a previous run as a match for a later derived spec although this is
+deliberately skip analysis steps by selecting an upstream derivative
+from a previously run workflow as a match for a downstream derivative, although this is
 not recommended as standard practice.
 
-Specific files and fields that are not stored within a repository can be
-passed as inputs in \emph{FilesetCollection} and \emph{FieldCollection}
+Specific file sets and fields can be passed as inputs to a Study in
+\emph{FilesetCollection} and \emph{FieldCollection}
 objects. Collection objects reference an entry in the data specification
@@
 
-When using BIDS repositories, the selection stage is typically already
+When using BIDS repositories, the input selection stage is typically
 included in the data specification (see \emph{Data and parameter
@@
 Provenance is stored for each pipeline run alongside the generated
-derivatives and consists of parameter values used by the pipeline,
-software versions used by the pipeline, interface parameters,
-a graph representation of the underlying Nipype workflow, checksums of inputs,
-version of Arcana used, version of Nipype used, and any subject and visit IDs
-that were joined over in the workflow.
+derivatives and consists of interface parameter values,
+software versions of external requirements, Arcana and Nipype, 
+a graph representation of the underlying Nipype workflow, checksums of inputs
+and outputs, and any subject and visit IDs that were joined over in the workflow.
 
 For subsequent analyses, changes with respect to any of the stored provenance values will
-be flagged as a mismatch, with the exception of interface package versions
+be flagged as a mismatch by default, with the exception of interface package versions
 (e.g. Nipype or Banana versions). How mismatches are handled depends on the \emph{reprocess} flag passed to the
@@
 implemented as part of the \emph{Biomedical imging ANAlysis iN Arcana (Banana)} package
-(\url{github.com/MonashBI/banana}; \url{pypi.org./project/banana}).
+(\url{github.com/MonashBI/banana}; \url{pypi.org/project/banana}).
 All three classes, \emph{T1Study}, \emph{T2starStudy} and
@@
 
+The framework that Arcana provides should facilitate the development of workflows
+that are consistent with the F.A.I.R. guiding principles \citep{wilkinson_fair_2016}.
+\begin{itemize}
+\item Findable all in one code-base
+\item Accessible open source and implemented in different systems
+\item Interoperable with BIDS derivatives
+\item Interoperable with different analysis software
+\item Reusable in different contexts
+\item Reusable with detailed provenance
+\end{itemize}
+
 \section*{Conclusion}

### 2019-03-19 manuscript/manuscript.tex
writing FAIR paragraph

@@
 We present Arcana, a software framework to facilitate the development of
-comprehensive analysis suites for neuroimaging data that implement
+analysis suites for neuroimaging data that implement
 complete workflows from repository data to publication results. The
@@
 versioning, coupled with ability to submit jobs to HPC clusters, enables
-workflows implemented in Arcana to scale to large datasets. Arcana
-thereby enables researchers to quickly prototype analysis suites on
-local workstations that can be deployed on large-scale
-infrastructure without modification.
+workflows implemented in Arcana to scale to large datasets. Researchers
+are able to quickly prototype analyses that can be deployed on large-scale
+infrastructure on local workstations without modification.
 
@@
 such as data retrieval and storage, format conversions, and provenance,
-reducing the time and effort required to implement robust workflows from
-acquired data to publication results.
+reducing the time and effort required to implement robust workflows.
 
@@
 with the framework. In addition, class inheritance provides a manageable
-way to adapt and extend to existing analyses and highlights where
+way to adapt and extend existing analyses, and highlights where
 modified analyses differ from standard procedures.
@@
 necessary, it is recommended to create a subclass specific to the
-research study in question and aggregate all related analysis within it,
-since such classes can be applied to alternate datasets in order to
+research study in question and aggregate all related analysis within it.
+Since such classes can be applied to alternate datasets in order to
 reproduce the exact analysis. The \emph{ArcanaPaper} class
@@
 
-Arcana's management of intermediate derivatives and provenance
+The management of intermediate derivatives and provenance in Arcana
 guarantees that the same analysis is applied across the dataset without
@@
 (Figure \ref{fig:fa_adc} and \ref{fig:tractography}), processing time as
-well as time required for manual
-QC is minimised. Given analyses implemented in Arcana are also able to
-be processed on HPC clusters, they scale well to large studies.
-
-The framework that Arcana provides should facilitate the development of workflows
-that are consistent with the F.A.I.R. guiding principles \citep{wilkinson_fair_2016}.
-\begin{itemize}
-\item Findable all in one code-base
-\item Accessible open source and implemented in different systems
-\item Interoperable with BIDS derivatives
-\item Interoperable with different analysis software
-\item Reusable in different contexts
-\item Reusable with detailed provenance
-\end{itemize}
+well as time required for manual QC is minimised. Given analyses implemented
+in Arcana are also able to be processed on HPC clusters, they scale well to large studies.
+
+The framework provided by Arcana should facilitate the development of workflows
+that are consistent with F.A.I.R. guiding principles \citep{wilkinson_fair_2016},
+particularly with regards to interoperability and reusability.
+and their extensible, modular architecture should encourage code reuse. Every derivative created
+by arcana is accompanied with sufficient provenance information to
+fully reproduce the workflow. Analyses implemented in Arcana are interoperable between different
+repository and execution environments. In addition, the implementation of neuroimaging
+analyses in Banana is planned to closely follow the specification for BIDS
+derivatives \citep{gorgolewski_bids_nodate} to enable interoperability with other tool chains.
+Collaboration within a common code-base should help improve the visibility of
+workflow implementations.
+open source and includes text descriptions and citations of the relevant literature.
 

### 2019-03-20 manuscript/manuscript.tex
finished revising for resubmission

@@
 
-Study classes encapsulate a study dataset (i.e. data collected across
+Study classes encapsulate a study dataset (e.g. data collected across
 multiple subjects using the same acquisition protocol) with the suite of
@@
 
-At the heart of each Study class is the data specification attribute, which
+At the heart of each Study class is the data specification class attribute, which
 specifies the input and output data of the analysis, and all
@@
 Entries in the data specification can be of either a
-\emph{file set} or \emph{field} type. File sets represent single files,
+\emph{file-set} or \emph{field} type. File-sets represent single files,
 or sets of related files typically contained within a directory
 (e.g. a multi-volume DICOM dataset). Fields
-represent integer, floating point, date-time, or character string
-values. By default, a field represents a single value but if the \emph{array}
-flag is set, a field represents a list of values.
+represent integer, floating point, date-time, or unicode string
+values. By default, a field contains a single value but if the \emph{array}
+flag is set, a field can contain a list of values.
 Each file set references a \emph{FileFormat} object, which
@@
 and \emph{FieldInputSpec} subtypes. However, the distinction between
-input and derived data is somewhat blurred, as derivative specifications can be
+input and derived data is somewhat blurred, as derivative specification
+entries can be
 passed input data when the class is instantiated. In addition,
-when subclassing a Study class, or combining it in a MultiStudy class,
-derivative specifications can be overridden by input
-specifications, and vice-versa.
+when subclassing a Study class or combining it in a MultiStudy class,
+derivative specification entries can be overridden by input
+specification entries, and vice-versa.
 
@@
 
-All data specifications have a \emph{frequency} attribute which specifies
+All data specification entries have a \emph{frequency} attribute which specifies
 where the data sits in the hierarchy of the
@@
 'per\_subject, 'per\_visit' or 'per\_study'. In
-addition, derived specifications are passed the name of a method in the
+addition, derived specification entries are passed the name of a method in the
 class that constructs the pipeline to derive them. Therefore, while a
@@
 (\url{github.com/nipy/nipype/issues/2539}).
-Within a pipeline constructor method, a Pipeline object is constructed by the \emph{Study.pipeline} method
+Within a pipeline constructor method, a Pipeline object is constructed by the \emph{Study.new\_pipeline} method
 (Figure \ref{fig:pipeline_constructor}). At initialisation, each pipeline is assigned a name,
-which must be unique amongst the pipelines constructed by the Study given the any combination of
+which must be unique amongst the pipelines constructed by the Study given any combination of
 switches. The methods implemented by the pipeline can be characterised by providing a the list of citations
@@
 
-The \emph{add(name, interface)} method is used to add a node to a pipeline and takes
+The \emph{add(name, interface)} method is used to add a node to a pipeline. It takes
 a unique name for the node (within the pipeline) and a Nipype Interface object, and returns
-a reference to the newly added node. For clarity, is recommended to put all static inputs
+a reference to the newly added node. For clarity, it is recommended to put all static inputs
 (i.e. parameters) of the interface as keyword arguments of the interface constructor
 (Figure \ref{fig:pipeline_constructor}). However, if an input conditionally depends on a parameter of the
-study it can be set via the \emph{inputs} attribute of the node (e.g. \lstinline{my_node.inputs.my_param = 1.0}).
-
-Node interfaces are connected to each other, and to inputs and outputs of the pipeline, by
+study it can be set via the \emph{inputs} attribute of the returned Nipype node
+(e.g. \lstinline{my_node.inputs.my_param = 1.0}).
+
+Node inputs and ouputs are connected to each other, and to inputs and outputs of the pipeline, by
 providing \emph{inputs} and \emph{outputs} keyword arguments to the \emph{add} method. Both
 arguments take a dictionary. The keys of the \emph{inputs} dictionary correspond to
-trait names in the node's input interface, whereas the keys of the \emph{outputs} dictionary correspond to
-names of entries in the data specification. The values of both dictionaries are 2-tuples. For pipeline
-inputs, values of the \emph{inputs} dictionary consist of a name of an entry in the data specification
+trait names in the node's input specification, whereas the keys of the \emph{outputs} dictionary correspond to
+names of entries in the study data specification. The values of both dictionaries are 2-tuples. For pipeline
+inputs, values of the \emph{inputs} dictionary consist of a name of an entry in the study data specification
 and the format the input data is expected in (i.e. a FileFormat for Fileset specifications or core Python type for Field specifications).
-For pipeline outputs, values of the \emph{outputs} dictionary consist of a trait name in the node's output interface and the format the
+For pipeline outputs, values of the \emph{outputs} dictionary consist of a trait name in the node's output specification and the format the
 output data is generated in. For input connections from other nodes, values of the \emph{inputs} dictionary
 consist of a reference to the upstream node and the name of a trait in the
-upstream node's output interface (output connections to other nodes are implied by input connections to the receiving nodes).
+upstream node's output specification (output connections to other nodes are implied by input connections to the receiving nodes).
 
@@
 wall time for the node execution should be provided to the keyword arguments
-\emph{memory}, and \emph{wall\_time}.
+\emph{mem\_gb}, and \emph{wall\_time}.
 
@@
 parameter. The analysis branch designated by a switch value should be
-tested with \emph{Study.branch(name)} in the case of boolean switches and
-\emph{Study.branch(name, ref\_value)} in the case of string switches.
+tested with \emph{Study.branch(switch\_name)} in the case of boolean switches and
+\emph{Study.branch(switch\_name, branch\_name)} in the case of string switches.
 
@@
 parameterisations). Parameters are set on initialisation of the Study object
-along with the range of subject and visit IDs to be included in the analysis
-If subject and visit IDs are not explicitly provided then all IDs found in the repository are included.
+along with the range of subject and visit IDs to be included in the analysis.
+If subject and visit IDs are not explicitly provided, then all IDs found in the repository are included.
 The remaining arguments passed to the Study object at initialisation are the
@@
 
-Data from group analyses (i.e. with \emph{per\_subject}, \emph{per\_visit}, and
+Summary data (i.e. with \emph{per\_subject}, \emph{per\_visit}, and
 \emph{per\_study} frequencies\emph{)} are stored in specially named
@@
 with the data specification of the Study class, input file sets and fields
-do not need to be conventionally named when using basic or XNAT
+do not need specific names when using basic or XNAT
 repositories. In these cases, a selection stage matches input data to
@@
 no restrictions on selecting any data, derived or otherwise, to match
-input or derived specifications. For example, it is possible to
+a specification entry. For example, it is possible to
 deliberately skip analysis steps by selecting an upstream derivative
-from a previously run workflow as a match for a downstream derivative, although this is
-not recommended as standard practice.
+from a workflow that was run previously as a match for a downstream derivative,
+although this is not recommended as standard practice.
 
@@
 templates as inputs to analyses. They can also be set as the default
-for a data specification via the \emph{default} keyword
+for a data specification entry via the \emph{default} keyword
 argument. However, for the sake of portability, default inputs should be
@@
 initialisation of the Study. However, BidsInput and
-BidsAssocInput objects can be provided to override the default
+BidsAssocInput objects can be provided as inputs to override the default
 selections if required.
@@
 abstract base class, wrapping additional Nipype plugins as required is
-trivial.
+straightforward.
 
@@
 Provenance is stored for each pipeline run alongside the generated
-derivatives and consists of interface parameter values,
-software versions of external requirements, Arcana and Nipype, 
+derivatives and consists of the supplied node parameter values,
+software versions of external requirements, Arcana and Nipype used, 
 a graph representation of the underlying Nipype workflow, checksums of inputs
@@
 Changes with respect to any element in the provenance JSON document can be ignored by providing
-a list of JSONPath queries to the \emph{prov\_ignore} keyword argument.
+a list of JSONPath queries to the \emph{prov\_ignore} keyword argument of the Processor.
 
@@
 
-The software packages installed on the system that are required by a study's
+The software packages installed on the system that are required by a
 workflows (e.g. FSL, SPM) are detected and managed by
@@
 Python Package Index (PyPI) (\url{pypi.org/project/arcana/}).
-Study classes for T1, T2* and diffusion weighted MRI data have been
+Study classes for T1, T2* and diffusion-weighted MRI data have been
 implemented as part of the \emph{Biomedical imging ANAlysis iN Arcana (Banana)} package
@@
 The framework provided by Arcana should facilitate the development of workflows
-that are consistent with F.A.I.R. guiding principles \citep{wilkinson_fair_2016},
-particularly with regards to interoperability and reusability.
-and their extensible, modular architecture should encourage code reuse. Every derivative created
-by arcana is accompanied with sufficient provenance information to
-fully reproduce the workflow. Analyses implemented in Arcana are interoperable between different
-repository and execution environments. In addition, the implementation of neuroimaging
-analyses in Banana is planned to closely follow the specification for BIDS
-derivatives \citep{gorgolewski_bids_nodate} to enable interoperability with other tool chains.
-Collaboration within a common code-base should help improve the visibility of
-workflow implementations.
-open source and includes text descriptions and citations of the relevant literature.
+that are consistent with the F.A.I.R. guiding principles \citep{wilkinson_fair_2016}.
+Each pipeline is accompanied by a text description and
+a list of citations to describe the techniques it employs.
+The extensibility and modularity of workflows in Arcana should encourage
+their reuse, and enable communal development of code repositories.
+Arcana analyses are interoperable between different
+repository and execution environments. In addition, the development of
+Banana is planned to closely follow the specification for BIDS
+derivatives \citep{gorgolewski_bids_nodate} to enable interoperability with
+other BIDS apps.
 

### 2019-03-20 manuscript/manuscript.tex
final touch ups before sending to co-authors

@@
 flag is set, a field can contain a list of values.
-Each file set references a \emph{FileFormat} object, which
+Each file-set references a \emph{FileFormat} object, which
 specifies the formats of the files in the set. File formats are
@@
 \caption{Example data and parameter specifications. The data
-specification specifies two input file sets, `one' and `ten' and
-ten derived file sets that can be derived from them, at least
+specification specifies two input file-sets, `one' and `ten' and
+ten derived file-sets that can be derived from them, at least
 indirectly. Each derived data spec, specifies the name of the pipeline
@@
 While derivatives generated by a Study object are named in accordance
-with the data specification of the Study class, input file sets and fields
+with the data specification of the Study class, input file-sets and fields
 do not need specific names when using basic or XNAT
@@
 
-Specific file sets and fields can be passed as inputs to a Study in
+Specific file-sets and fields can be passed as inputs to a Study in
 \emph{FilesetCollection} and \emph{FieldCollection}
@@
 workflows implemented in Arcana to scale to large datasets. Researchers
-are able to quickly prototype analyses that can be deployed on large-scale
+are able to quickly prototype analyses that can be deployed to large-scale
 infrastructure on local workstations without modification.
@@
 Banana is planned to closely follow the specification for BIDS
-derivatives \citep{gorgolewski_bids_nodate} to enable interoperability with
+derivatives \citep{gorgolewski_bids_nodate} for interoperability with
 other BIDS apps.

### 2019-03-20 manuscript/manuscript.tex
touch ups to manuscript and added response to reviewer

@@
 % Insert the name of "your journal" with
-% \journalname{myjournal}
+\journalname{Neuroinformatics}
 
@@
 complex workflows that are portable and complete.
-
-% Provenanced mentioned here
 
@@
 input and derived data is somewhat blurred, as derivative specification
-entries can be
-passed input data when the class is instantiated. In addition,
-when subclassing a Study class or combining it in a MultiStudy class,
-derivative specification entries can be overridden by input
-specification entries, and vice-versa.
+entries can be passed input data when the class is instantiated. In addition,
+when subclassing a Study class or aggregating it in a MultiStudy class,
+derivative entries can be overridden by input entries, and vice-versa.
 
@@
 
-The framework provided by Arcana should facilitate the development of workflows
+The framework provided by Arcana should aid the development of workflows
 that are consistent with the F.A.I.R. guiding principles \citep{wilkinson_fair_2016}.

### 2019-03-24 manuscript/manuscript.tex
fixed typos in manuscript and response

@@
 
-Node inputs and ouputs are connected to each other, and to inputs and outputs of the pipeline, by
+Node inputs and outputs are connected to each other, and to inputs and outputs of the pipeline, by
 providing \emph{inputs} and \emph{outputs} keyword arguments to the \emph{add} method. Both

### 2019-03-25 manuscript/manuscript.tex
removed relative links to graphics and code listings
final submission

@@
     \centering
-    \includegraphics[width=0.55\textwidth]{../figures/example_study}
+    \includegraphics[width=0.55\textwidth]{example_study}
   \caption{Example study. Blue boxes represent input
@@
     \centering
-    \includegraphics[width=0.9\textwidth]{../figures/simplified_arcana_uml}
+    \includegraphics[width=0.9\textwidth]{simplified_arcana_uml}
   \caption{Unified Modelling Language (UML) diagram
@@
 \begin{figure}
-\lstinputlisting[basicstyle=\footnotesize,firstline=2, lastline=59]{../code/example_study.py}
+\lstinputlisting[language=Python,basicstyle=\footnotesize,firstline=2, lastline=59]{example_study.py.txt}
 \caption{Example data and parameter specifications. The data
@@
 \begin{figure}
-\lstinputlisting[firstline=61, basicstyle=\footnotesize]{../code/example_study.py}
+\lstinputlisting[language=Python, firstline=61, basicstyle=\footnotesize]{example_study.py.txt}
 \caption{Example pipeline constructor method. Pipelines are
@@
   \centering
-    \includegraphics[width=0.775\textwidth]{../figures/example_multi_study}
+    \includegraphics[width=0.775\textwidth]{example_multi_study}
   \caption{Example MultiStudy. Blue boxes represent input data
@@
 	\centering
-    \includegraphics[width=\textwidth]{../figures/full_arcana_uml}
+    \includegraphics[width=\textwidth]{full_arcana_uml}
   \caption{Detailed Unified Modelling Language (UML) diagram of
@@
 \begin{figure}
-\lstinputlisting[basicstyle=\footnotesize]{../code/example_application.py}
+\lstinputlisting[language=Python, basicstyle=\footnotesize]{example_application.py.txt}
 \caption{Example application of Study class to a dataset stored in an XNAT
@@
 	\centering
-    \includegraphics[width=0.55\textwidth]{../figures/dwi_study}
+    \includegraphics[width=0.55\textwidth]{dwi_study}
   \caption{Example diffusion-weighted MRI (DWI) study, which can derive
@@
 	\centering
-    \includegraphics[width=0.775\textwidth]{../figures/t2star_t1_study}
+    \includegraphics[width=0.775\textwidth]{t2star_t1_study}
   \caption{Combined T2*/T1-weighted studies within \emph{ArcanaPaper}
@@
     \centering
-    \includegraphics[width=\textwidth]{../figures/veins}
+    \includegraphics[width=\textwidth]{veins}
   \caption{Composite vein image (\emph{third row}) constructed by
@@
     \centering
-    \includegraphics[width=\textwidth]{../figures/fa_adc}
+    \includegraphics[width=\textwidth]{fa_adc}
   \caption{Fractional Anisotropy (FA) \emph{(top row)} and
@@
     \centering
-    \includegraphics[width=\textwidth]{../figures/tractography}
+    \includegraphics[width=\textwidth]{tractography}
   \caption{Global tractography performed using the MRtrix

### 2019-03-25 code/example_application.py

@@ -1,52 +1,0 @@
-#!/usr/bin/env python3
-import os.path as op
-from arcana import (
-    FilesetInput, FieldInput, XnatRepo, SlurmProc, ModulesEnv)
-from .example_study import ExampleStudy
-from banana.file_format import dicom_format
-from myproj.requirements import package1_req
-
-# Create study object that accesses an XNAT repository
-# and submits jobs to a SLURM scheduler
-study = ExampleStudy(
-    # Give a name to this analysis to
-    # differentiate it from other analyses
-    # performed on the same data
-    name='example',
-    # Set up connection to XNAT repository
-    repository=XnatRepo(
-        project_id='SAMPLE_PROJECT',
-        server='https://central.xnat.org',
-        cache_dir=op.expanduser('~/xnat-cache')),
-    # Specify the use the SLURM scheduler to submit
-    # nodes as jobs using Nipype's SlurmGraphPlugin
-    processor=SlurmProc(
-        work_dir=op.expanduser('~/work')),
-    # Specify the use of environment modules to
-    # satisfy software requirements. Non-standard
-    # package names explicitly mapped to approp. reqs.
-    environment=ModulesEnv(
-        packages_map={
-            package1_req: 'Package1_Parallel'}),
-    # Link files and fields in the repository
-    # to entries in the data specification
-    inputs={
-        'acquired1_file': FilesetInput(pattern='.*mprage.*',
-                                       dicom_format),
-        'acquired_file2': FilesetInput('SWI_Images',
-                                       dicom_format),
-        'acquired_field1': FieldInput('YOB', int,
-                                      frequency='per_subject'),
-        'acquired_field2': FieldInput('weight', float)},
-    # Specify parameters specific to this
-    # analysis
-    parameters={'parameter1': 55.0,
-                'pipeline_tool': 'toolB'})
-
-# Generate whole brain tracks and return path to
-# a cached dataset
-derived5 = study.data('whole_brain_tracks')
-print("The \"derived5\" fileset for the 'SECOND' visit "
-      "of subject 'PILOT1' was produced at:\n{}"
-      .format(derived5.path(subject_id='PILOT1',
-                            visit_id='SECOND')))

### 2019-03-25 code/example_study.py

@@ -1,114 +1,0 @@
-import os
-from arcana import (
-    Study, StudyMetaClass, FilesetInputSpec, FilesetSpec,
-    FieldInputSpec, FieldSpec, ParamSpec, SwitchSpec,
-    FilesetInput, XnatRepo)
-from banana.file_format import (
-    nifti_gz_format, dicom_format, nifti_format, analyze_format,
-    text_format, text_matrix_format)
-
-STD_IMAGE_FORMATS = (dicom_format, nifti_format, nifti_gz_format,
-                     analyze_format)
-
-# Select a Fileset collection to use as a default for template1
-template_repo = XnatRepo(
-    server='http://central.xnat.org', project_id='TEMPLATES',
-    cache=os.path.expanduser(os.path.join('~', 'xnat-cache')))
-template_selector = FilesetInput('MNI152_T1', nifti_gz_format,
-                                 frequency='per_study')
-template_collectn = template_selector.match(template_repo.tree())
-
-
-class ExampleStudy(Study, metaclass=StudyMetaClass):
-
-    add_data_specs = [
-        # Acquired file sets
-        FilesetInputSpec('acquired_file1', text_format),
-        FilesetInputSpec('acquired_file2', STD_IMAGE_FORMATS),
-        # Acquired fields
-        FieldInputSpec('acquired_field1', int, array=True,
-                       frequency='per_subject'),
-        FieldInputSpec('acquired_field2', float, optional=True),
-        # "Acquired" file set with default value. Useful for
-        # standard templates
-        FilesetInputSpec('template1', STD_IMAGE_FORMATS,
-                         frequency='per_study',
-                         default=template_collectn),
-        # Derived file sets
-        FilesetSpec('derived_file1', text_format, 'pipeline1'),
-        FilesetSpec('derived_file2', nifti_gz_format, 'pipeline1'),
-        FilesetSpec('derived_file3', text_matrix_format,
-                    'pipeline2'),
-        FilesetSpec('derived_file4', dicom_format, 'pipeline3'),
-        FilesetSpec('derived_file5', nifti_gz_format, 'pipeline3',
-                    frequency='per_subject'),
-        FilesetSpec('derived_file6', analyze_format, 'pipeline2',
-                    frequency='per_visit'),
-        # Derived fields
-        FieldSpec('derived_field1', float, 'pipeline2'),
-        FieldSpec('derived_field2', int, 'pipeline4',
-                  frequency='per_study')]
-
[…]

### 2019-05-13 manuscript/manuscript.tex
Updated FilesetInput to InputFileset

@@
 classes during the creation of the class. Input data to the study are
-distinguished from derivatives by using the \emph{FilesetInputSpec}
-and \emph{FieldInputSpec} subtypes. However, the distinction between
+distinguished from derivatives by using the \emph{InputFilesetSpec}
+and \emph{InputFieldSpec} subtypes. However, the distinction between
 input and derived data is somewhat blurred, as derivative specification
@@
 the \emph{inputs} argument of the Study object at instantiation in a
-dictionary mapping data specification names to \emph{FilesetInput} and
-\emph{FieldInput} objects.
-
-FilesetInput and FieldInput objects are required
+dictionary mapping data specification names to \emph{InputFileset} and
+\emph{InputField} objects.
+
+InputFileset and InputField objects are required
 to match exactly one fileset or field in every session included in the study.

### 2019-05-13 code/arcana_paper.py

@@ -1,7 +1,7 @@
 #!/usr/bin/env python3
 from arcana import (
     MultiStudy, MultiStudyMetaClass, SubStudySpec, ParamSpec)
-from banana.study import (
+from banana.study.mri import (
     DwiStudy, T1Study, T2Study, T2starStudy, MriStudy)
 from banana.plot import ImageDisplayMixin
 
@@ -31,8 +31,8 @@ class ArcanaPaper(MultiStudy, ImageDisplayMixin,
             't2star',
             T2starStudy,
             name_map={'coreg_ref_brain': 't1_brain',
-                      'coreg_to_atlas_mat': 't1_coreg_to_atlas_mat',
-                      'coreg_to_atlas_warp': 't1_coreg_to_atlas_warp'}),
+                      'coreg_to_template_mat': 't1_coreg_to_template_mat',
+                      'coreg_to_template_warp': 't1_coreg_to_template_warp'}),
         # Sub-study to process the dMRI data
         SubStudySpec(
             'dmri',
@@ -57,7 +57,7 @@ class ArcanaPaper(MultiStudy, ImageDisplayMixin,
 
     def vein_fig(self, save_path=None, **kwargs):
         """
-        Generates an image panel containing the SWI, QSM, vein atlas,
+        Generates an image panel containing the SWI, QSM, vein template,
         and vein mask
 
         Parameters
@@ -66,14 +66,14 @@ class ArcanaPaper(MultiStudy, ImageDisplayMixin,
             The path to save the image to. If None the image will be
             displayed instead of saved
         """
-        # Derive (when necessary) and access data SWI, QSM, vein atlas,
+        # Derive (when necessary) and access data SWI, QSM, vein template,
         # and vein mask data in the repository.
         vein_masks = self.data('t2star_vein_mask')
         qsms = self.data('t2star_qsm')
         swis = self.data('swi_brain')
         cv_image = self.data('t2star_composite_vein_image')
         # Loop through all sessions
-        for swi, qsm, vein_atlas, vein_mask in zip(swis, qsms, cv_image,
+        for swi, qsm, vein_template, vein_mask in zip(swis, qsms, cv_image,
                                                    vein_masks):
             # Set the saturation limits for the QSM image
             row_kwargs = [{} for _ in range(4)]
@@ -82,7 +82,7 @@ class ArcanaPaper(MultiStudy, ImageDisplayMixin,
             # Display slices from the filesets in a panel using
             # method from the ImageDisplayMixin base class.
             self.display_slice_panel(
[…]

### 2019-05-13 examples/manuscript.py

@@ -1,7 +1,7 @@
-from arcana import (Study, StudyMetaClass, FilesetInputSpec, FilesetSpec,
-                    FieldInputSpec, FieldSpec, ParamSpec, SwitchSpec,
+from arcana import (Study, StudyMetaClass, InputFilesetSpec, FilesetSpec,
+                    InputFieldSpec, FieldSpec, ParamSpec, SwitchSpec,
                     FilesetCollection, XnatRepo, Fileset)
-from arcana.data.file_format.standard import text_format
+from arcana.data.file_format import text_format
 from banana.file_format import (
     nifti_gz_format, dicom_format, nifti_format, analyze_format)
 
@@ -9,21 +9,21 @@ STD_IMAGE_FORMATS = (dicom_format, nifti_format, nifti_gz_format,
                      analyze_format)
 
 template_repo = XnatRepo('http://central.xnat.org', 'SAMPLE_TEMPLATES')
-template1_default = FilesetCollection(Fileset('sample_atlas', ))
+template1_default = FilesetCollection(Fileset('sample_template', ))
 
 
 class ExampleStudy(Study, metaclass=StudyMetaClass):
 
     add_data_specs = [
-        # Acquired file sets
-        FilesetInputSpec('acquired_file1', text_format),
-        FilesetInputSpec('acquired_file2', IMAGE_FORMATS),
-        # Acquired fields
-        FieldInputSpec('acquired_field1', int, frequency='per_subject'),
-        FieldInputSpec('acquired_field2', str,),
-        # "Acquired" file set with default value. Useful for standard templates
-        FilesetInputSpec('template1', IMAGE_FORMATS, frequency='per_study',
-                            default=template1_default),
+        # Input file sets
+        InputFilesetSpec('acquired_file1', text_format),
+        InputFilesetSpec('acquired_file2', STD_IMAGE_FORMATS),
+        # Input fields
+        InputFieldSpec('acquired_field1', int, frequency='per_subject'),
+        InputFieldSpec('acquired_field2', str,),
+        # "Input" file set with default value. Useful for standard templates
+        InputFilesetSpec('template1', STD_IMAGE_FORMATS, frequency='per_study',
+                         default=template1_default),
         # Derived file sets
         FilesetSpec('derived_file1', text_format, 'pipeline1'),
         FilesetSpec('derived_file2', nifti_gz_format, 'pipeline1'),
